### 2021-03-23 manuscript.rmd
initial draft

---
title             : "The Bayesian turn in comparative content analysis"
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

author: 
  - name          : "Chung-hong Chan"
    affiliation   : "1"
    corresponding : yes
    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
    email         : "chung-hong.chan@mzes.uni-mannheim.de"
  - name          : "Adrian Rauschfleisch"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
  - id            : "2"
    institution   : "National Taiwan University, Taiwan"

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
  Source code and data are available at xxxxxx. Prereg: https://osf.io/2h4w8/

abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

keywords          : "Excepteur sint occaecat cupidatat non proident"
wordcount         : "0"

bibliography      : ["/home/chainsawriot/dev/dotfiles/bib.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
figsintext        : yes
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

*"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM

Comparative content analysis is a frequently used research design in journalism studies. Comparative content analysis is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI], among others. A comparative content analysis includes news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) and their countries (e.g. post-communist country) influence the content of news articles. For example, some hypotheses are "the coverage of foreign countries by the news is primarily  determined  by  geographical  proximity  and  the  status  of  the  covered  country" [@wilke:2012, p.306] and "the  degree  of  opinion-orientation  will  be  highest  in  newspapers  from  Polarized  Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g. newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g. degree of opinion-orientation [in news articles]).

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide. One finding from Durkheim was the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining , in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare but has a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. Traditional hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches are violating the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel: a news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

## Non-atomicity

*"When it comes to regression, multilevel regression deserves to be the default approach"* @mcelreath2020statistical [p. 356]

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries’ chocolate consumption and countries’ number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

In a comparative content analysis, it is easy to incorrectly assume that macro-level independent variables (e.g. Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g. the  degree of opinion-orientation). The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable. Suppose one wants to study how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China. In the following regression equation, let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China). Suppose there are $m$ news articles where $i = 1,2,\ldots,m$.

\begin{align}
  y_{i} = \beta_{0} + \beta_{1} x_{i} + \epsilon_{i}
\end{align}

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy[@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other. It is unrealistic to assume articles from the same media outlet are independent: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries are almost always not randomly selected. [^1] This sampling approach makes the independence assumption even more fragile.

[^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa.

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis. [^2]

[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook avocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. See also @nezlek:2008:IMM for criticism of such justification.

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across macro-level. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with regression equation like so:

\begin{equation}
  \label{eq:2}
  z_{k} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
\end{equation}

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. This method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogenous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

Another solution is to use the multilevel model (linear mixed model, or hierarchical model). In a multilevel model, the effect on micro-level dependent variable ($y$) is modeled with equations at different levels. Using the above example, $y_{ik}$ denotes whether the $i$-th article in the $j$-th country is covering China; $x_{k}$ denotes the trade volume with China of the $k$-th country where the media outlet of $i$-th article is located.

\begin{align}
  y_{ik} &= \beta_{0} + \epsilon_{ik} \\
  \beta_{0} &= \gamma_{00} + \gamma_{01} x_{k} + \mu_{0k}
\end{align}

In this equation, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average. It is usually set as a normal distribution with a variance $\tau_{00}$, i.e. $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$. Instead of a single value, regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group. It addresses the problem of clustering of articles by macro-level variables. This model is called the varying-intercept model and is used frequently in social science research. We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.

The benefit of using multilevel modeling lies in its flexibility in handling multi-level data. Suppose we also want to consider the clustering of articles around $o$ different media outlets in the above example and $j$-th media outlet is the media outlet of the $i$-th article, where $j = 1,\ldots, o$. The multilevel regression equations are rewritten as:

\begin{align}
y_{ijk} &= \pi_{0} + \epsilon_{ijk} \\
\pi_{0} &= \beta_{00} + \mu_{0j} \\
\beta_{00} &= \gamma_{000} + \mu_{00k} + \gamma_{001} x_{k}
\end{align}

This flexibility is demonstrated in the study by @rinke:2016:ISB. He studied the likelihood of opinion justification in 1559 utterances nested in 329 news items, which were in turn nested in 101 news broadcasts. Multilevel logistic regression was used to model the natural three-level hierarchy of his data.

Multilevel modeling is the way to go for analyzing non-atomic data from comparative content analysis. However, the conventional approach for statistical inference makes it not optimal.

## Non-stochasticity

*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box (TODO)

The conventional approach for statistical inference in multilevel modeling is maximum likelihood estimation (MLE). @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e. more false positive) and the shrinkage is more severe when the number of macro-level units (e.g. countries) is small. @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF;@bryan:2015:MMC]. Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons. Our argument is more in line with @western:1994:BIC.

Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is. Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from the population. Based on this assumption and with just one experiment, we make an estimation about the population. The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e. which subjects were randomly sampled from the population. Randomized surveys, for examples, are assumed to be repeatable through repeated random sampling of the population. Suppose we replicated the same survey for 100 times and we would obtain a slightly different sample every time. We then calculated the 90\% confidence interval of the mean for each of these 100 surveys. We should anticipate that more or less 90 out of these 100 confidence intervals would include the true mean of the population. We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**. However, we can say 90 is more probable than says, 0 or 100.

Comparative content analysis, unlike randomized surveys or randomized media experiments, usually collects all available data. In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014-2015. 
Census-style studies are not repeatable and thus they generate non-stochastic data. In other words, data from comparative content analysis are fundamentally irrelevant for frequentist inference [@western:1994:BIC]. P-values and confidence intervals generated do not have the same meaning as those from repeatable studies. According to @western:1994:BIC [p. 413], these values from non-stochastic data "lack meaning even as abstract propositions".

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis.

## Bayesian analysis

*"PROBABILITY DOES NOT EXIST."* Bruno de Finetti

What is the probability for this paper being accepted by *Digital Journalism*? Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate from *Digital Journalism*’s website. After this paper is submitted and is not desk rejected, the probability might be around 24 to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40 to 60%. If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data. We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$). This can be summarize in the following equation [@gelman2020bayesian]:

\begin{align}
	P(\theta | X) \propto  P(\theta) P(X| \theta)
\end{align}

The $P(X| \theta)$ part is called likelihood function. In the $Digital Journalism$ example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. More often than not, we do not have any information to set an informative prior (e.g. What about *Journal of Communication*?). One option is to consult experts or to make an educated guess. But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying prior attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from prior is greatly weakened, when the data is getting bigger. Also, one can select a weakly informative prior [@lemoine:2019:M] which only specifies the possible range of the posterior [^4]. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose a appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).

[^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised.

## Bayesian communication research

*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modelling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19]

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative content analysis that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative content analysis fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modelling is no longer an issue.

# Methods

We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis. The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage? In other words, we studied the ecological effect of the distance from China on the frequency of China coverage. Several distance measures were used to formulate our pre-registered hypotheses: physical distance between two capitals, trade volume between two countries, and cultural distance between two societies.

For demonstrative purposes, our analysis was separated into two levels: outlet-level analysis and article-level analysis. The outlet-level analysis is an aggregated version of article-level analysis. It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with very small data size. The article-level analysis is used to demonstrate the analysis of a massive three-level dataset.

## Data

The useNews is an openly available dataset [@puschmann:2020] that includes media content data from an array of worldwide media outlets from 2019 to 2020. The media content data was collected from the MIT MediaCloud and made available as document-term matrices.

We used only the data from 2019 as the baseline. It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was in the zenith of the US-China trade war.

Also, we excluded media outlets that contributed <1000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

In the outlet-level analysis, the data has 61 rows and each row represents a media outlet. The data contains a count of articles covering China ($z$), total number of articles ($n$), country of the outlet($k$), and distance measures ($x$).

In the article-level analysis, the data has 1,525,871 rows and each row represents an article. The data contains a binary dependent variable of China coverage ($y$), media outlet($j$), country of the outlet($k$), and distance measures ($x$).

## Coverage of China

A dictionary-based approach was used. The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis. The seed dictionaries contain words about Chinese, China, Beijing and Shanghai. We developed further the Spanish, Romanian, Korean, Portugese, Norwegian, and Dutch dictionaries. The dictionaries were applied to the 61 DTMs of all included media outlets. An article is classified as China coverage when at least one dictionary match is detected.

<!-- ```{r, echo = FALSE} -->
<!-- Language <- c("English", "German", "Spanish", "Romanian", "Korean", "Portugese", "Norwegian", "Dutch") -->

<!-- Lexicon <- c("chinese, china, beijing, shanghai", "chinesisch*, chinesin*, chinese*, china*, peking, shanghai", "chino*, china*, pekin, shanghái", "chinez*, china, beijing, shanghai", "중국인, 중화, 중국, 베이징, 북경, 상하이, 상해", "chinês, chines*, china, pequim, xangai", "kineser*, kinesar*, kinesisk, kina, beijing, shanghai", "chinezen, chinees*, chinezin*, chines*, china, peking, beijing, sjanghai, shanghai") -->
<!-- papaja::apa_table(data.frame(Language, Lexicon), caption = "Dictionaries used for detecting China coverage") -->
<!-- ``` -->

## Distance measures

Several distance measures were used as the independent variable to test our central research questions: physical distance, trade volume, and cultural distance. Physical distance is calculated as the Great-circle distance between Beijing and the capital of the hosting city of the media outlet (e.g. Bucharest). The volumes of import to and export from China with the host country of a media outlet was extracted from the 2019 edition of China Statistical Yearbook (http://www.stats.gov.cn/tjsj/ndsj/2019/indexeh.htm). Cultural distance from China to the host country of a media outlet was extracted from culturaldistance.com, which was calculated using the data from World Value Survey with the algorithm from @bell:2009:C. All of these distance measures were log-transformed.

## Modeling

For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression. It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach. It is because disaggregation approach commits atomistic fallacy and MLE approach ignores the non-stochastic nature of the data.

### Outlet-level analysis

We used negative binomial regression for this analysis. Media outlets are nested in countries (e.g. *Der Standard* and *Österreichischer Rundfunk* are nested in Austria). Thus, a country-based variance is added ($\mu_{0k}$). Applying the same notation under the introduction section, the multilevel regression equations are:

\begin{align}
\log(\frac{z_{jk}}{n_{j}}) &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}
\end{align}

In lme4 and brms, the equation is expressed as such:

```r
# brms
brms::brm(z ~ offset(log(n)) + (1|k)+log(x),
          family = negbinomial(), data = outlet_data)
# lme4
lme4::glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
```

In the disaggregation case, the multilevel structure is ignored and the regression equation becomes:

\begin{align}
\log(\frac{z_{jk}}{n_{j}}) &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
\end{align}

In MASS, it is expressed as such:

```r
MASS::glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
```

We named the models with different independent variables as model A1-4 respectively (A1: log import volume; A2: log export volume; A3: log physical distance; A4: log cultural distance).

### Article-level analysis

We used logistic regression for this analysis. Due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.

In this analysis, an article is nested in its media outlet. The media outlet is in turn nested in its country. Two variance terms ($\mu_{0j}$ and $\mu_{00k}$) are needed. The multilevel regression equations are:

\begin{align}
p_{ijk} &= Pr(y_{ijk} = 1) \\
L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
L_{ijk} &= \pi_{0} + \epsilon_{ijk} \\
\pi_{0} &= \beta_{00} + \mu_{0j} \\
\beta_{00} &= \gamma_{000} + \mu_{00k} + \gamma_{001} x_{k}
\end{align}

Or in lme4/brms code:

```r
brms::brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
lme4::glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
```

In the disaggregation case, the multilevel structure is ignored and the regression equations become:

\begin{align}
p_{ijk} &= Pr(y_{ijk} = 1) \\
L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
L_{ijk} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{ijk} \\
\end{align}

In MASS, it is expressed as such:

```r
MASS::glm(y ~ log(x), family = binomial(), data = article_data)
```

We named this model as model B1.

### Priors

For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$. For the article-level analysis, the four unknown paramters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$. The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.

Usually, the first step for choosing priors is to review previous studies and look for possible values to be used as our informative priors. Although @wu:2000:SDI is a possible reference point, we select not to use this because China was not studied. Also, the modeling technique was quite different from the current one.

In this analysis, we used weakly informative priors suggested by @lemoine:2019:M.

For regression coefficients, e.g. $\gamma_{00}$, we used a normal distribution of $\mathcal{N}(0, 1)$. For variance terms, e.g. $\mu_{0k}$, a student t-distribution of $\mathcal{t}(3, 0, 2.5)$ was used. A gamma distribution of $\mathcal{Gamma}(0.01, 0.01)$ was used for the shape parameter $\phi$.

All, except the prior for regression coefficients, are default priors suggested by *brms*. The prior can be set with the following R code.

```r
weaklyinformative_prior <- c(prior_string("normal(0, 1)",
                                          class = "b"),
                             prior_string("normal(0, 1)",
                                          class = "Intercept"))
# The sample_prior argument is optional. But useful for further analysis.
import_brms <- brms::brm(z~offset(log(n))+(1|k)+log(x_import),
          data = outlet_data, family = negbinomial(),
          prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms
```

### Other parameters

Other parameters for Bayesian multilevel regression analysis control how the MCMC should be performed. Three parameters are important: number of iterations, number of chains and *adapt_delta*. It is not some magic numbers that you can plug and play. However, it is in general safe to use the default values, i.e. number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence. *brms* is smart enough to give suggestions on how to adjust these three values. Nonetheless, we provide a short guide on how to diagnose convergence.

# Regression results

Table \@ref(tab:t1) shows a summary of all models from outlet-level analysis using three different ways of modeling. The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$). It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution. By default, *brms* displays the mean and the 95\% high density interval (HDI). [^5] These two values represent the point and interval estimates of the regression coefficient.

[^5]: HDI is one representation of Bayesian credible interval. It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility, but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval. However, there is a general concern about this crediblity level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitariness of the practice. @leeuw:2020:AAT select 90\%.

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China.

Table: (\#tab:t1) Point and interval estimates from outlet-level analysis using three different analytic strategies: Disaggregation approach, multilevel modeling using MLE and Bayesian multililevel modeling

| Model                           | Disaggregate ($\beta_{1}$, 95\% CI) | MLE ($\gamma_{01}$, 95\% CI) | Bayesian ($\gamma_{01}$, 95\% HDI) |
|:--------------------------------|:------------------------------------|------------------------------|------------------------------------|
| Model A1: Log import volume     | 0.25 (0.18, 0.33)                   | 0.25 (0.18, 0.33)            | 0.25 (0.18, 0.33)                  |
| Model A2: Log export volume     | 0.22 (0.14, 0.30)                   | 0.22 (0.13, 0.31)            | 0.22 (0.11, 0.33)                  |
| Model A3: Log Physical distance | -0.02 (-0.34, 0.24)                 | -0.10 (-0.55, 0.31)          | -0.12 (-0.63, 0.39)                |
| Model A4: Log Cultural distance | -0.45 (-1.26, 0.34)                 | -0.60 (-1.80, 0.55)          | -0.62 (-2.12, 0.78)                |

Model B1 confirms the above again (Table \@ref(tab:t2) ). Therefore, both article- and outlet-level analyses arrive at the same conclusion.

```{r t2, results = "asis"}
### TODO: to prim it further
require(brms)
require(parameters)
require(dplyr)
article_level <- readRDS("import_logit.RDS")
article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res

res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2)
```

## Diagnosis of convergence

It is important to confirm the model is converged. We demonstrate how to confirm this with model A1.

The first step is Gelman-Rubin convergence diagnostic [@brooks:1998:GMM; @vehtari:2020:RNF]. *brms* displays this in the form of $\widehat{R}$. In general, $\widehat{R} \approx 1$. The model might not have converged, when $\widehat{R} \ge 1.01$ [@vehtari:2020:RNF]. The *summary()* function of brms displays the $\widehat{R}$ for each of the estimated unknown parameters. All parameter estimates have a $\widehat{R} = 1.0$.

The second step is the MCMC trace plot (can be obtained with the function *plot()*). The traceplot should display the so-called "fuzzy caterpillar" pattern (Figure \@ref(fig:fig1)). There should be no breakage.

```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy catepillar pattern."}
require(brms)
import_brms <- readRDS("import_brms.RDS")
plot(import_brms)
```

An additional check is to study the autocorrelation of all chains. The correlogram should display low serial correlation (successive high correlation). The function *mcmc_plot* can be used to plot this (Figure \@ref(fig:fig2)).

If the diagnostics show evidence of nonconvergence, it is suggested to increase the number of iterations and number of chains.

```{r fig2, echo = FALSE, fig.cap = "Correlogram of four chains showing no significant higher-order lag"}
mcmc_plot(import_brms, type = "acf")
```

## Further diagnostics

There are several diagnostic checks that we can do to make sure our model is valid.

* Increasing number of iterations

The first test is to increase the number of iterations from 2000 to a higher value, e.g. 4000, and see if the result is consistent with the initial analysis. This check makes sure our result is not some transient result due to short iteration time.

Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between two analyses.

* Using another weakly informative prior

We can also use another weakly informative prior to see how our initial choice influence the result. We tried another weakly informative prior for the regression coefficients, $\mathcal{t}(1, 0, 0.25)$ [@gelman:2008]. Similarly, changing prior only impacts the second decimal place of the estimates.

* Posterior predictive checks

We can use posterior predictive checks to study how our model fits our data. The gist of the method is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original data ($y$). A good model should display a similar probability distribution of $y_{rep}$ and $y$. It can be done with the function *pp_check()* (Figure \@ref(fig:fig3).

```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
pp_check(import_brms, nsamples = 100)
```

# Discussion

Instead of arguing the advatnages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

## Extension #1: Hypothesis testing

Under the Bayesian framework, we can test hypotheses about the parameter estimates [@shikano:2019:HTB]. These hypotheses are similar to the null hypothesis in the Neyman-Pearson's sense. For example, we want to test the two-sided hypothesis of $\gamma_{01} = 0$ for Model A1. For this, we need to calculate the posterior probability of this hypothesis: $P(\gamma_{01} = 0 | X)$. The function *hypothesis()* can be used to test such hypothesis.

```r
hypothesis(import_brms, "logx_import = 0")
```

The posterior probability of this hypothesis is 0. Therefore, we can safely reject the hypothesis and conclude that $\gamma_{01} \neq 0$, i.e. log import volume of the outlet's country is associated with the frequency of China coverage at the outlet level.

Another approach suggested by @kruschke:2018:RAP, which uses the region of practical equivalence (ROPE), is available from the package bayestestR [@makowski:2019].

## Extension #2: Cross-level interaction

We can also study the interaction between a macro- and a micro-level variable. Cross-level interaction is useful to study how the effect of context variables manifest differently in individuals with different characteristics. An example of cross-level interaction in our example is whether the relationship between import volume and increase in China coverage manifests differently between public broadcasters and for-profit media.

We can model a cross-level interaction by adding an interaction term between the macro- and micro-level variables, as well as a varying-slope component for the micro-level variable [@heisig:2019:WYS]. With *brms*, it can be done with this:

```r
# suppose "public" is a binary variable
import_brms_public <- brms::brm(
      z~offset(log(n))+(1 + public|k)+log(x_import)*public,
      data = outlet_data, family = negbinomial(),
      prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms_public
```

The regression coefficients for the main effect of public broadcasting and the interaction terms have a wide 95\% HDI that covers zero. It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function). The trajectories of public broadcastors and for-profit media outlets are similar, indicating no interaction.

```{r fig4, echo = FALSE, fig.cap = "Conditional effects plot showing no interaction among public broadcasting, import volume and China coverage."}
require(ggplot2)
condit_plots <- readRDS("condit_plots.RDS")
condit_plots$`x_import:public` + xlab("Import Volume") + ylab("Number of articles mentioning China per 10,000 articles") + scale_x_continuous(labels = scales::comma) + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
```

## Extension #3: Current study as the informative prior for the next study

Suppose we would like to replicate the study and confirm the same relationship with the 2020 useNews data. This time, we do not need to (and actually, we should not) use the weakly informative prior again. It is because we have *prior* understanding about the outlet-level determinants of China coverage: We know from the 2019 data that $\gamma_{01}$ should be around 0.25 with a standard deviation of 0.05. This can be entered into our new analysis as the informative prior.

```r
informative_prior <- c(prior_string("normal(0.25, 0.05)", class = "b",
                                    coef = "logx_import"),
                       prior_string("normal(-6.69, 0.66)",
                                    class = "Intercept"))
import_2020 <- brm(z_2020~offset(log(n_2020))+(1|k)+log(x_import),
                   data = outlet_data2020, family = negbinomial(),
                   prior = informative_prior, sample_prior = TRUE)
```

The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020. This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, the raison d'être of open science [@dienlin:2020:AOS].

## Extension #4: Temporal changes

Bayesian multilevel regression analysis is also useful to study temporal changes, because observations from the same subject collected from different time points are naturally a cluster. The same strategy for handling the clustering of observations in the multilevel modeling can be used. We model observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries. Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic and the presidential election in the US. It can be analyzed with this 3-level model.

```r
## Suppose yr is a binary dummy variable indicating the year 2020.
import_long <- brm(z~offset(log(n))+(1|k/i)+yr, data = outlet_long,
                   family = negbinomial(),
                   prior = weaklyinformative_prior,
                   sample_prior = TRUE)
import_long
```

The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). It seems that there is a global increase in China coverage from 2019 to 2020.

# Contributions

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyse data from comparative content analyses. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-03-23 01_getting_data.R

@@ -1,0 +1,4 @@
+require(osfr)
+require(quanteda)
+
+osf_retrieve_node("uzca3") %>% osf_ls_files(n_max = 100, pattern = "rds") %>% osf_download(path = "data", progress = TRUE)

### 2021-03-23 02_data_munging.R

@@ -1,0 +1,66 @@
+require(quanteda)
+require(tidyverse)
+
+mc <- readRDS(here::here("data/usenews.mediacloud.2019.rds"))
+wm <- readRDS(here::here("data/usenews.mediacloud.wm.2019.rds"))
+
+dfm_lookup(wm[[1]], dictionary(list(China = c("China"))))
+saveRDS(wm[[1]], "NYT_2019.RDS")
+
+gen_overview <- function(i, wm) {
+    x <- wm[[i]]
+    docvars(x) %>% count(language, sort = TRUE) %>% pull(language) -> langs
+    lang <- langs[1]
+    media <- unique(docvars(x, 'media_name'))
+    n <- nrow(docvars(x))
+    tibble(i = i, media = media, lang = lang, n = n)
+}
+
+overview <- map_dfr(seq_len(length(wm)), gen_overview, wm = wm)
+overview %>% filter(n > 1000) %>% pull(lang) %>% unique
+
+##head(docvars(wm[[1]]))
+
+##overview %>% filter(n > 1000) %>% rio::export("media1k.csv")
+
+media1k <- rio::import("media1k.csv")
+
+china_dict <- dictionary(file = "chinese.yml")
+
+cal_china <- function(media_id, media_lang, wm, china_dict) {
+    print(media_id)
+    ## weird bug of read_yaml treating "no" as FALSE
+    dict_id <- which(media_lang == c("en", "no", "es", "ro", "de", "nl", "ko", "pt"))
+    dfm_lookup(wm[[media_id]], china_dict[dict_id], levels = 1) %>% convert(to = "data.frame") %>% pull(2) -> res
+    return(sum(res != 0))
+}
+
+res <- map2_int(media1k$i, media1k$lang, cal_china, wm = wm, china_dict = china_dict)
+
+cbind(media1k, res) %>% group_by(country) %>% summarise(mr = sum(res) / sum(n)) %>% arrange(mr) -> country_summary
+
+countries <- rio::import("countries.xlsx") %>% tibble::as_tibble()
+
+country_summary %>% left_join(countries, by = "country") %>% pivot_longer(cols = phy_dist:cult_dist, names_to = "dist", values_to = "value", names_repair = "minimal") %>% ggplot(aes(x = mr, y = value, label = country)) + geom_text() + facet_grid(dist ~ . , scales = "free") + scale_y_continuous(trans='log2') + geom_smooth(method = "lm", se = FALSE)
+
[…]

### 2021-03-23 03_big_lr.R

@@ -1,0 +1,83 @@
+require(quanteda)
+require(tidyverse)
+
+mc <- readRDS(here::here("data/usenews.mediacloud.2019.rds"))
+wm <- readRDS(here::here("data/usenews.mediacloud.wm.2019.rds"))
+
+gen_overview <- function(i, wm) {
+    x <- wm[[i]]
+    docvars(x) %>% count(language, sort = TRUE) %>% pull(language) -> langs
+    lang <- langs[1]
+    media <- unique(docvars(x, 'media_name'))
+    n <- nrow(docvars(x))
+    tibble(i = i, media = media, lang = lang, n = n)
+}
+
+overview <- map_dfr(seq_len(length(wm)), gen_overview, wm = wm)
+overview %>% filter(n > 1000) %>% pull(lang) %>% unique
+
+##head(docvars(wm[[1]]))
+
+##overview %>% filter(n > 1000) %>% rio::export("media1k.csv")
+
+media1k <- rio::import("media1k.csv")
+
+china_dict <- dictionary(file = "chinese.yml")
+
+cal_china <- function(media_id, media_lang, wm, china_dict) {
+    print(media_id)
+    ## weird bug of read_yaml treating "no" as FALSE
+    dict_id <- which(media_lang == c("en", "no", "es", "ro", "de", "nl", "ko", "pt"))
+    dfm_lookup(wm[[media_id]], china_dict[dict_id], levels = 1) %>% convert(to = "data.frame") %>% pull(2) -> res
+    return(sum(res != 0))
+}
+
+res <- map2_int(media1k$i, media1k$lang, cal_china, wm = wm, china_dict = china_dict)
+
+cbind(media1k, res) %>% group_by(country) %>% summarise(mr = sum(res) / sum(n)) %>% arrange(mr) -> country_summary
+
+countries <- rio::import("countries.xlsx") %>% tibble::as_tibble()
+
+## country_summary %>% left_join(countries, by = "country") %>% pivot_longer(cols = phy_dist:cult_dist, names_to = "dist", values_to = "value", names_repair = "minimal") %>% ggplot(aes(x = mr, y = value, label = country)) + geom_text() + facet_grid(dist ~ . , scales = "free") + scale_y_continuous(trans='log2') + geom_smooth(method = "lm", se = FALSE)
+
+country_summary %>% left_join(countries, by = "country") %>% select(-country) %>% cor(use = "pair", method = "kendall")
+
[…]

### 2021-03-23 04_small_count.R

@@ -1,0 +1,124 @@
+require(brms)
+require(lme4)
+require(tidyverse)
+
+set.seed(2021)
+
+## require(sjmisc)
+## require(sjstats)
+
+outlet_data <- readRDS("small_df.RDS")
+
+### To match the notion in the paper
+
+colnames(outlet_data) <- c("j", "media", "lang", "n", "k", "z", "x_phy", "x_export", "x_import", "x_cult")
+
+media1k <- rio::import("media1k.csv") %>% tibble::as_tibble()
+
+outlet_data$public <- ifelse(media1k$public == 1, "Yes", "No")
+
+## media_summary %>% mutate(prob = res / n, logexport = log(export)) %>% select(prob, logexport, country) %>% ggplot(aes(x = logexport, y = prob, color = country)) + geom_point()
+
+import_formula <- brmsformula(z~offset(log(n))+(1|k)+log(x_import))
+
+get_prior(import_formula, data = outlet_data, family = negbinomial())
+
+## IMPORT
+weaklyinformative_prior <- c(prior_string("normal(0, 1)", class = "b"), prior_string("normal(0, 1)", class = "Intercept"))
+
+## import_brms_prior <-  brm(z~offset(n)+(1|k)+log(x_import), data = outlet_data, family = negbinomial(), control = list(adapt_delta = 0.99), sample_prior = "only", prior = weaklyinformative_prior)
+
+## condit <- data.frame(x_import = unique(outlet_data$x_import), n = 10)
+## y_prep <- posterior_predict(import_brms_prior, nsamples = 4000)
+## prior_checks <- conditional_effects(import_brms_prior, conditions = condit, method = "predict")
+## prior_checks_plot <- plot(prior_checks, ncol = 6, plot = FALSE)
+## prior_checks_plot[[1]] + ggtitle("Prior predictive distributions")
+
+import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import), data = outlet_data, family = negbinomial(), control = list(adapt_delta = 0.99), prior = weaklyinformative_prior, sample_prior = TRUE)
+saveRDS(import_brms, "import_brms.RDS")
+
+
+## svg("fig1.svg")
+## plot(import_brms)
+## dev.off()
+
+conditional_effects(import_brms)
+
+summary(import_brms)
+
+pp_check(import_brms)
+
[…]

### 2021-03-23 05_munging2020data.R

@@ -1,0 +1,51 @@
+require(quanteda)
+require(tidyverse)
+
+mc <- readRDS(here::here("data/usenews.mediacloud.2020.rds"))
+wm <- readRDS(here::here("data/usenews.mediacloud.wm.2020.rds"))
+
+gen_overview <- function(i, wm) {
+    x <- wm[[i]]
+    docvars(x) %>% count(language, sort = TRUE) %>% pull(language) -> langs
+    lang <- langs[1]
+    media <- unique(docvars(x, 'media_name'))
+    n <- nrow(docvars(x))
+    tibble(i = i, media = media, lang = lang, n = n)
+}
+
+overview <- map_dfr(seq_len(length(wm)), gen_overview, wm = wm)
+
+outlet_data <- readRDS("small_df.RDS")
+
+### To match the notion in the paper
+
+colnames(outlet_data) <- c("j", "media", "lang", "n", "k", "z", "x_phy", "x_export", "x_import", "x_cult")
+
+media1k <- rio::import("media1k.csv") %>% tibble::as_tibble()
+
+outlet_data$public <- ifelse(media1k$public == 1, "Yes", "No")
+
+require(fuzzyjoin)
+
+overview %>% mutate(media = recode(media, `Sydney Morning Herald` = "The Sydney Morning Herald", `HuffPost` = "Huffington Post", `Spiegel` = "spiegel.de")) %>% stringdist_left_join(outlet_data, by = "media") %>% filter(n.x >= 1000 & !is.na(j)) -> overview1920
+
+overview1920
+
+china_dict <- dictionary(file = "chinese.yml")
+
+cal_china <- function(media_id, media_lang, wm, china_dict) {
+    print(media_id)
+    ## weird bug of read_yaml treating "no" as FALSE
+    dict_id <- which(media_lang == c("en", "no", "es", "ro", "de", "nl", "ko", "pt"))
+    dfm_lookup(wm[[media_id]], china_dict[dict_id], levels = 1) %>% convert(to = "data.frame") %>% pull(2) -> res
+    return(sum(res != 0))
+}
+
+res <- map2_int(overview1920$i, overview1920$lang.x, cal_china, wm = wm, china_dict = china_dict)
+overview1920$z_2020 <- res
+
[…]

### 2021-03-23 06_analyzing2020.R

@@ -1,0 +1,35 @@
+require(brms)
+
+import2019 <- readRDS("import_brms.RDS")
+
+outlet_data2020 <- readRDS("overview1920.RDS")
+
+import2019
+
+## gamma01 0.25, se 0.05
+## gamma00 -6.69, se 0.66
+## sd 0.08 se 0.07
+
+parameters::parameters(import2019, dispersion = TRUE, centrality = "mean")
+
+informative_prior <- c(prior_string("normal(0.25, 0.05)", class = "b",, coef = "logx_import"), prior_string("normal(-6.69, 0.66)", class = "Intercept"))
+
+
+set.seed(2021)
+import_2020 <- brm(z_2020~offset(log(n_2020))+(1|k)+log(x_import), data = outlet_data2020, family = negbinomial(), control = list(adapt_delta = 0.99), prior = informative_prior, sample_prior = TRUE)
+summary(import_2020)
+
+require(tidyverse)
+
+outlet_data2020 %>% select(i, k, n_2020, n_2019, k) %>% pivot_longer(starts_with("n"), names_to = "yr", values_to = "n") -> n_long
+
+outlet_data2020 %>% select(i, z_2020, z_2019) %>% pivot_longer(-i, names_to = "yr", values_to = "z") -> z_long
+
+n_long$z <- z_long$z
+
+n_long %>% mutate(yr = ifelse(yr == "n_2020", TRUE, FALSE)) -> outlet_long
+
+weaklyinformative_prior <- c(prior_string("normal(0, 1)", class = "b"), prior_string("normal(0, 1)", class = "Intercept"))
+
+set.seed(2021)
+import_long <- brm(z~offset(log(n))+(1|k/i)+yr, data = outlet_long, family = negbinomial(), control = list(adapt_delta = 0.99), prior = weaklyinformative_prior, sample_prior = TRUE)

### 2021-04-05 manuscript.rmd
Further update the manuscript, add abstract, fix language

@@
   The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
-  Source code and data are available at xxxxxx. Prereg: https://osf.io/2h4w8/
+  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/
 
 abstract: |
-  Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+  The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis.
+It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data.
+Bayesian multilevel regression is suggested to be a, and probably, the only, valid analytical approach.
+Using the openly available useNews data and the R package brms, we demonstrate how to apply such approach for the analysis of comparative content analysis.
+We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model.
 
-keywords          : "Excepteur sint occaecat cupidatat non proident"
+keywords          : "Bayesian inference, multilevel model, comparative content analysis, ecological effect"
 wordcount         : "0"
@@
 newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g.
-degree of opinion-orientation [in news articles]).
+degree of opinion-orientation), namely, the article-level.
 
@@
 A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide.
-One finding from Durkheim was the higher suicide rate among citizens from Scandinvian countries than those from other European countries.
+Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries.
 Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis.
-An example of hypothesis-generating comparative content analysis is @chan2020combining , in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
-Hypothesis-generating comparative content analysis, however, is rare but has a confirmatory outlook.
+An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
+Hypothesis-generating comparative content analysis, however, is rare.
+Most studies have a confirmatory outlook.
 As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects.
-Traditional hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
+Traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
 In @wu:2000:SDI, multiple stepwise regression was used.
-These approaches are violating the underlying assumptions of the statistical analyses.
-It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel: a news article is nested within its media outlet and its media outlet is in turn nested within its country.
+These approaches violate the underlying assumptions of the statistical analyses.
+It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel.
+A news article is nested within its media outlet and its media outlet is in turn nested within its country.
 Such data structure brings two problems: non-atomicity and non-stochasticity.
@@
 Eating more chocolate makes one cleverer) based on macro-level data (e.g.
-the correlation between countries’ chocolate consumption and countries’ number of Nobel winners).
+the correlation between countries' chocolate consumption and countries' number of Nobel winners).
 The reverse of ecological fallacy, i.e.
@@
 This method is the so-called "disaggregation approach".
-From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy[@hox2017multilevel].
+From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel].
 From a statistical standpoint, this approach violates the underlying independence assumption.
@@
 We reject this justification because it violates the independence assumption and thus commits atomistic fallacy.
-See also @nezlek:2008:IMM for criticism of such justification.
+See also @nezlek:2008:IMM for a criticism of such justification.
 
 There are two solutions to this.
-The first solution is to aggregate the micro-level dependent variable across macro-level.
+The first solution is to aggregate the micro-level dependent variable across a macro-level inpendent variable.
 Suppose there are $n$ countries in the above example.
 One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$.
-Then, we can do a count-based regression with regression equation like so:
+Then, we can do a count-based regression with a regression equation like so:
 
@@
 
-In this equation, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average.
-It is usually set as a normal distribution with a variance $\tau_{00}$, i.e.
+In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average.
+It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e.
 $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$.
@@
 
-*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box (TODO)
+*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box
 
@@
 The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper.
-We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition.
-The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM].
+<!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition.
+--> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM].
 And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S].
@@
 
-Also, we excluded media outlets that contributed <1000 articles in that year.
-This threshold allowed us to retain media outlets that the frequency of China coverage be reliably estimated.
+We excluded media outlets that contributed <1000 articles in that year.
+This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated.
 In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included.
@@
 4000, and see if the result is consistent with the initial analysis.
-This check makes sure our result is not some transient result due to short iteration time.
+This check makes sure our result is not transient due to short iteration time.
 
@@
 A good model should display a similar probability distribution of $y_{rep}$ and $y$.
-It can be done with the function *pp_check()* (Figure \@ref(fig:fig3).
+It can be done with the function *pp_check()* (Figure \@ref(fig:fig3) ).
 
@@
 The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020.
-This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, the raison d'être of open science [@dienlin:2020:AOS].
+This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, what open science hopes to enable [@dienlin:2020:AOS].
 

### 2021-04-05 extract_bib.R
add extract_bib: to extract bib entries from the master bib file

@@ -1,0 +1,1 @@
+condensebib::reduce_bib("manuscript.rmd", master_bib = "/home/chainsawriot/dev/dotfiles/bib.bib", out_bib = "manuscript.bib")

### 2021-04-09 manuscript.rmd
extract bib file
add extract_bib: to extract bib entries from the master bib file
small edits

@@
 
-bibliography      : ["/home/chainsawriot/dev/dotfiles/bib.bib"]
+bibliography      : ["manuscript.rmd"]
 
@@
 @wu:2000:SDI], among others.
-A comparative content analysis includes news articles from various outlets and usually also from various countries.
+A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries.
 Then the included news articles are coded either manually or automatically.
@@
 As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects.
-Traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
+In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
 In @wu:2000:SDI, multiple stepwise regression was used.
@@
 A news article is nested within its media outlet and its media outlet is in turn nested within its country.
+Theoretically with a large enough sample it can be argued that a news article is nested within authors.
 Such data structure brings two problems: non-atomicity and non-stochasticity.
@@
 It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect.
-This method still has important drawbacks.
+However, this method still has important drawbacks.
 First, it cannot be used for data with more than two levels.
@@
 That is the published acceptance rate from *Digital Journalism*’s website.
-After this paper is submitted and is not desk rejected, the probability might be around 24 to 30%.
+After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%.
 After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%.
-After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40 to 60%.
+After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%.
 If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
@@
 But one person's expert opinion could be another person's wishful thinking.
-And this perceived subjectivity of specifying prior attracts wide-spread criticism from both statisticians [e.g.
+And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g.
 @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].
@@
 $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].
-The documentation of Stan also provides information on how to choose a appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).
+The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).
 

### 2021-04-13 manuscript.rmd
Explaining offset, ref #1
Fix prior journal problem, ref #1
Fix table 2, ref #1

@@
 
-bibliography      : ["manuscript.rmd"]
+bibliography      : ["manuscript.bib"]
 
@@
 @burggraaff:2017:T;@wilke:2012], news flow research [e.g.
-@wu:2000:SDI], among others.
+@wu:2000:SDI;@grasland:2019:I], among others.
 A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries.
@@
   \label{eq:2}
-  z_{k} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
+  \log{z_{k}} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
 \end{equation}
@@
 More often than not, we do not have any information to set an informative prior (e.g.
-What about *Journal of Communication*?).
+What about a new journal?).
 One option is to consult experts or to make an educated guess.
@@
 Thus, a country-based variance is added ($\mu_{0k}$).
+We also added $\log{n_{j}}$ as an offset value.
+An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation \@ref(eq:2).
+Effectively, we modeled the *rate* of China coverage.
 Applying the same notation under the introduction section, the multilevel regression equations are:
@@
 \begin{align}
-\log(\frac{z_{jk}}{n_{j}}) &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}
+\log{z_{jk}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \log{n_j} + \epsilon_{jk} \\
+\log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} +  \epsilon_{jk} \\
+\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk} \\
 \end{align}
@@
 \begin{align}
-\log(\frac{z_{jk}}{n_{j}}) &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
+\log\frac{z_{jk}}{n_{j}} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
 \end{align}
@@
 
-```{r t2, results = "asis"}
-### TODO: to prim it further
-require(brms)
-require(parameters)
-require(dplyr)
-article_level <- readRDS("import_logit.RDS")
-article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res
+<!-- ```{r t2, results = "asis"} -->
+<!-- ### TODO: to prim it further -->
+<!-- require(brms) -->
+<!-- require(parameters) -->
+<!-- require(dplyr) -->
+<!-- article_level <- readRDS("import_logit.RDS") -->
+<!-- article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res -->
 
-res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2)
-```
+<!-- res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2) -->
+<!-- ``` -->
+
+Table: (\#tab:t2) Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country
+
+| Parameter                          | Estimate | SD   | 95 \%HDI       |
+|:-----------------------------------|:---------|------|----------------|
+| $\gamma_{000}$ (Intercept)         | -7.06    | 0.81 | (-8.61, -5.44) |
+| $\gamma_{001}$ (Log import volume) | 0.27     | 0.06 | (0.16, 0.38)   |
 

### 2021-04-14 manuscript.rmd
Log transform, ref #1
added Morey et al. -Abstract - Introduction - Before Bayesian analysis

--- 2021-04-09 manuscript.rmd
@@
 abstract: |
+  Comparative content analysis is a frequently used research design in journalism studies.
 The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis.
@@
 We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model.
+Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.
 
@@
 
+# cite Durkheim's book about suicide here or a reference discussing Durkheim's reserach
 This study of ecological effect on individual behaviours has a long tradition in social sciences.
@@
 Such data structure brings two problems: non-atomicity and non-stochasticity.
+
+# add Hoekstra, R., Morey, R. D., Rouder, J. N., & Wagenmakers, E. J. (2014). Robust misinterpretation of confidence intervals. Psychonomic bulletin & review, 21(5), 1157-1164.
+# add Morey, R. D., Hoekstra, R., Rouder, J. N., Lee, M. D., & Wagenmakers, E. J. (2016). The fallacy of placing confidence in confidence intervals. Psychonomic bulletin & review, 23(1), 103-123.
+In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
+While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" (Morey et al., 2016, p.
+121) and solve the issue of misinterpreted confidence intervals (Hoeckstra et al., 2014; Rinke & Schneider, 2016).
+Using the openly available useNews data and the R package brms, we then demonstrate how to apply a Bayesian approach for the analysis of comparative content analysis.
 
@@
 Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis.
+Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals Hoeckstra et al., 2014; Rinke & Schneider, 2016).
+Switching to a Bayesian approach addresses this issue as Bayesian „credible intervals support an interpretation of probability in terms of plausibility" (Morey et al., 2016, p.
+120).
+However, for Bayesian models priors have to be chosen by reserachers.
 

### 2021-04-14 manuscript.rmd
Formatting morey

@@
 
-# cite Durkheim's book about suicide here or a reference discussing Durkheim's reserach
 This study of ecological effect on individual behaviours has a long tradition in social sciences.
-A famous example was Émile Durkheim’s investigation on the ecological factors associated with suicide.
+A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
 Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries.
-Using today’s standard, Durkheim’s analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis.
+Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis.
 An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
@@
 
-# add Hoekstra, R., Morey, R. D., Rouder, J. N., & Wagenmakers, E. J. (2014). Robust misinterpretation of confidence intervals. Psychonomic bulletin & review, 21(5), 1157-1164.
-# add Morey, R. D., Hoekstra, R., Rouder, J. N., Lee, M. D., & Wagenmakers, E. J. (2016). The fallacy of placing confidence in confidence intervals. Psychonomic bulletin & review, 23(1), 103-123.
 In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
-While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" (Morey et al., 2016, p.
-121) and solve the issue of misinterpreted confidence intervals (Hoeckstra et al., 2014; Rinke & Schneider, 2016).
+While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p.
+121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
 Using the openly available useNews data and the R package brms, we then demonstrate how to apply a Bayesian approach for the analysis of comparative content analysis.

### 2021-04-15 manuscript.rmd
- added an interpretation of CI and CredI - Extended the conclusion

--- 2021-04-14 manuscript.rmd
@@
 The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China.
+While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of infference.
+The Bayesian approach alloows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling witin  0.18 and 0.33*.
+In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*.
+This example illustrates that a Bayesian approach allows us to interpret the results in a more intutitive way.
+On of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way (Morey et al., 2016).
 
@@
 
-# Contributions
+# Conclusion
 
@@
 We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
+Using a Bayesian approach, however, has also clearly some disadvantages.
+Reserachers have to define priors in order to run a Bayesian regression analysis.
+As we could show this limitation does not pose a controversial challenge as weakly informative prios can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
+If we have prior knowledge it allows us to create even better models.
+Furthermore, it takes more time to get the results of a Bayesian regression analysis.
+Estimating a Bayesian regression model is a computationally demanding task.
+It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles.
+Still, eventually it worked and typical studies in comparative journalism research (HERE SOME EXAMPLES FROM THE LITERATURE) can be estimated in a reasonable time.
+(LETS TAKE A RANDOM SAMPLE OF 100 AND 1000 ARTICLES TO SHOW THIS IS NOT REALLY A PROBLEM).
 

### 2021-04-16 manuscript.rmd
benchmark

@@
 In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*.
+One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015].
 This example illustrates that a Bayesian approach allows us to interpret the results in a more intutitive way.
-On of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way (Morey et al., 2016).
 
@@
 Estimating a Bayesian regression model is a computationally demanding task.
-It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles.
-Still, eventually it worked and typical studies in comparative journalism research (HERE SOME EXAMPLES FROM THE LITERATURE) can be estimated in a reasonable time.
-(LETS TAKE A RANDOM SAMPLE OF 100 AND 1000 ARTICLES TO SHOW THIS IS NOT REALLY A PROBLEM).
+It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1).
+Still, eventually it worked and typical studies in comparative journalism research [e.g.
+6525 articles in @esser:2013:C] can be estimated in a reasonable time [^TIME].
+
+[^TIME]: We benchmarked the same model but with a random subset of data of some more "typical" sample sizes.
+A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical computer with 6 cores.
+Although it is comparatively more computational intensive than lme4, the time needed is still reasonable.
 

### 2021-04-16 031_big_lr_brms.R

@@ -1,0 +1,84 @@
+require(quanteda)
+require(tidyverse)
+
+## mc <- readRDS(here::here("data/usenews.mediacloud.2019.rds"))
+## wm <- readRDS(here::here("data/usenews.mediacloud.wm.2019.rds"))
+
+## gen_overview <- function(i, wm) {
+##     x <- wm[[i]]
+##     docvars(x) %>% count(language, sort = TRUE) %>% pull(language) -> langs
+##     lang <- langs[1]
+##     media <- unique(docvars(x, 'media_name'))
+##     n <- nrow(docvars(x))
+##     tibble(i = i, media = media, lang = lang, n = n)
+## }
+
+## overview <- map_dfr(seq_len(length(wm)), gen_overview, wm = wm)
+## overview %>% filter(n > 1000) %>% pull(lang) %>% unique
+
+## ##head(docvars(wm[[1]]))
+
+## ##overview %>% filter(n > 1000) %>% rio::export("media1k.csv")
+
+## media1k <- rio::import("media1k.csv")
+
+## china_dict <- dictionary(file = "chinese.yml")
+
+## cal_china <- function(media_id, media_lang, wm, china_dict) {
+##     print(media_id)
+##     ## weird bug of read_yaml treating "no" as FALSE
+##     dict_id <- which(media_lang == c("en", "no", "es", "ro", "de", "nl", "ko", "pt"))
+##     dfm_lookup(wm[[media_id]], china_dict[dict_id], levels = 1) %>% convert(to = "data.frame") %>% pull(2) -> res
+##     return(sum(res != 0))
+## }
+
+## res <- map2_int(media1k$i, media1k$lang, cal_china, wm = wm, china_dict = china_dict)
+
+## cbind(media1k, res) %>% group_by(country) %>% summarise(mr = sum(res) / sum(n)) %>% arrange(mr) -> country_summary
+
+## countries <- rio::import("countries.xlsx") %>% tibble::as_tibble()
+
+## ## country_summary %>% left_join(countries, by = "country") %>% pivot_longer(cols = phy_dist:cult_dist, names_to = "dist", values_to = "value", names_repair = "minimal") %>% ggplot(aes(x = mr, y = value, label = country)) + geom_text() + facet_grid(dist ~ . , scales = "free") + scale_y_continuous(trans='log2') + geom_smooth(method = "lm", se = FALSE)
+
+## country_summary %>% left_join(countries, by = "country") %>% select(-country) %>% cor(use = "pair", method = "kendall")
+
[…]

### 2021-04-16 032_big_lr_time.R

@@ -1,0 +1,24 @@
+require(quanteda)
+require(tidyverse)
+
+require(brms)
+
+set.seed(4521314)
+
+
+article_level_data <- readRDS("article_level_data.RDS")
+
+sample(article_level_data, 100)
+
+res100 <- microbenchmark(brm(china~(1|country/media)+log(import), data = sample_n(article_level_data, 100), family = bernoulli(), control = list(adapt_delta = 0.9), core = 6), times = 10)
+
+res1000 <- microbenchmark(brm(china~(1|country/media)+log(import), data = sample_n(article_level_data, 1000), family = bernoulli(), control = list(adapt_delta = 0.9), core = 6), times = 10)
+
+res10000 <- microbenchmark(brm(china~(1|country/media)+log(import), data = sample_n(article_level_data, 10000), family = bernoulli(), control = list(adapt_delta = 0.9), core = 6), times = 10)
+
+res30000 <- microbenchmark(brm(china~(1|country/media)+log(import), data = sample_n(article_level_data, 30000), family = bernoulli(), control = list(adapt_delta = 0.9), core = 6), times = 10)
+
+saveRDS(list(res100, res1000, res10000, res30000), "benchmark.RDS")
+
+benchmark <- readRDS("benchmark.RDS")
+plot(c(100, 1000, 10000, 30000), map_dbl(benchmark, ~mean(.$time)/1000000000))

### 2021-04-16 03_big_lr_munging.R

@@ -79,5 +79,7 @@ res_df <- map2_dfr(media1k$i, media1k$lang, cal_china2, wm = wm, china_dict = ch
 
 res_df %>% left_join(media1k, by = "i") %>% left_join(countries, by = "country") %>% as_tibble %>% mutate(china = ifelse(china == 0, 0, 1)) -> article_level_data
 
-import_brms_log <- brm(china~(1|country/media)+log(import), data = article_level_data, family = bernoulli(), control = list(adapt_delta = 0.9), core = 6)
-saveRDS(import_brms_log, "import_logit.RDS")
+saveRDS(article_level_data, "article_level_data.RDS")
+
+##import_brms_log <- brm(china~(1|country/media)+log(import), data = article_level_data, family = bernoulli(), control = list(adapt_delta = 0.9), core = 6)
+##saveRDS(import_brms_log, "import_logit.RDS")

### 2021-04-16 manuscript.rmd

@@
 Cultural distance from China to the host country of a media outlet was extracted from culturaldistance.com, which was calculated using the data from World Value Survey with the algorithm from @bell:2009:C.
-All of these distance measures were log-transformed.
+All of these distance measures were log-transformed, because previous studies showed the relationship between news coverage and these distance measures is not linear [@grasland:2019:I;@wu:2000:SDI].
 

### 2021-04-16 manuscript.rmd
Spell check with ispell, fix formatting issues

@@
 
-This study of ecological effect on individual behaviours has a long tradition in social sciences.
+This study of ecological effect on individual behaviors has a long tradition in social sciences.
 A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
-Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries.
+Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries.
 Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis.
@@
 [^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5].
-Even a multilevel modeling textbook avocates this justification [@bickel2007multilevel].
+Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel].
 We reject this justification because it violates the independence assumption and thus commits atomistic fallacy.
@@
 There are two solutions to this.
-The first solution is to aggregate the micro-level dependent variable across a macro-level inpendent variable.
+The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable.
 Suppose there are $n$ countries in the above example.
@@
 First, it cannot be used for data with more than two levels.
-In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogenous and the information about media outlets was discarded.
+In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogeneous and the information about media outlets was discarded.
 Second, this method discards a massive amount of information.
@@
 Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis.
-Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals Hoeckstra et al., 2014; Rinke & Schneider, 2016).
-Switching to a Bayesian approach addresses this issue as Bayesian „credible intervals support an interpretation of probability in terms of plausibility" (Morey et al., 2016, p.
-120).
-However, for Bayesian models priors have to be chosen by reserachers.
+Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
+Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
+However, for Bayesian models priors have to be chosen by researchers.
 
@@
 --> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM].
-And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S].
+And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S].
 R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users.
@@
 
-*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modelling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
+*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
 19]
@@
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
-The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modelling is no longer an issue.
+The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
 
@@
 We used only the data from 2019 as the baseline.
-It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
+It is important to note that the Hong Kong protests, the 30th anniversary of the Tienanmen Square Protests and the 70th anniversary of the communist regime were in that year.
 Also, it was in the zenith of the US-China trade war.
@@
 The seed dictionaries contain words about Chinese, China, Beijing and Shanghai.
-We developed further the Spanish, Romanian, Korean, Portugese, Norwegian, and Dutch dictionaries.
+We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries.
 The dictionaries were applied to the 61 DTMs of all included media outlets.
@@
 ```r
+require(brms)
+require(lme4)
 # brms
-brms::brm(z ~ offset(log(n)) + (1|k)+log(x),
+brm(z ~ offset(log(n)) + (1|k)+log(x),
           family = negbinomial(), data = outlet_data)
 # lme4
-lme4::glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
+glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
 ```
@@
 ```r
-MASS::glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
+require(MASS)
+glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
 ```
@@
 ```r
-brms::brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
-lme4::glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
+brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
+glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
 ```
@@
 ```r
-MASS::glm(y ~ log(x), family = binomial(), data = article_data)
+glm(y ~ log(x), family = binomial(), data = article_data)
 ```
@@
 For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$.
-For the article-level analysis, the four unknown paramters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$.
+For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$.
 The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.
@@
 # The sample_prior argument is optional. But useful for further analysis.
-import_brms <- brms::brm(z~offset(log(n))+(1|k)+log(x_import),
+import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
           data = outlet_data, family = negbinomial(),
@@
 @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval.
-However, there is a general concern about this crediblity level as being unstable for Bayesian analysis [@kruschke2014doing].
+However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
 Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals.
-@mcelreath2020statistical selects 89\% to show the arbitariness of the practice.
+@mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.
 @leeuw:2020:AAT select 90\%.
@@
 The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China.
-While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of infference.
-The Bayesian approach alloows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling witin  0.18 and 0.33*.
+While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
+The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*.
 In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*.
 One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015].
-This example illustrates that a Bayesian approach allows us to interpret the results in a more intutitive way.
+This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.
 
@@
 
-```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy catepillar pattern."}
+```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy caterpillar pattern."}
 require(brms)
@@
 
-Instead of arguing the advatnages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis.
+Instead of arguing the advantages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis.
 The analyses in these extensions are not preregistered.
@@
 # suppose "public" is a binary variable
-import_brms_public <- brms::brm(
+import_brms_public <- brm(
       z~offset(log(n))+(1 + public|k)+log(x_import)*public,
@@
 It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function).
-The trajectories of public broadcastors and for-profit media outlets are similar, indicating no interaction.
+The trajectories of public broadcasters and for-profit media outlets are similar, indicating no interaction.
 
@@
 
-In this paper, we argue the case for using Bayesian multilevel regression analysis to analyse data from comparative content analyses.
+In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative content analyses.
 We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
 Using a Bayesian approach, however, has also clearly some disadvantages.
-Reserachers have to define priors in order to run a Bayesian regression analysis.
-As we could show this limitation does not pose a controversial challenge as weakly informative prios can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
+Researchers have to define priors in order to run a Bayesian regression analysis.
+As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
 If we have prior knowledge it allows us to create even better models.
@@
 Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6525 articles in @esser:2013:C] can be estimated in a reasonable time [^TIME].
+6525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].
 
-[^TIME]: We benchmarked the same model but with a random subset of data of some more "typical" sample sizes.
-A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical computer with 6 cores.
-Although it is comparatively more computational intensive than lme4, the time needed is still reasonable.
+[^TIME]: We benchmarked the same model B1 but with subsets of data of some more "typical" sample sizes.
+A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 6-core computer.
+Although it is comparatively more computational intensive than *lme4*, the time needed is still reasonable.
 

### 2021-04-16 manuscript.rmd
Replace all 'comparative content analysis'

@@
 ---
-title             : "The Bayesian turn in comparative content analysis"
+title             : "The Bayesian turn in comparative communication research"
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 abstract: |
-  Comparative content analysis is a frequently used research design in journalism studies.
-The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative content analysis.
+  Comparative approach such as comparative content analysis is frequently used in journalism studies.
+The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study.
 It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data.
-Bayesian multilevel regression is suggested to be a, and probably, the only, valid analytical approach.
-Using the openly available useNews data and the R package brms, we demonstrate how to apply such approach for the analysis of comparative content analysis.
-We also address common queries of the approach such as choosing the prior distribution and diagnosing the convergence of the model.
+Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach.
+Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply such approach for the analysis of comparative data.
+We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model.
 Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.
 
-keywords          : "Bayesian inference, multilevel model, comparative content analysis, ecological effect"
+keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
 wordcount         : "0"
@@
 
-Comparative content analysis is a frequently used research design in journalism studies.
-Comparative content analysis is used in modeling journalistic culture [e.g.
+Communication research is often comparative, journalism studies are no exception.
+For example, comparative approach is used in modeling journalistic culture [e.g.
 @esser:2013:C], comparative news value research [e.g.
@@
 @wu:2000:SDI;@grasland:2019:I], among others.
-A typical comparative content analysis in journalism research includes news articles from various outlets and usually also from various countries.
+A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries.
 Then the included news articles are coded either manually or automatically.
-Although some comparative content analysis studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g.
+Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g.
 political orientation, online versus offline) and their countries (e.g.
@@
 Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries.
-Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis.
-An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
-Hypothesis-generating comparative content analysis, however, is rare.
+Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research.
+An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
+Hypothesis-generating comparative study, however, is rare.
 Most studies have a confirmatory outlook.
@@
 These approaches violate the underlying assumptions of the statistical analyses.
-It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel.
+It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in multilevel.
 A news article is nested within its media outlet and its media outlet is in turn nested within its country.
@@
 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
-Using the openly available useNews data and the R package brms, we then demonstrate how to apply a Bayesian approach for the analysis of comparative content analysis.
+Using the openly available *useNews* data and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis.
 
@@
 
-In a comparative content analysis, it is easy to incorrectly assume that macro-level independent variables (e.g.
+In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g.
 Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g.
@@
 
-Multilevel modeling is the way to go for analyzing non-atomic data from comparative content analysis. However, the conventional approach for statistical inference makes it not optimal.
+Multilevel modeling is the way to go for analyzing non-atomic data from comparative research. However, the conventional approach for statistical inference makes it not optimal.
 
@@
 
-Comparative content analysis, unlike randomized surveys or randomized media experiments, usually collects all available data.
+Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data.
 In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
@@
 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014-2015.
+
 Census-style studies are not repeatable and thus they generate non-stochastic data.
-In other words, data from comparative content analysis are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
+In other words, data from comparative journalism studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
 P-values and confidence intervals generated do not have the same meaning as those from repeatable studies.
@@
 
-Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis.
+Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative research in our field.
 Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
@@
 @kovic:2017:B;@chan2020high] these studies are not comparative.
-As far as we know, the only available comparative content analysis that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT.
-We believe comparative content analysis fits the use case of Bayesian multilevel regression analysis.
+As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT.
+We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
 Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced].
@@
 
-In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative content analyses.
+In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research.
 We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.

### 2021-04-17 manuscript.rmd
small edits

@@
 Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative research in our field.
-Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
+Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
 Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
-However, for Bayesian models priors have to be chosen by researchers.
+However, for Bayesian models so-called priors have to be chosen by researchers.
 
@@
 More often than not, we do not have any information to set an informative prior (e.g.
-What about a new journal?).
+What about a new journal for which no acceptance rate is yet known?).
 One option is to consult experts or to make an educated guess.
@@
 We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries.
-The dictionaries were applied to the 61 DTMs of all included media outlets.
+The dictionaries were applied to the 61 document-term matrices (format of the provided dataset) of all included media outlets.
 An article is classified as China coverage when at least one dictionary match is detected.
@@
 For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression.
-It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach.
+It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach [@morey:2015].
 It is because disaggregation approach commits atomistic fallacy and MLE approach ignores the non-stochastic nature of the data.
@@
 In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*.
-One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015].
+One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
 This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.

### 2021-04-17 manuscript.rmd
downgrade the author argument to a footnote

@@
 It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in multilevel.
-A news article is nested within its media outlet and its media outlet is in turn nested within its country.
-Theoretically with a large enough sample it can be argued that a news article is nested within authors.
+A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author].
 Such data structure brings two problems: non-atomicity and non-stochasticity.
+
+[^author]: Theoretically with a large enough sample it can be argued that a news article is nested within authors.
 

### 2021-04-17 manuscript.rmd
maintain consistency

@@
 @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p.
-6) and that amounted to 762,095 articles from 9 outlets in the period of 2014-2015.
+6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.
 
@@
 
-We excluded media outlets that contributed <1000 articles in that year.
+We excluded media outlets that contributed <1,000 articles in that year.
 This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated.
@@
 Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic and the presidential election in the US.
-It can be analyzed with this 3-level model.
+It can be analyzed with this three-level model.
 
@@
 
-The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). It seems that there is a global increase in China coverage from 2019 to 2020.
+The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). There is a global increase in China coverage from 2019 to 2020.
 
@@
 Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].
+6,525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].
 

### 2021-04-17 manuscript.rmd
Adding WC; edit bib; ready for DJ
Rename 03 to 030 for better listing

@@
 author: 
-  - name          : "Chung-hong Chan"
+  - name          : "(redacted)"
     affiliation   : "1"
     corresponding : yes
-    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
-    email         : "chung-hong.chan@mzes.uni-mannheim.de"
-  - name          : "Adrian Rauschfleisch"
-    affiliation   : "2"
 
@@
   - id            : "1"
-    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
-  - id            : "2"
-    institution   : "National Taiwan University, Taiwan"
+    institution   : "Planet dust"
 
 authornote: |
-  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
+  (redacted).
   Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/
@@
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
-wordcount         : "0"
+wordcount         : "7509"
 

### 2021-04-18 manuscript.rmd
Revert "Adding WC; edit bib; ready for DJ"
This reverts commit a0871bc6430c2b9168db867bec7e769931d3d811.
Anonymized
Fix horrible grammar of footnote 5

--- 2021-04-17 manuscript.rmd
@@
 [^5]: HDI is one representation of Bayesian credible interval.
-It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility, but some established conventions.
+It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility but some established conventions.
 We choose, like many published works [e.g.
-@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval.
+@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval.
 However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
-Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals.
+Some Bayesians, notably, Andrew Gelman, report very liberal 50\% credible intervals.
 @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.

### 2022-01-20 manuscript.rmd
ICA submission verion

@@
 ---
-title             : "The Bayesian turn in comparative communication research"
+title             : "Bayesian (comparative) journalism studies"
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 abstract: |
-  Comparative approach such as comparative content analysis is frequently used in journalism studies.
+  Comparative approaches such as comparative content analysis are frequently used in journalism studies.
 The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study.
@@
 Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach.
-Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply such approach for the analysis of comparative data.
+Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
 We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model.
@@
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
-wordcount         : "7509"
+wordcount         : "7618"
 
@@
 linenumbers       : no
-mask              : no
+mask              : yes
 draft             : no
@@
 
-This study of ecological effect on individual behaviors has a long tradition in social sciences.
+This study of ecological effects on individual behaviors has a long tradition in social sciences.
 A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
@@
 These approaches violate the underlying assumptions of the statistical analyses.
-It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in multilevel.
+It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
 A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author].
@@
 
-[^author]: Theoretically with a large enough sample it can be argued that a news article is nested within authors.
+[^author]: Theoretically with a large enough data it can be argued that a news article is nested within authors.
 
@@
 The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
-Suppose one wants to study how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China.
-In the following regression equation, let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China).
+Suppose one wants to study a classic news value question of how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China.
+It is related to the news value of "meaningfulness" in @galtung:1965:SFN.
+The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China).
 Suppose there are $m$ news articles where $i = 1,2,\ldots,m$.
@@
 From a statistical standpoint, this approach violates the underlying independence assumption.
-Almost all frequentist statistical tests assume that the observations are independent of each other.
-It is unrealistic to assume articles from the same media outlet are independent: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer.
+Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.).
+Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer.
 Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it.
@@
 
-[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5].
+[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years.
+One could question the necessity of another repetition in this paper.
+The non-atomicity argument might be repetitious but we believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
+356] said-- is still not the default regression approach in communication research.
+For example, as recent as in 2020 some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5].
 Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel].
 We reject this justification because it violates the independence assumption and thus commits atomistic fallacy.
+A fallacious result with less error is still fallacious.
 See also @nezlek:2008:IMM for a criticism of such justification.
@@
 This method is useful when $x$ is the only independent variable, akin @esser:2013:C.
-It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect.
+It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect.
 However, this method still has important drawbacks.
@@
 Second, this method discards a massive amount of information.
-It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g.
+It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
 counting a binary variable).
@@
 Another solution is to use the multilevel model (linear mixed model, or hierarchical model).
-In a multilevel model, the effect on micro-level dependent variable ($y$) is modeled with equations at different levels.
+In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels.
 Using the above example, $y_{ik}$ denotes whether the $i$-th article in the $j$-th country is covering China; $x_{k}$ denotes the trade volume with China of the $k$-th country where the media outlet of $i$-th article is located.
@@
 $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$.
-Instead of a single value, regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group.
+Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group.
 It addresses the problem of clustering of articles by macro-level variables.
@@
 
-Multilevel modeling is the way to go for analyzing non-atomic data from comparative research. However, the conventional approach for statistical inference makes it not optimal.
-
-## Non-stochasticity
-
-*"Statisticians, like artists, have the bad habit of falling in love with their models."* George E.P. Box
-
+Multilevel modeling is the way to go for analyzing non-atomic data from comparative research.
+However, the conventional approach for statistical inference makes it not optimal.
 The conventional approach for statistical inference in multilevel modeling is maximum likelihood estimation (MLE).
 @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e.
-more false positive) and the shrinkage is more severe when the number of macro-level units (e.g.
+more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
 countries) is small.
@@
 
+## Non-stochasticity
+
+*"If Czech history **could** be repeated, we should of course find it desirable to test the other possibility each time and compare the results.
+Without such an experiment, all considerations of this kind remain a game of hypotheses."* [@kundera2020unbearable, emphasis added]
+
 Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is.
-Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from the population.
-Based on this assumption and with just one experiment, we make an estimation about the population.
+Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population.
+Random experiments are assumed to be repeated arbitrarily often.
+Based on this assumption and with just one experiment from the current study, we make an estimation about the population.
 The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e.
 which subjects were randomly sampled from the population.
-Randomized surveys, for examples, are assumed to be repeatable through repeated random sampling of the population.
+Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population.
 Suppose we replicated the same survey for 100 times and we would obtain a slightly different sample every time.
@@
 We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**.
-However, we can say 90 is more probable than says, 0 or 100.
+However, we can say 90 is more probable than 0 or 100.
 
@@
 
-Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative research in our field.
+A common counterargument to this is the classic one from @deming:1941:ICS [p.
+45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3].
+In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation.
+This counterargument could be useful but unlike a regular sample, whose representativeness can be assessed, we can never assess the representativeness of the census with respect to the theoretical superpopulation.
+Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.
+
+Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field.
 Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
 Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
-However, for Bayesian models so-called priors have to be chosen by researchers.
+<!-- However, for Bayesian models so-called priors have to be chosen by researchers.
+-->
 
@@
 
-Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data.
+Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data .
 We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$).
-This can be summarize in the following equation [@gelman2020bayesian]:
+This can be summarized in the following equation [@gelman2020bayesian]:
 
@@
 The $P(X| \theta)$ part is called likelihood function.
-In the $Digital Journalism$ example, the likelihood function is based on rough rules from our experience and thus is not systematic.
-In actual analysis, we need to derive such likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
+In the *Digital Journalism* example, the likelihood function is based on rough rules from our experience and thus is not systematic [^dj].
+In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
 Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
+
+[^dj]: As a side note: we have actually performed the experiment by submitting this paper to *Digital Journalism*. But for pragmatic reasons we cannot report the posterior.
 
@@
 <!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition.
---> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM].
+--> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computers since the mid-1990s [@robert:2011:SHM].
 And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S].
@@
 In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
-More often than not, we do not have any information to set an informative prior (e.g.
-What about a new journal for which no acceptance rate is yet known?).
+Finding previous studies for an informative prior is the logical first thing to do.
+@keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt.
+For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.
+
+For the other six sevenths, one might not have any information to set an informative prior.
 One option is to consult experts or to make an educated guess.
+Expert elicitation is a way to probe how the experts in the field think about the hypotheses.
+A standardized protocol for expert elicitation is available [@hanea:2017:IDE] and there are many software tools available to facilitate the process [^experttools].
+
+[^experttools]: Some examples are the web-based MATCH Uncertainty Elicitation Tool (http://optics.eee.nottingham.ac.uk/match/uncertainty.php) and the R package SHELF.
+
 But one person's expert opinion could be another person's wishful thinking.
-And this perceived subjectivity of specifying priors attracts wide-spread criticism from both statisticians [e.g.
+And this perceived subjectivity of specifying priors by experts’ judgement attracts wide-spread criticism from both statisticians [e.g.
 @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].
@@
 Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB].
-But the influence from prior is greatly weakened, when the data is getting bigger.
-Also, one can select a weakly informative prior [@lemoine:2019:M] which only specifies the possible range of the posterior [^4].
+But the influence from priors is greatly weakened, when the data is getting bigger.
+Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M].
+In this way, one specifies only the possible range of the posterior [^4].
 Some so-called "default weakly informative priors", e.g.
@@
 The outlet-level analysis is an aggregated version of article-level analysis.
-It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with very small data size.
+It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with a very small data size.
 The article-level analysis is used to demonstrate the analysis of a massive three-level dataset.
@@
 
-The useNews is an openly available dataset [@puschmann:2020] that includes media content data from an array of worldwide media outlets from 2019 to 2020.
+The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets .
 The media content data was collected from the MIT MediaCloud and made available as document-term matrices.
@@
 We used only the data from 2019 as the baseline.
-It is important to note that the Hong Kong protests, the 30th anniversary of the Tienanmen Square Protests and the 70th anniversary of the communist regime were in that year.
-Also, it was in the zenith of the US-China trade war.
+It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
+Also, it was at the zenith of the US-China trade war.
 
@@
 The seed dictionaries contain words about Chinese, China, Beijing and Shanghai.
-We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries.
+We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries [^dict_val].
 The dictionaries were applied to the 61 document-term matrices (format of the provided dataset) of all included media outlets.
 An article is classified as China coverage when at least one dictionary match is detected.
+
+[^dict_val]: One might argue our seed dictionaries are not validated.
+We deem that the criterion validity of our dictionary should be built-in.
+Coverage of China, by definition, should mention words about China.
+We also maintain that it is difficult to conduct a human validation of the seed dictionaries because the useNews dataset [@puschmann:2020] doesn’t provide access to the full-length articles.
+Nonetheless, we attempted to conduct such validation by randomly selecting 10 matching and 10 non-matching items for each language.
+In total, 160 items were selected.
+A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the meta data provided in the useNews dataset [@puschmann:2020].
+For some languages, the coder used Google Translate to translate the full text article to English.
+In total, only 138 URLs were still accessible.
+Comparing the ground truth and the human coding, 62 and 70 are true-positive and true-negative cases.
+There are also 5 false-negative and 1 false-positive cases.
+There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases.
+The false-positive case is Korean and that could be due to incorrect tokenization at the MIT Media Cloud’s end.
+The 5 false-negative cases are in Norwegian, Portuguese, and Romanian.
+The content on the website might have changed since MIT Media Cloud collected the data.
+For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM.
+Despite all these caveats, our seed dictionaries have a precision and recall of 98.4% and 92.5% respectively.
+For the purpose of demonstrating regression analysis, this level of accuracy is more than sufficient.
 
@@
 For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression.
-It is important to remind our readers that the results from the three are likely to be similar, but it is not an evidence for the disaggregation approach and the MLE approach are replacement of Bayesian approach [@morey:2015].
-It is because disaggregation approach commits atomistic fallacy and MLE approach ignores the non-stochastic nature of the data.
+It is important to remind our readers that the results from the three are likely to be similar, but it is not evidence for the disaggregation approach and the MLE approach is a replacement of the Bayesian approach [@morey:2015].
+It is because the disaggregation approach commits atomistic fallacy and the MLE approach ignores the non-stochastic nature of the data.
 
@@
 \log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} +  \epsilon_{jk} \\
-\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk} \\
-\end{align}
+\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}\end{align}
 
-In lme4 and brms, the equation is expressed as such:
+The estimand of interest, $\gamma_{01}$, is interpreted as the average unit change in the log rate of China coverage, $\log\frac{z_{jk}}{n_{j}}$, for each unit change in the distance measure of the outlet $k$.
+
+In lme4 and brms, the above equation is expressed as such:
 
@@
 L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
-L_{ijk} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{ijk} \\
+L_{ijk} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{ijk}
 \end{align}
@@
 For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$.
-For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$.
+For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ and $\mu_{0j}$.
 The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.
@@
 Three parameters are important: number of iterations, number of chains and *adapt_delta*.
-It is not some magic numbers that you can plug and play.
+They are not some magic numbers that you can plug and play.
 However, it is in general safe to use the default values, i.e.
@@
 
-[^5]: HDI is one representation of Bayesian credible interval.
-It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility but some established conventions.
+[^5]: HDI is one representation of the Bayesian credible interval.
+It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions.
 We choose, like many published works [e.g.
@@
 It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF].
-The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China.
+The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting of China.
 While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
 The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*.
-In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*.
+In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true estimate of log import volume*.
 One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
@@
 
-We can also use another weakly informative prior to see how our initial choice influence the result.
+We can also use another weakly informative prior to see how our initial choice influences the result.
 We tried another weakly informative prior for the regression coefficients, $\mathcal{t}(1, 0, 0.25)$ [@gelman:2008].
@@
 
-Another approach suggested by @kruschke:2018:RAP, which uses the region of practical equivalence (ROPE), is available from the package bayestestR [@makowski:2019].
+While accepting a null hypothesis is not a feasible option in a frequentist framework, as such a framework has an "inability to gain evidence for the null" [@rouder:2009:B, p.
+226] hypothesis, it is practically possible to  accept a null hypothesis in a Bayesian framework [@kruschke:2018:RAP].
+Bayes factor or the region of practical equivalence (ROPE) could be used to decide to accept the null hypothesis.
+@kruschke:2018:RAP, for example, suggests using $\sigma = \pm 0.1$ as half of small effect size to establish a ROPE.
+However, there is no fixed rule on how to define a ROPE.
+If now 95\% of the HDI for an estimate falls within the ROPE, researchers could accept the null hypothesis for practical purposes.
+A practical application could be with manual content analysis or survey research in communication research if some variables are challenging and costly to measure.
+In a frequentist framework, failing to reject the null hypothesis could wrongly inform researchers to collect more data in subsequent studies to discern between insufficient power [^POWER] or the null is true.
+Instead, ROPE could be used to decide whether, in future studies, more data should be collected to retest the same hypothesis.
+When ROPE provides a strong signal that the null hypothesis is true, it is no longer worthy to collect more of the costly data just to boost the statistical power.
+
+[^POWER]: Statistical power is a frequentist concept specifying the long run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.
+
+The package bayestestR [@makowski:2019] can be used to calculate and visualize the ROPE.
+
+```r
+library(bayestestR)
+rope(import_brms)
+plot(rope(import_brms))
+```
+
+```{r, include = FALSE}
+library(bayestestR)
+fig <- plot(rope(import_brms))
+```
+
+```{r figrope, results = "asis", fig.cap = "The Region of Practical Equivalence and the 95% High Density Interval"}
+fig
+```
+
+The proportion of 95\% HDI falling inside the ROPE is 0\%.
+Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) have no overlap with the ROPE (the shaded region).
+Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided).
+In the current situation, it is very clear that the 95\% HDI falls outside of the ROPE as there is 0\% overlap.
+Similar to the result from *hypothesis()*, there is a practical effect and it is correct to reject the null hypothesis.
+
+However, in another situation when we have a simulated independent variable *noise* that is basically random noise.
+
+```r
+outlet_data$noise <- rnorm(nrow(outlet_data))
+
+noise_brms <- brm(z~offset(log(n))+(1|k)+noise,
+                  data = outlet_data, family = negbinomial(),
+                  control = list(adapt_delta = 0.99),
+                  prior = weaklyinformative_prior,
+                  sample_prior = TRUE)
+rope(noise_brms)
+```
+
+In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%.
+The proportion is quite high but it is not decisive.
+@kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE.
+Accordingly, the current situation of 68\% is "undecided".
+It might be worthwhile to retest the hypothesis with a larger amount of data.
+
+One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g.
+how to determine the ROPE, how wide should the ROPE be, and which level of HDI to use.
+ROPE is also sensitive to the scale of measurement.
+Nonetheless, ROPE can provide much richer information to inform how future studies should be designed.
 
@@
 The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020.
-This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, what open science hopes to enable [@dienlin:2020:AOS].
+This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, which open science hopes to enable [@dienlin:2020:AOS].
+The use of informative prior in replication studies enables us to update our prior beliefs with the new evidence from the replications.
+Priors, replicable or not, will get updated.
 
@@
 The same strategy for handling the clustering of observations in the multilevel modeling can be used.
-We model observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries.
-Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic and the presidential election in the US.
+We model that observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries.
+Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic or the presidential election in the US.
 It can be analyzed with this three-level model.
@@
 Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6,525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].
+6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].
 

### 2022-01-20 04_small_count.R

@@ -37,10 +37,24 @@ weaklyinformative_prior <- c(prior_string("normal(0, 1)", class = "b"), prior_st
 import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import), data = outlet_data, family = negbinomial(), control = list(adapt_delta = 0.99), prior = weaklyinformative_prior, sample_prior = TRUE)
 saveRDS(import_brms, "import_brms.RDS")
 
+## ## the output of the function scale() is a column matrix
+## ## use [,1] to convert it to vector
+## outlet_data$normalized_x_import <- scale(log(outlet_data$x_import))[,1]
+
+## import_brms_norm <- brm(z~offset(log(n))+(1|k)+normalized_x_import, data = outlet_data, family = negbinomial(), control = list(adapt_delta = 0.99), prior = weaklyinformative_prior, sample_prior = TRUE)
+## saveRDS(import_brms_norm, "import_brms_norm.RDS")
+
+set.seed(1010120)
+outlet_data$noise <- runif(nrow(outlet_data))
+## outlet_data$normalized_noise <- scale(outlet_data$noise)[,1]
+
+noise_brms <- brm(z~offset(log(n))+(1|k)+noise, data = outlet_data, family = negbinomial(), control = list(adapt_delta = 0.99), prior = weaklyinformative_prior, sample_prior = TRUE)
+rope(noise_brms_norm) ## 59%
 
 ## svg("fig1.svg")
 ## plot(import_brms)
 ## dev.off()
+
 
 conditional_effects(import_brms)
 

### 2022-01-20 manuscript.rmd
Make room for the WJS example

@@
 Then the included news articles are coded either manually or automatically.
+Surveys in journalism research are often comparative, e.g.
+the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].
+
 Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g.
 political orientation, online versus offline) and their countries (e.g.
-post-communist country) influence the content of news articles.
-For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological.
+post-communist country) influence the content of news articles or behaviours of journalists.
+For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
 It assumes a macro contextual factor (e.g.
 newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g.
-degree of opinion-orientation), namely, the article-level.
+degree of opinion-orientation), namely, the article-level or journalist-level.
 
@@
 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
-Using the openly available *useNews* data and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis.
+Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
 
@@
 
-Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data.
-In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
+Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data.
+In contrast to sampling, these studies are actually doing census of all data.
+There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
 It is especially true for modern large-N studies using automated content analytic techniques.
@@
 -->
+
+Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayiesan approach**.
+The same approach is equally applicable to both non-stochastic and stochastic comparative datasets.
+Therefore, one can analyse both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.
 
@@
 We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
-Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced].
+Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced].
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
@@
 
-# Methods
+The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archtypes of comparative journalism studies.
+The first example is an analysis of a comparative, non-stochastic content analytic dataset.
+The second example is an analysis of a comparative, stochastic survey dataset.
 
-We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis.
+# Example 1: useNews
+
+We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis on a nonstochastic comparative dataset.
 The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage?
@@
 
-### Priors
+## Priors
 
@@
 
-# Regression results
+## Regression results
 
@@
 
-## Diagnosis of convergence
+### Diagnosis of convergence
 
@@
 
-## Further diagnostics
+### Further diagnostics
 
@@
 
-# Discussion
+## Extentions
 
-Instead of arguing the advantages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis.
-The analyses in these extensions are not preregistered.
+We propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.
 
-## Extension #1: Hypothesis testing
+### Extension #1: Hypothesis testing
 
@@
 
-## Extension #2: Cross-level interaction
+### Extension #2: Cross-level interaction
 
@@
 
-## Extension #3: Current study as the informative prior for the next study
+### Extension #3: Current study as the informative prior for the next study
 
@@
 
+# Example 2: The Worlds of Journalism study
+
+Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis. In this example, the same approach is applied to a stochastic dataset from a randomize survey.
+
 # Conclusion
@@
 In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research.
-We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
+We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
 Using a Bayesian approach, however, has also clearly some disadvantages.
@@
 Estimating a Bayesian regression model is a computationally demanding task.
-It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1).
+It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 1, Model B1).
 Still, eventually it worked and typical studies in comparative journalism research [e.g.

### 2022-01-31 manuscript.rmd
Add WJS example

@@
 linenumbers       : no
-mask              : yes
+mask              : no
 draft             : no
@@
 
-Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis. In this example, the same approach is applied to a stochastic dataset from a randomize survey.
+Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis.
+In this example, the same approach is applied to a stochastic dataset from a randomize survey.
+The starting point of this example is the recent study by @hamada:2021:DJA.
+Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*.
+
+It is important to point out that the study is actually a replication.
+The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkable similar title to that of @hamada:2021:DJA.
+The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.
+
+Interestingly, the analytical approaches are also similar in the two studies.
+The study by @reich:2013:DJP contains multiple regression models on how journalist-level characters predict perceived professional autonomy.
+However, for country-level predictors such as Index of Democracy, @reich:2013:DJP apply an aggregated approach due to "methodological considerations" of "includ[ing] substantive country-level predictors in an OLS regression" (p.
+146).
+Effectively, the analysis boils down to aggregating the perceived professional autonomy of all journalists into mean values according to baskets of Index of Democracy and then comparing those mean values by ANOVA.
+The subsequent study by @hamada:2021:DJA applies the same aggregated approach by studying the bivariate correlation between the mean perceived professional autonomy of all journalists in a country and the Index of Democracy of a country.
+
+There are two weaknesses of the aggregated approach.
+First, a massive amount of information at the author-level was discarded and cannot leverage the hierarchical structure of the data.
+As showed in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy.
+Taking the aggregated approach assumes that all of these author-level variables are homogeneous.
+This assumption could create spurious correlation when the distribution of author-level variables is associated with contextual factors, e.g.
+Index of Democracy.
+Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the more perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g.
+the average level of perceived professional autonomy of journalists in a country).
+Interpreting the macro-level association wrongly at the micro-level leads to ecological fallacy.
+
+## Bayesian analysis of WJS
+
+Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data.
+Bayesian multilevel regression is probably the only valid approach.
+First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance at the journalist-level perceived professional autonomy.
+Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replication clearer.
+
+From the model 4 in @reich:2013:DJP, we know that the standardized beta coefficients for the variables rank and professional experience are .15 and .07 respectively.
+Unfortunately, the associated standard errors (or standard deviations) were not reported but only asterisks representing statistical significance (p < 0.001 for rank, p < 0.01 for professional experience).
+We estimated the maximum standard deviation based on the significance level.
+For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving [^wald]:
+
+\begin{align}
+Pr(\frac{\beta'_{1}}{\sigma_{\beta'_{1}}}) &= \frac{0.001}{2} \sim \mathcal{N}(0, 1) \\
+\frac{\beta'_{1}}{\sigma_{\beta'_{1}}} &= 3.29 \\
+\frac{0.15}{\sigma_{\beta'_{1}}} &= 3.29 \\
+\sigma_{\beta'_{1}} &= 0.045
+\end{align}
+
+or in R
+
+```r
+beta_d_1 <- 0.15
+sig_level <- 0.001
+beta_d_1 / abs(qnorm(sig_level / 2))
+```
+
+The above information can be used as an informative prior of the current analysis.
+Unfortunately, the ANOVA result from @reich:2013:DJP cannot be used as the prior and we still need to use weakly informative prior.
+However, @reich:2013:DJP suggest that the relationship between Index of Democracy and perceived professional autonomy is in convex "J shape", with the average perceived professional autonomy of journalists in authoritarian regimes (the lowest end of democracy performance) being higher than those in hybrid regimes (3.92 vs 3.65).
+We can incorporate this prior information into our model by modeling a cubic relationship between Index of Democracy and perceived professional autonomy.
+Similar to the general procedure of conducting polynomial regression, we also create a parsimonious model assuming only a linear relationship to study whether the cubic regression improves the model fit.
+In other words, whether the relationship is really in convex "J shape" is studied [^jshape].
+
+```{r, echo = FALSE}
+pts_tab <- readRDS("pts_tab.RDS")
+```
+
+Another advantage of taking a Bayesian multilevel regression approach rather than the bivariate approach as in @reich:2013:DJP is the possibility to adjust for the possible confounding effects of other marco-level variables.
+For example, GDP per capita (according to World Bank) is moderately correlated with Index of Democracy (r = `r cor(pts_tab$eiu, pts_tab$gdppc, use = "complete")`).
+The correlation between Index of Democracy and perceived professional autonomy found by @reich:2013:DJP could be spurious and the GDP per capita were the actual determinant of perceived professional autonomy.
+We can adjust for the effect of GDP per capita by entering it also as an independent variable.
+The data can also provide such variance because there are countries with high GDP per capita but with low democracy (e.g.
+UAE and Qatar) and vice versa (e.g.
+Botswana and India).
+
+In order to make the result from this replication comparable to that of @reich:2013:DJP, we also calculate the standardized regression coefficients, i.e.
+all variables are mean-centered before entering into the regression model.
+
+The following is the complete code to construct the two Bayesian model. The cubic relationship can be set using the `I()` function.
+
+```r
+require(tidyverse)
+
+informative_prior <- c(prior_string("normal(0, 1)", class = "b"),
+                       prior_string("normal(0, 1)", class = "Intercept"),
+                       prior_string("normal(0.14, 0.045)",
+                                    class = "b", coef = "EXPRNCE"),
+                       prior_string("normal(0.07, 0.027)",
+                                    class = "b", coef = "RANK"))
+
+std <- function(x){
+  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
+}
+## eiu is Index of Democracy, gdppc is GDP per capita (log)
+set.seed(12121)
+wjs %>%
+    select(ppa, EXPRNCE, RANK, GENDER, UNI_EDU, UNI_EDU, eiu, gdppc, COUNTRY) %>%
+    mutate(gdppc = log(gdppc), COUNTRY = as.factor(COUNTRY)) %>%
+    mutate_at(vars(ppa:gdppc), std) -> wjs_processed
+brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
+    data = wjs_processed, cores = 4, iter = 3000, prior = informative_prior,
+        sample_prior = TRUE) -> ppa_mod
+
+set.seed(12121)
+## iter needs to set larger to ensure convergence
+brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + I(eiu^3) + gdppc + (1|COUNTRY),
+    data = wjs_processed, cores = 4, iter = 4000, prior = informative_prior,
+    sample_prior = TRUE) -> ppa_qmod
+```
+
+By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34).
+It is not only statistical significant in the traditional sense but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
+It supports @hamada:2021:DJA's h2a, but our model does that without the problem of aforementioned ecological fallacy and with adjustment for other potential confounders.
+
+Regarding the possible convex "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194).
+By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not convex "J shape".
+Journalists in countries scored a lower Index of Democracy have also the lowest perceived professional autonomy.
+
+```{r fig5, echo = FALSE, fig.cap = 'Conditional effects plot showing no convex "J shape" relationship between perceived professional autonomy and Index of Democracy.'}
+x <- readRDS("qmod_condit.RDS")
+x$`eiu` + xlab("Index of Democracy (mean-centered)") + ylab("Perceived professional autonomy (mean-centered)") + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
+```
+
+[^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported.
+And t-distribution approximates z-distribution asymptotically when df gets larger.
+
+[^jshape]: Actually, the replication by @hamada:2021:DJA has shown that the relationship is not in such convex J shape. But we were assumed to be in the time point before such replication.
 

### 2022-01-31 scrape_eiu.R

@@ -1,0 +1,8 @@
+require(rvest)
+
+eiu_raw <- read_html("https://en.wikipedia.org/wiki/Democracy_Index")
+
+eiu <- html_table(eiu_raw)[[6]]
+
+eiu %>% select(3, `2012`, `2013`, `2014`, `2015`, `2016`) %>% rename(country = `Country`, e12 = `2012`, e13 = `2013`, e14 = `2014`, e15 = `2015`, e16 = `2016`) %>% rowwise() %>% mutate(eiu = mean(c(e12, e13, e14, e15, e16))) %>% select(country, eiu) %>% saveRDS(here::here("data/eiu.RDS"))
+

### 2022-01-31 wjs.R

@@ -1,0 +1,58 @@
+require(rio)
+require(tidyverse)
+require(brms)
+
+wjs_raw <- haven::read_sav("data/WJS2 open V4-02 030517.sav", encoding = "latin1") %>% tibble::as_tibble()
+
+## wjs_raw %>% count(COUNTRY) %>% mutate(COUNTRY_NAME = as_factor(COUNTRY)) %>% rio::export("wjs_countries.csv")
+
+pts <- rio::import("data/PTS-2021.xlsx") %>% tibble::as_tibble() %>% filter(Year == 2017) %>% select(Country, PTS_A, PTS_H, PTS_S) %>% mutate(PTS_A = as.numeric(PTS_A), PTS_H = as.numeric(PTS_H), PTS_S = as.numeric(PTS_S)) %>% rowwise() %>% mutate(PTS = median(c(PTS_A, PTS_H, PTS_S), na.rm = TRUE)) %>% ungroup %>% filter(!is.na(PTS)) %>% select(Country, PTS) %>% mutate(Country = recode(Country, `Korea, Republic of` = "South Korea", `Tanzania, United Republic of` = "Tanzania", `United Arab Emirates` = "UAE", `United Kingdom` = "UK", `United States` = "USA", `Russian Federation` = "Russia", `Moldova, Republic of` = "Moldova"))
+
+eiu <- readRDS(here::here("data/eiu.RDS")) %>% ungroup %>% mutate(country = recode(country, `United Arab Emirates` = "UAE", `United Kingdom` = "UK", `United States` = "USA"))
+
+gdp <- rio::import("data/API_NY.GDP.PCAP.CD_DS2_en_csv_v2_3469501.csv", skip = 5) %>% tibble::as_tibble()
+
+gdp_r1 <- rio::import("data/API_NY.GDP.PCAP.CD_DS2_en_csv_v2_3469501.csv", skip = 4)[1,] %>% unlist %>% as.vector
+
+colnames(gdp) <- gdp_r1
+
[…]

### 2022-01-31 wjs2.R

@@ -1,0 +1,6 @@
+require(brms)
+
+x <- readRDS("ppa_qmod.RDS")
+qmod_condit <- plot(conditional_effects(x, effects = "eiu", ask = FALSE, plot = FALSE))
+
+saveRDS(qmod_condit, "qmod_condit.RDS")

### 2022-02-07 021_val_dict.R
Add dictionary validation script

@@ -1,0 +1,50 @@
+require(quanteda)
+require(tidyverse)
+
+mc <- readRDS(here::here("data/usenews.mediacloud.2019.rds"))
+wm <- readRDS(here::here("data/usenews.mediacloud.wm.2019.rds"))
+
+## dfm_lookup(wm[[1]], dictionary(list(China = c("China"))))
+## saveRDS(wm[[1]], "NYT_2019.RDS")
+
+gen_overview <- function(i, wm) {
+    x <- wm[[i]]
+    docvars(x) %>% count(language, sort = TRUE) %>% pull(language) -> langs
+    lang <- langs[1]
+    media <- unique(docvars(x, 'media_name'))
+    n <- nrow(docvars(x))
+    tibble(i = i, media = media, lang = lang, n = n)
+}
+
+
+media1k <- rio::import("media1k.csv")
+
+china_dict <- dictionary(file = "chinese.yml")
+
+cal_china <- function(media_id, media_lang, wm, china_dict) {
+    print(media_id)
+    ## weird bug of read_yaml treating "no" as FALSE
+    dict_id <- which(media_lang == c("en", "no", "es", "ro", "de", "nl", "ko", "pt"))
+    dfm_lookup(wm[[media_id]], china_dict[dict_id], levels = 1) %>% convert(to = "data.frame") %>% pull(2) -> res
+    tibble(url = docvars(wm[[media_id]])$url, title = docvars(wm[[media_id]])$title, media_id = media_id, media_lang = media_lang, china = (res != 0))
+}
+
+res <- map2_dfr(media1k$i, media1k$lang, cal_china, wm = wm, china_dict = china_dict)
+
+set.seed(121212)
+res %>% group_by(media_lang, china) %>% sample_n(10) %>% mutate(id = row_number(), ran = rnorm(n = 10)) %>% ungroup %>% arrange(media_lang, ran) -> content_to_be_coded
+
+saveRDS(content_to_be_coded, "content_to_be_coded.RDS")
+
+content_to_be_coded %>% select(-china, -ran) %>% rio::export("content_to_be_coded.xlsx")
+
+gh <- readRDS("content_to_be_coded.RDS")
+x <- rio::import("WOS - China Dictionary Validation.csv") %>% tibble::as_tibble()
+
+
+table(gt = gh$china, coded = x$coded_china)
+require(ROCR)
+
[…]

### 2022-02-07 extension.rmd
Move extensions and LOO to `extension.rmd`

--- 2022-01-20 manuscript.rmd
@@
 ---
-title             : "Bayesian (comparative) journalism studies"
+title             : "Appendix to \"Bayesian (comparative) journalism studies\""
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 
-authornote: |
-  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
-  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/
-
-abstract: |
-  Comparative approaches such as comparative content analysis are frequently used in journalism studies.
-The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study.
-It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data.
-Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach.
-Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
-We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model.
-Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.
-
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
@@
 library("papaja")
+require(brms)
+import_brms <- readRDS("import_brms.RDS")
 ```
@@
 
-*"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM
+# Validation of the seed dictionaries
 
-Communication research is often comparative, journalism studies are no exception.
-For example, comparative approach is used in modeling journalistic culture [e.g.
-@esser:2013:C], comparative news value research [e.g.
-@burggraaff:2017:T;@wilke:2012], news flow research [e.g.
-@wu:2000:SDI;@grasland:2019:I], among others.
-A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries.
-Then the included news articles are coded either manually or automatically.
-Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g.
-political orientation, online versus offline) and their countries (e.g.
-post-communist country) influence the content of news articles.
-For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content in these hypotheses is assumed to be ecological.
-It assumes a macro contextual factor (e.g.
-newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g.
-degree of opinion-orientation), namely, the article-level.
-
-This study of ecological effects on individual behaviors has a long tradition in social sciences.
-A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
-Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries.
-Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research.
-An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
-Hypothesis-generating comparative study, however, is rare.
-Most studies have a confirmatory outlook.
-As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects.
-In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
-In @wu:2000:SDI, multiple stepwise regression was used.
-These approaches violate the underlying assumptions of the statistical analyses.
-It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
-A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author].
-Such data structure brings two problems: non-atomicity and non-stochasticity.
-
-[^author]: Theoretically with a large enough data it can be argued that a news article is nested within authors.
-
-In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
-While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p.
-121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
-Using the openly available *useNews* data and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis.
-
-## Non-atomicity
-
-*"When it comes to regression, multilevel regression deserves to be the default approach"* @mcelreath2020statistical [p. 356]
-
-It is perhaps well-known what ecological fallacy is.
-We commit ecological fallacy, when we make inference at micro-level (e.g.
-Eating more chocolate makes one cleverer) based on macro-level data (e.g.
-the correlation between countries' chocolate consumption and countries' number of Nobel winners).
-The reverse of ecological fallacy, i.e.
-making inference at macro-level based on micro-level data, is equally fallacious.
-This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].
-
-In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g.
-Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g.
-the  degree of opinion-orientation).
-The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
-Suppose one wants to study a classic news value question of how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China.
-It is related to the news value of "meaningfulness" in @galtung:1965:SFN.
-The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China).
-Suppose there are $m$ news articles where $i = 1,2,\ldots,m$.
-
-\begin{align}
-  y_{i} = \beta_{0} + \beta_{1} x_{i} + \epsilon_{i}
-\end{align}
-
-This method is the so-called "disaggregation approach".
-From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel].
-From a statistical standpoint, this approach violates the underlying independence assumption.
-Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.).
-Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer.
-Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it.
-The choice of media outlets or countries are almost always not randomly selected.
-[^1] This sampling approach makes the independence assumption even more fragile.
-
-[^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa.
-
-Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g.
-@clarke:2008:W;@chen:2012:IIL].
-The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis.
-[^2]
-
-[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years.
-One could question the necessity of another repetition in this paper.
-The non-atomicity argument might be repetitious but we believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
-356] said-- is still not the default regression approach in communication research.
-For example, as recent as in 2020 some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5].
-Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel].
-We reject this justification because it violates the independence assumption and thus commits atomistic fallacy.
-A fallacious result with less error is still fallacious.
-See also @nezlek:2008:IMM for a criticism of such justification.
-
-There are two solutions to this.
-The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable.
-Suppose there are $n$ countries in the above example.
-One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$.
-Then, we can do a count-based regression with a regression equation like so:
-
-\begin{equation}
-  \label{eq:2}
-  \log{z_{k}} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
-\end{equation}
-
-Using this aggregation method, the unit of analysis effectively switches from article to country.
-This method is useful when $x$ is the only independent variable, akin @esser:2013:C.
-It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect.
-However, this method still has important drawbacks.
-First, it cannot be used for data with more than two levels.
-In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogeneous and the information about media outlets was discarded.
-Second, this method discards a massive amount of information.
-It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
-counting a binary variable).
-For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H].
-Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$).
-Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g.
-$n$) is large.
-It is also useful to collapse micro-levels (e.g.
-article-level) that are not useful in answering one’s research questions.
-
-Another solution is to use the multilevel model (linear mixed model, or hierarchical model).
-In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels.
-Using the above example, $y_{ik}$ denotes whether the $i$-th article in the $j$-th country is covering China; $x_{k}$ denotes the trade volume with China of the $k$-th country where the media outlet of $i$-th article is located.
-
-\begin{align}
-  y_{ik} &= \beta_{0} + \epsilon_{ik} \\
-  \beta_{0} &= \gamma_{00} + \gamma_{01} x_{k} + \mu_{0k}
-\end{align}
-
-In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average.
-It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e.
-$\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$.
-Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group.
-It addresses the problem of clustering of articles by macro-level variables.
-This model is called the varying-intercept model and is used frequently in social science research.
-We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.
-
-The benefit of using multilevel modeling lies in its flexibility in handling multi-level data.
-Suppose we also want to consider the clustering of articles around $o$ different media outlets in the above example and $j$-th media outlet is the media outlet of the $i$-th article, where $j = 1,\ldots, o$.
-The multilevel regression equations are rewritten as:
-
-\begin{align}
-y_{ijk} &= \pi_{0} + \epsilon_{ijk} \\
-\pi_{0} &= \beta_{00} + \mu_{0j} \\
-\beta_{00} &= \gamma_{000} + \mu_{00k} + \gamma_{001} x_{k}
-\end{align}
-
-This flexibility is demonstrated in the study by @rinke:2016:ISB.
-He studied the likelihood of opinion justification in 1559 utterances nested in 329 news items, which were in turn nested in 101 news broadcasts.
-Multilevel logistic regression was used to model the natural three-level hierarchy of his data.
-
-Multilevel modeling is the way to go for analyzing non-atomic data from comparative research.
-However, the conventional approach for statistical inference makes it not optimal.
-The conventional approach for statistical inference in multilevel modeling is maximum likelihood estimation (MLE).
-@stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e.
-more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
-countries) is small.
-@stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF;@bryan:2015:MMC].
-Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons.
-Our argument is more in line with @western:1994:BIC.
-
-## Non-stochasticity
-
-*"If Czech history **could** be repeated, we should of course find it desirable to test the other possibility each time and compare the results.
-Without such an experiment, all considerations of this kind remain a game of hypotheses."* [@kundera2020unbearable, emphasis added]
-
-Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is.
-Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population.
-Random experiments are assumed to be repeated arbitrarily often.
-Based on this assumption and with just one experiment from the current study, we make an estimation about the population.
-The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e.
-which subjects were randomly sampled from the population.
-Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population.
-Suppose we replicated the same survey for 100 times and we would obtain a slightly different sample every time.
-We then calculated the 90\% confidence interval of the mean for each of these 100 surveys.
-We should anticipate that more or less 90 out of these 100 confidence intervals would include the true mean of the population.
-We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**.
-However, we can say 90 is more probable than 0 or 100.
-
-Comparative research in journalism studies, unlike randomized surveys or randomized media experiments, usually collects all available data.
-In contrast to sampling, these studies are actually doing census of all data and there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
-It is especially true for modern large-N studies using automated content analytic techniques.
-@burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p.
-6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.
-
-Census-style studies are not repeatable and thus they generate non-stochastic data.
-In other words, data from comparative journalism studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
-P-values and confidence intervals generated do not have the same meaning as those from repeatable studies.
-According to @western:1994:BIC [p.
-413], these values from non-stochastic data "lack meaning even as abstract propositions".
-
-A common counterargument to this is the classic one from @deming:1941:ICS [p.
-45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3].
-In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation.
-This counterargument could be useful but unlike a regular sample, whose representativeness can be assessed, we can never assess the representativeness of the census with respect to the theoretical superpopulation.
-Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.
-
-Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field.
-Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
-Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
-<!-- However, for Bayesian models so-called priors have to be chosen by researchers.
--->
-
-## Bayesian analysis
-
-*"PROBABILITY DOES NOT EXIST."* Bruno de Finetti
-
-What is the probability for this paper being accepted by *Digital Journalism*?
-Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
-It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*.
-Instead, we assert before submission that this paper has a probability of 24% for being accepted.
-That is the published acceptance rate from *Digital Journalism*’s website.
-After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%.
-After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%.
-After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%.
-If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
-
-Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data .
-We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$).
-This can be summarized in the following equation [@gelman2020bayesian]:
-
-\begin{align}
-        P(\theta | X) \propto  P(\theta) P(X| \theta)
-\end{align}
-
-The $P(X| \theta)$ part is called likelihood function.
-In the *Digital Journalism* example, the likelihood function is based on rough rules from our experience and thus is not systematic [^dj].
-In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
-Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
-
-[^dj]: As a side note: we have actually performed the experiment by submitting this paper to *Digital Journalism*. But for pragmatic reasons we cannot report the posterior.
-
-We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount.
-The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper.
-<!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition.
---> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computers since the mid-1990s [@robert:2011:SHM].
-And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S].
-R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users.
-But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE.
-Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.
-
-Part 3 (Prior) is arguably the most controversial part of Bayesian analysis.
-In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
-Finding previous studies for an informative prior is the logical first thing to do.
-@keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt.
-For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.
-
-For the other six sevenths, one might not have any information to set an informative prior.
-One option is to consult experts or to make an educated guess.
-Expert elicitation is a way to probe how the experts in the field think about the hypotheses.
-A standardized protocol for expert elicitation is available [@hanea:2017:IDE] and there are many software tools available to facilitate the process [^experttools].
-
-[^experttools]: Some examples are the web-based MATCH Uncertainty Elicitation Tool (http://optics.eee.nottingham.ac.uk/match/uncertainty.php) and the R package SHELF.
-
-But one person's expert opinion could be another person's wishful thinking.
-And this perceived subjectivity of specifying priors by experts’ judgement attracts wide-spread criticism from both statisticians [e.g.
-@efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].
-
-Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB].
-But the influence from priors is greatly weakened, when the data is getting bigger.
-Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M].
-In this way, one specifies only the possible range of the posterior [^4].
-Some so-called "default weakly informative priors", e.g.
-$\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].
-The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).
-
-[^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised.
-
-## Bayesian communication research
-
-*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
-19]
-
-Bayesian analysis is still a minority statistical method in social sciences.
-It is reasonable to say that Bayesian analysis is extremely rare in our field.
-Although some communication researchers adopted the method [e.g.
-@kovic:2017:B;@chan2020high] these studies are not comparative.
-As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT.
-We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
-Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced].
-As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
-The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
-
-# Methods
-
-We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis.
-The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage?
-In other words, we studied the ecological effect of the distance from China on the frequency of China coverage.
-Several distance measures were used to formulate our pre-registered hypotheses: physical distance between two capitals, trade volume between two countries, and cultural distance between two societies.
-
-For demonstrative purposes, our analysis was separated into two levels: outlet-level analysis and article-level analysis.
-The outlet-level analysis is an aggregated version of article-level analysis.
-It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with a very small data size.
-The article-level analysis is used to demonstrate the analysis of a massive three-level dataset.
-
-## Data
-
-The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets .
-The media content data was collected from the MIT MediaCloud and made available as document-term matrices.
-
-We used only the data from 2019 as the baseline.
-It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
-Also, it was at the zenith of the US-China trade war.
-
-We excluded media outlets that contributed <1,000 articles in that year.
-This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated.
-In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included.
-These 61 media outlets contributed 1,525,871 articles.
-
-In the outlet-level analysis, the data has 61 rows and each row represents a media outlet.
-The data contains a count of articles covering China ($z$), total number of articles ($n$), country of the outlet($k$), and distance measures ($x$).
-
-In the article-level analysis, the data has 1,525,871 rows and each row represents an article.
-The data contains a binary dependent variable of China coverage ($y$), media outlet($j$), country of the outlet($k$), and distance measures ($x$).
-
-## Coverage of China
-
-A dictionary-based approach was used.
-The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis.
-The seed dictionaries contain words about Chinese, China, Beijing and Shanghai.
-We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries [^dict_val].
-The dictionaries were applied to the 61 document-term matrices (format of the provided dataset) of all included media outlets.
-An article is classified as China coverage when at least one dictionary match is detected.
-
-[^dict_val]: One might argue our seed dictionaries are not validated.
+One might argue our seed dictionaries are not validated.
 We deem that the criterion validity of our dictionary should be built-in.
@@
 
-<!-- ```{r, echo = FALSE} -->
-<!-- Language <- c("English", "German", "Spanish", "Romanian", "Korean", "Portugese", "Norwegian", "Dutch") -->
-
-<!-- Lexicon <- c("chinese, china, beijing, shanghai", "chinesisch*, chinesin*, chinese*, china*, peking, shanghai", "chino*, china*, pekin, shanghái", "chinez*, china, beijing, shanghai", "중국인, 중화, 중국, 베이징, 북경, 상하이, 상해", "chinês, chines*, china, pequim, xangai", "kineser*, kinesar*, kinesisk, kina, beijing, shanghai", "chinezen, chinees*, chinezin*, chines*, china, peking, beijing, sjanghai, shanghai") -->
-<!-- papaja::apa_table(data.frame(Language, Lexicon), caption = "Dictionaries used for detecting China coverage") -->
-<!-- ``` -->
-
-## Distance measures
-
-Several distance measures were used as the independent variable to test our central research questions: physical distance, trade volume, and cultural distance.
-Physical distance is calculated as the Great-circle distance between Beijing and the capital of the hosting city of the media outlet (e.g.
-Bucharest).
-The volumes of import to and export from China with the host country of a media outlet was extracted from the 2019 edition of China Statistical Yearbook (http://www.stats.gov.cn/tjsj/ndsj/2019/indexeh.htm).
-Cultural distance from China to the host country of a media outlet was extracted from culturaldistance.com, which was calculated using the data from World Value Survey with the algorithm from @bell:2009:C.
-All of these distance measures were log-transformed, because previous studies showed the relationship between news coverage and these distance measures is not linear [@grasland:2019:I;@wu:2000:SDI].
-
-## Modeling
-
-For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression.
-It is important to remind our readers that the results from the three are likely to be similar, but it is not evidence for the disaggregation approach and the MLE approach is a replacement of the Bayesian approach [@morey:2015].
-It is because the disaggregation approach commits atomistic fallacy and the MLE approach ignores the non-stochastic nature of the data.
-
-### Outlet-level analysis
-
-We used negative binomial regression for this analysis.
-Media outlets are nested in countries (e.g.
-*Der Standard* and *Österreichischer Rundfunk* are nested in Austria).
-Thus, a country-based variance is added ($\mu_{0k}$).
-We also added $\log{n_{j}}$ as an offset value.
-An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation \@ref(eq:2).
-Effectively, we modeled the *rate* of China coverage.
-Applying the same notation under the introduction section, the multilevel regression equations are:
-
-\begin{align}
-\log{z_{jk}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \log{n_j} + \epsilon_{jk} \\
-\log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} +  \epsilon_{jk} \\
-\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}\end{align}
-
-The estimand of interest, $\gamma_{01}$, is interpreted as the average unit change in the log rate of China coverage, $\log\frac{z_{jk}}{n_{j}}$, for each unit change in the distance measure of the outlet $k$.
-
-In lme4 and brms, the above equation is expressed as such:
-
-```r
-require(brms)
-require(lme4)
-# brms
-brm(z ~ offset(log(n)) + (1|k)+log(x),
-          family = negbinomial(), data = outlet_data)
-# lme4
-glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
-```
-
-In the disaggregation case, the multilevel structure is ignored and the regression equation becomes:
-
-\begin{align}
-\log\frac{z_{jk}}{n_{j}} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
-\end{align}
-
-In MASS, it is expressed as such:
-
-```r
-require(MASS)
-glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
-```
-
-We named the models with different independent variables as model A1-4 respectively (A1: log import volume; A2: log export volume; A3: log physical distance; A4: log cultural distance).
-
-### Article-level analysis
-
-We used logistic regression for this analysis.
-Due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.
-
-In this analysis, an article is nested in its media outlet.
-The media outlet is in turn nested in its country.
-Two variance terms ($\mu_{0j}$ and $\mu_{00k}$) are needed.
-The multilevel regression equations are:
-
-\begin{align}
-p_{ijk} &= Pr(y_{ijk} = 1) \\
-L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
-L_{ijk} &= \pi_{0} + \epsilon_{ijk} \\
-\pi_{0} &= \beta_{00} + \mu_{0j} \\
-\beta_{00} &= \gamma_{000} + \mu_{00k} + \gamma_{001} x_{k}
-\end{align}
-
-Or in lme4/brms code:
-
-```r
-brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
-glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
-```
-
-In the disaggregation case, the multilevel structure is ignored and the regression equations become:
-
-\begin{align}
-p_{ijk} &= Pr(y_{ijk} = 1) \\
-L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
-L_{ijk} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{ijk}
-\end{align}
-
-In MASS, it is expressed as such:
-
-```r
-glm(y ~ log(x), family = binomial(), data = article_data)
-```
-
-We named this model as model B1.
-
-### Priors
-
-For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$.
-For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ and $\mu_{0j}$.
-The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.
-
-Usually, the first step for choosing priors is to review previous studies and look for possible values to be used as our informative priors.
-Although @wu:2000:SDI is a possible reference point, we select not to use this because China was not studied.
-Also, the modeling technique was quite different from the current one.
-
-In this analysis, we used weakly informative priors suggested by @lemoine:2019:M.
-
-For regression coefficients, e.g.
-$\gamma_{00}$, we used a normal distribution of $\mathcal{N}(0, 1)$.
-For variance terms, e.g.
-$\mu_{0k}$, a student t-distribution of $\mathcal{t}(3, 0, 2.5)$ was used.
-A gamma distribution of $\mathcal{Gamma}(0.01, 0.01)$ was used for the shape parameter $\phi$.
-
-All, except the prior for regression coefficients, are default priors suggested by *brms*. The prior can be set with the following R code.
-
-```r
-weaklyinformative_prior <- c(prior_string("normal(0, 1)",
-                                          class = "b"),
-                             prior_string("normal(0, 1)",
-                                          class = "Intercept"))
-# The sample_prior argument is optional. But useful for further analysis.
-import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
-          data = outlet_data, family = negbinomial(),
-          prior = weaklyinformative_prior, sample_prior = TRUE)
-import_brms
-```
-
-### Other parameters
-
-Other parameters for Bayesian multilevel regression analysis control how the MCMC should be performed.
-Three parameters are important: number of iterations, number of chains and *adapt_delta*.
-They are not some magic numbers that you can plug and play.
-However, it is in general safe to use the default values, i.e.
-number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence.
-*brms* is smart enough to give suggestions on how to adjust these three values.
-Nonetheless, we provide a short guide on how to diagnose convergence.
-
-# Regression results
-
-Table \@ref(tab:t1) shows a summary of all models from outlet-level analysis using three different ways of modeling.
-The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$).
-It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution.
-By default, *brms* displays the mean and the 95\% high density interval (HDI).
-[^5] These two values represent the point and interval estimates of the regression coefficient.
-
-[^5]: HDI is one representation of the Bayesian credible interval.
-It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions.
-We choose, like many published works [e.g.
-@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval.
-However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
-Some Bayesians, notably, Andrew Gelman, report very liberal 50\% credible intervals.
-@mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.
-@leeuw:2020:AAT select 90\%.
-
-Consistently, point estimates are remarkably similar.
-Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods.
-It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF].
-The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting of China.
-While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
-The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*.
-In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true estimate of log import volume*.
-One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
-This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.
-
-Table: (\#tab:t1) Point and interval estimates from outlet-level analysis using three different analytic strategies: Disaggregation approach, multilevel modeling using MLE and Bayesian multililevel modeling
-
-| Model                           | Disaggregate ($\beta_{1}$, 95\% CI) | MLE ($\gamma_{01}$, 95\% CI) | Bayesian ($\gamma_{01}$, 95\% HDI) |
-|:--------------------------------|:------------------------------------|------------------------------|------------------------------------|
-| Model A1: Log import volume     | 0.25 (0.18, 0.33)                   | 0.25 (0.18, 0.33)            | 0.25 (0.18, 0.33)                  |
-| Model A2: Log export volume     | 0.22 (0.14, 0.30)                   | 0.22 (0.13, 0.31)            | 0.22 (0.11, 0.33)                  |
-| Model A3: Log Physical distance | -0.02 (-0.34, 0.24)                 | -0.10 (-0.55, 0.31)          | -0.12 (-0.63, 0.39)                |
-| Model A4: Log Cultural distance | -0.45 (-1.26, 0.34)                 | -0.60 (-1.80, 0.55)          | -0.62 (-2.12, 0.78)                |
-
-Model B1 confirms the above again (Table \@ref(tab:t2) ). Therefore, both article- and outlet-level analyses arrive at the same conclusion.
-
-<!-- ```{r t2, results = "asis"} -->
-<!-- ### TODO: to prim it further -->
-<!-- require(brms) -->
-<!-- require(parameters) -->
-<!-- require(dplyr) -->
-<!-- article_level <- readRDS("import_logit.RDS") -->
-<!-- article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res -->
-
-<!-- res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2) -->
-<!-- ``` -->
-
-Table: (\#tab:t2) Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country
-
-| Parameter                          | Estimate | SD   | 95 \%HDI       |
-|:-----------------------------------|:---------|------|----------------|
-| $\gamma_{000}$ (Intercept)         | -7.06    | 0.81 | (-8.61, -5.44) |
-| $\gamma_{001}$ (Log import volume) | 0.27     | 0.06 | (0.16, 0.38)   |
-
-## Diagnosis of convergence
-
-It is important to confirm the model is converged. We demonstrate how to confirm this with model A1.
-
-The first step is Gelman-Rubin convergence diagnostic [@brooks:1998:GMM; @vehtari:2020:RNF].
-*brms* displays this in the form of $\widehat{R}$.
-In general, $\widehat{R} \approx 1$.
-The model might not have converged, when $\widehat{R} \ge 1.01$ [@vehtari:2020:RNF].
-The *summary()* function of brms displays the $\widehat{R}$ for each of the estimated unknown parameters.
-All parameter estimates have a $\widehat{R} = 1.0$.
-
-The second step is the MCMC trace plot (can be obtained with the function *plot()*).
-The traceplot should display the so-called "fuzzy caterpillar" pattern (Figure \@ref(fig:fig1)).
-There should be no breakage.
-
-```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy caterpillar pattern."}
-require(brms)
-import_brms <- readRDS("import_brms.RDS")
-plot(import_brms)
-```
-
-An additional check is to study the autocorrelation of all chains.
-The correlogram should display low serial correlation (successive high correlation).
-The function *mcmc_plot* can be used to plot this (Figure \@ref(fig:fig2)).
-
-If the diagnostics show evidence of nonconvergence, it is suggested to increase the number of iterations and number of chains.
-
-```{r fig2, echo = FALSE, fig.cap = "Correlogram of four chains showing no significant higher-order lag"}
-mcmc_plot(import_brms, type = "acf")
-```
-
-## Further diagnostics
-
-There are several diagnostic checks that we can do to make sure our model is valid.
-
-* Increasing number of iterations
-
-The first test is to increase the number of iterations from 2000 to a higher value, e.g.
-4000, and see if the result is consistent with the initial analysis.
-This check makes sure our result is not transient due to short iteration time.
-
-Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between two analyses.
-
-* Using another weakly informative prior
-
-We can also use another weakly informative prior to see how our initial choice influences the result.
-We tried another weakly informative prior for the regression coefficients, $\mathcal{t}(1, 0, 0.25)$ [@gelman:2008].
-Similarly, changing prior only impacts the second decimal place of the estimates.
-
-* Posterior predictive checks
-
-We can use posterior predictive checks to study how our model fits our data.
-The gist of the method is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original data ($y$).
-A good model should display a similar probability distribution of $y_{rep}$ and $y$.
-It can be done with the function *pp_check()* (Figure \@ref(fig:fig3) ).
-
-```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
-pp_check(import_brms, nsamples = 100)
-```
-
-# Discussion
-
-Instead of arguing the advantages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis.
-The analyses in these extensions are not preregistered.
+# Extensions to Example 1
 
@@
 
-# Conclusion
+# Leave-one-out cross validation of Example 2
 
-In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research.
-We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
-Using a Bayesian approach, however, has also clearly some disadvantages.
-Researchers have to define priors in order to run a Bayesian regression analysis.
-As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
-If we have prior knowledge it allows us to create even better models.
-Furthermore, it takes more time to get the results of a Bayesian regression analysis.
-Estimating a Bayesian regression model is a computationally demanding task.
-It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1).
-Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].
+Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross validation (LOO).
+The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time.
+Given the rest of the data and the prediction model, we evaluate how accurate is the model to predict the outcome of the removed data point.
+The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].
 
-[^TIME]: We benchmarked the same model B1 but with subsets of data of some more "typical" sample sizes.
-A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 6-core computer.
-Although it is comparatively more computational intensive than *lme4*, the time needed is still reasonable.
+In R, the LOO cross validation of the two models (parsimonious model: *ppa_mod*; cubic model *ppa_qmod*) can be launched with the function `loo`.
+
+```r
+loo(ppa_qmod, ppa_mod)
+```
+
+The difference in $elpd_{loo}$ between the cubic model and the parsimonious model is only -0.3 but with a standard error of 0.5.
+One would say there is a difference in out of sample model fit, when $elpa_{loo}$ is many times larger than its standard error.
 

### 2022-02-07 manuscript.rmd
Move extensions and LOO to `extension.rmd`

@@
 Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach.
-Using the openly available *useNews* data and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
+Using the openly available *useNews* and *Worlds of Journalism Study* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
 We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model.
@@
 For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
-It assumes a macro contextual factor (e.g.
-newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g.
-degree of opinion-orientation), namely, the article-level or journalist-level.
+It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.
 
@@
 A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
-Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries.
+Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries.
 Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research.
@@
 
-[^author]: Theoretically with a large enough data it can be argued that a news article is nested within authors.
+[^author]: Theoretically, with large enough data it can be argued that a news article is nested within authors.
 
-In our paper we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
+In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
 While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p.
@@
 It is perhaps well-known what ecological fallacy is.
-We commit ecological fallacy, when we make inference at micro-level (e.g.
+We commit ecological fallacy, when we make inference at the micro-level (e.g.
 Eating more chocolate makes one cleverer) based on macro-level data (e.g.
@@
 Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it.
-The choice of media outlets or countries are almost always not randomly selected.
+The choice of media outlets or countries is almost always not randomly selected.
 [^1] This sampling approach makes the independence assumption even more fragile.
@@
 Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data.
-In contrast to sampling, these studies are actually doing census of all data.
+In contrast to sampling, these studies are actually doing a census of all data.
 There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
@@
 
-Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayiesan approach**.
+Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayesian approach**.
 The same approach is equally applicable to both non-stochastic and stochastic comparative datasets.
-Therefore, one can analyse both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.
+Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.
 
@@
 
-What is the probability for this paper being accepted by *Digital Journalism*?
-Under the frequentist framework (and if *Digital Journalism* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Digital Journalism*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
-It is indeed impractical as well as inhumane to the editorial team of *Digital Journalism*.
+What is the probability for this paper being accepted by *Journalism Studies*?
+Under the frequentist framework (and if *Journalism Studies* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Journalism Studies*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
+It is indeed impractical as well as inhumane to the editorial team of *Journalism Studies*.
 Instead, we assert before submission that this paper has a probability of 24% for being accepted.
-That is the published acceptance rate from *Digital Journalism*’s website.
+That is the published acceptance rate from *Journalism Studies*’s website.
 After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%.
@@
 After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%.
-If you see this paper under the "Latest articles" section of *Digital Journalism*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
+If you see this paper under the "Latest articles" section of *Journalism Studies*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
 
@@
 The $P(X| \theta)$ part is called likelihood function.
-In the *Digital Journalism* example, the likelihood function is based on rough rules from our experience and thus is not systematic [^dj].
+In the *Journalism Studies* example, the likelihood function is based on rough rules from our experience and thus is not systematic.
 In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
 Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
-
-[^dj]: As a side note: we have actually performed the experiment by submitting this paper to *Digital Journalism*. But for pragmatic reasons we cannot report the posterior.
 
@@
 Part 3 (Prior) is arguably the most controversial part of Bayesian analysis.
-In the *Digital Journalism* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
+In the *Journalism Studies* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
 Finding previous studies for an informative prior is the logical first thing to do.
@@
 But one person's expert opinion could be another person's wishful thinking.
-And this perceived subjectivity of specifying priors by experts’ judgement attracts wide-spread criticism from both statisticians [e.g.
+And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g.
 @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].
@@
 Although some communication researchers adopted the method [e.g.
-@kovic:2017:B;@chan2020high] these studies are not comparative.
-As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT.
+@kovic:2017:B;@chan2020high], these studies are not comparative.
+As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE.
 We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
-Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced].
+Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of the rest of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced].
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
-The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
+The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
 
-The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archtypes of comparative journalism studies.
+The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archetypes of comparative journalism studies.
 The first example is an analysis of a comparative, non-stochastic content analytic dataset.
@@
 
-The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets .
-The media content data was collected from the MIT MediaCloud and made available as document-term matrices.
+The useNews is an openly available dataset [@puschmann:2020] that includes 2019 to 2020 media content data from an array of worldwide media outlets.
+The media content data was collected from the MediaCloud and made available as document-term matrices.
 
@@
 
-[^dict_val]: One might argue our seed dictionaries are not validated.
-We deem that the criterion validity of our dictionary should be built-in.
-Coverage of China, by definition, should mention words about China.
-We also maintain that it is difficult to conduct a human validation of the seed dictionaries because the useNews dataset [@puschmann:2020] doesn’t provide access to the full-length articles.
-Nonetheless, we attempted to conduct such validation by randomly selecting 10 matching and 10 non-matching items for each language.
-In total, 160 items were selected.
-A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the meta data provided in the useNews dataset [@puschmann:2020].
-For some languages, the coder used Google Translate to translate the full text article to English.
-In total, only 138 URLs were still accessible.
-Comparing the ground truth and the human coding, 62 and 70 are true-positive and true-negative cases.
-There are also 5 false-negative and 1 false-positive cases.
-There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases.
-The false-positive case is Korean and that could be due to incorrect tokenization at the MIT Media Cloud’s end.
-The 5 false-negative cases are in Norwegian, Portuguese, and Romanian.
-The content on the website might have changed since MIT Media Cloud collected the data.
-For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM.
-Despite all these caveats, our seed dictionaries have a precision and recall of 98.4% and 92.5% respectively.
-For the purpose of demonstrating regression analysis, this level of accuracy is more than sufficient.
+[^dict_val]: The validation of the dictionary is available in the Appendix.
 
@@
 We used logistic regression for this analysis.
-Due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.
+However, due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.
 
@@
 number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence.
-*brms* is smart enough to give suggestions on how to adjust these three values.
+*brms* is smart enough to suggest how to adjust these three values.
 Nonetheless, we provide a short guide on how to diagnose convergence.
@@
 However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
-Some Bayesians, notably, Andrew Gelman, report very liberal 50\% credible intervals.
+Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals.
 @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.
@@
 
-Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between two analyses.
+Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses.
 
@@
 ```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
-pp_check(import_brms, nsamples = 100)
+pp_check(import_brms, ndraws = 100)
 ```
 
-## Extentions
+## Extensions
 
-We propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.
-
-### Extension #1: Hypothesis testing
-
-Under the Bayesian framework, we can test hypotheses about the parameter estimates [@shikano:2019:HTB].
-These hypotheses are similar to the null hypothesis in the Neyman-Pearson's sense.
-For example, we want to test the two-sided hypothesis of $\gamma_{01} = 0$ for Model A1.
-For this, we need to calculate the posterior probability of this hypothesis: $P(\gamma_{01} = 0 | X)$.
-The function *hypothesis()* can be used to test such hypothesis.
-
-```r
-hypothesis(import_brms, "logx_import = 0")
-```
-
-The posterior probability of this hypothesis is 0.
-Therefore, we can safely reject the hypothesis and conclude that $\gamma_{01} \neq 0$, i.e.
-log import volume of the outlet's country is associated with the frequency of China coverage at the outlet level.
-
-While accepting a null hypothesis is not a feasible option in a frequentist framework, as such a framework has an "inability to gain evidence for the null" [@rouder:2009:B, p.
-226] hypothesis, it is practically possible to  accept a null hypothesis in a Bayesian framework [@kruschke:2018:RAP].
-Bayes factor or the region of practical equivalence (ROPE) could be used to decide to accept the null hypothesis.
-@kruschke:2018:RAP, for example, suggests using $\sigma = \pm 0.1$ as half of small effect size to establish a ROPE.
-However, there is no fixed rule on how to define a ROPE.
-If now 95\% of the HDI for an estimate falls within the ROPE, researchers could accept the null hypothesis for practical purposes.
-A practical application could be with manual content analysis or survey research in communication research if some variables are challenging and costly to measure.
-In a frequentist framework, failing to reject the null hypothesis could wrongly inform researchers to collect more data in subsequent studies to discern between insufficient power [^POWER] or the null is true.
-Instead, ROPE could be used to decide whether, in future studies, more data should be collected to retest the same hypothesis.
-When ROPE provides a strong signal that the null hypothesis is true, it is no longer worthy to collect more of the costly data just to boost the statistical power.
-
-[^POWER]: Statistical power is a frequentist concept specifying the long run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.
-
-The package bayestestR [@makowski:2019] can be used to calculate and visualize the ROPE.
-
-```r
-library(bayestestR)
-rope(import_brms)
-plot(rope(import_brms))
-```
-
-```{r, include = FALSE}
-library(bayestestR)
-fig <- plot(rope(import_brms))
-```
-
-```{r figrope, results = "asis", fig.cap = "The Region of Practical Equivalence and the 95% High Density Interval"}
-fig
-```
-
-The proportion of 95\% HDI falling inside the ROPE is 0\%.
-Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) have no overlap with the ROPE (the shaded region).
-Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided).
-In the current situation, it is very clear that the 95\% HDI falls outside of the ROPE as there is 0\% overlap.
-Similar to the result from *hypothesis()*, there is a practical effect and it is correct to reject the null hypothesis.
-
-However, in another situation when we have a simulated independent variable *noise* that is basically random noise.
-
-```r
-outlet_data$noise <- rnorm(nrow(outlet_data))
-
-noise_brms <- brm(z~offset(log(n))+(1|k)+noise,
-                  data = outlet_data, family = negbinomial(),
-                  control = list(adapt_delta = 0.99),
-                  prior = weaklyinformative_prior,
-                  sample_prior = TRUE)
-rope(noise_brms)
-```
-
-In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%.
-The proportion is quite high but it is not decisive.
-@kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE.
-Accordingly, the current situation of 68\% is "undecided".
-It might be worthwhile to retest the hypothesis with a larger amount of data.
-
-One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g.
-how to determine the ROPE, how wide should the ROPE be, and which level of HDI to use.
-ROPE is also sensitive to the scale of measurement.
-Nonetheless, ROPE can provide much richer information to inform how future studies should be designed.
-
-### Extension #2: Cross-level interaction
-
-We can also study the interaction between a macro- and a micro-level variable.
-Cross-level interaction is useful to study how the effect of context variables manifest differently in individuals with different characteristics.
-An example of cross-level interaction in our example is whether the relationship between import volume and increase in China coverage manifests differently between public broadcasters and for-profit media.
-
-We can model a cross-level interaction by adding an interaction term between the macro- and micro-level variables, as well as a varying-slope component for the micro-level variable [@heisig:2019:WYS].
-With *brms*, it can be done with this:
-
-```r
-# suppose "public" is a binary variable
-import_brms_public <- brm(
-      z~offset(log(n))+(1 + public|k)+log(x_import)*public,
-      data = outlet_data, family = negbinomial(),
-      prior = weaklyinformative_prior, sample_prior = TRUE)
-import_brms_public
-```
-
-The regression coefficients for the main effect of public broadcasting and the interaction terms have a wide 95\% HDI that covers zero.
-It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function).
-The trajectories of public broadcasters and for-profit media outlets are similar, indicating no interaction.
-
-```{r fig4, echo = FALSE, fig.cap = "Conditional effects plot showing no interaction among public broadcasting, import volume and China coverage."}
-require(ggplot2)
-condit_plots <- readRDS("condit_plots.RDS")
-condit_plots$`x_import:public` + xlab("Import Volume") + ylab("Number of articles mentioning China per 10,000 articles") + scale_x_continuous(labels = scales::comma) + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
-```
-
-### Extension #3: Current study as the informative prior for the next study
-
-Suppose we would like to replicate the study and confirm the same relationship with the 2020 useNews data.
-This time, we do not need to (and actually, we should not) use the weakly informative prior again.
-It is because we have *prior* understanding about the outlet-level determinants of China coverage: We know from the 2019 data that $\gamma_{01}$ should be around 0.25 with a standard deviation of 0.05.
-This can be entered into our new analysis as the informative prior.
-
-```r
-informative_prior <- c(prior_string("normal(0.25, 0.05)", class = "b",
-                                    coef = "logx_import"),
-                       prior_string("normal(-6.69, 0.66)",
-                                    class = "Intercept"))
-import_2020 <- brm(z_2020~offset(log(n_2020))+(1|k)+log(x_import),
-                   data = outlet_data2020, family = negbinomial(),
-                   prior = informative_prior, sample_prior = TRUE)
-```
-
-The new analysis showed that $\gamma_{01}$ is 0.22 with a 95\% HDI of (0.15 to 0.29) for the year 2020.
-This analysis displays two things: 1) selection of prior is not always, as many authors have suggested, as controversial and subjective; and 2) Bayesian analysis also makes a strong case for replication studies, which open science hopes to enable [@dienlin:2020:AOS].
-The use of informative prior in replication studies enables us to update our prior beliefs with the new evidence from the replications.
-Priors, replicable or not, will get updated.
-
-## Extension #4: Temporal changes
-
-Bayesian multilevel regression analysis is also useful to study temporal changes, because observations from the same subject collected from different time points are naturally a cluster.
-The same strategy for handling the clustering of observations in the multilevel modeling can be used.
-We model that observations from the same media outlet are nested within the media outlet and then the media outlet is nested within its countries.
-Suppose we would like to study if there is a systematic increase in $z$ across all outlets, maybe due to the COVID-19 pandemic or the presidential election in the US.
-It can be analyzed with this three-level model.
-
-```r
-## Suppose yr is a binary dummy variable indicating the year 2020.
-import_long <- brm(z~offset(log(n))+(1|k/i)+yr, data = outlet_long,
-                   family = negbinomial(),
-                   prior = weaklyinformative_prior,
-                   sample_prior = TRUE)
-import_long
-```
-
-The regression coefficient for the year dummy variable is 0.49 (95\% HDI 0.38, 0.60). There is a global increase in China coverage from 2019 to 2020.
+We propose several extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes.
+The analyses in these extensions are not preregistered.
+Please refer to Appendix I for these extensions.
 
@@
 Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis.
-In this example, the same approach is applied to a stochastic dataset from a randomize survey.
+In this example, the same approach is applied to a stochastic dataset from a randomized survey.
 The starting point of this example is the recent study by @hamada:2021:DJA.
@@
 It is important to point out that the study is actually a replication.
-The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkable similar title to that of @hamada:2021:DJA.
+The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA.
 The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.
@@
 First, a massive amount of information at the author-level was discarded and cannot leverage the hierarchical structure of the data.
-As showed in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy.
-Taking the aggregated approach assumes that all of these author-level variables are homogeneous.
+As shown in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy.
+Taking the aggregated approach assumes that all of these author-level variables are homogeneous across countries.
 This assumption could create spurious correlation when the distribution of author-level variables is associated with contextual factors, e.g.
 Index of Democracy.
-Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the more perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g.
+Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g.
 the average level of perceived professional autonomy of journalists in a country).
@@
 Bayesian multilevel regression is probably the only valid approach.
-First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance at the journalist-level perceived professional autonomy.
-Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replication clearer.
+First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance on the journalist-level perceived professional autonomy.
+Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replicate clearer.
 
@@
 Unfortunately, the ANOVA result from @reich:2013:DJP cannot be used as the prior and we still need to use weakly informative prior.
-However, @reich:2013:DJP suggest that the relationship between Index of Democracy and perceived professional autonomy is in convex "J shape", with the average perceived professional autonomy of journalists in authoritarian regimes (the lowest end of democracy performance) being higher than those in hybrid regimes (3.92 vs 3.65).
+However, @reich:2013:DJP suggest that the relationship between Index of Democracy and perceived professional autonomy is in "J shape", with the average perceived professional autonomy of journalists in authoritarian regimes (the lowest end of democracy performance) being higher than those in hybrid regimes (3.92 vs 3.65).
 We can incorporate this prior information into our model by modeling a cubic relationship between Index of Democracy and perceived professional autonomy.
 Similar to the general procedure of conducting polynomial regression, we also create a parsimonious model assuming only a linear relationship to study whether the cubic regression improves the model fit.
-In other words, whether the relationship is really in convex "J shape" is studied [^jshape].
+In other words, whether the relationship is really in "J shape" is studied [^jshape].
 
@@
 Another advantage of taking a Bayesian multilevel regression approach rather than the bivariate approach as in @reich:2013:DJP is the possibility to adjust for the possible confounding effects of other marco-level variables.
-For example, GDP per capita (according to World Bank) is moderately correlated with Index of Democracy (r = `r cor(pts_tab$eiu, pts_tab$gdppc, use = "complete")`).
+For example, GDP per capita (according to the World Bank) is moderately correlated with the Index of Democracy (r = `r cor(pts_tab$eiu, pts_tab$gdppc, use = "complete")`).
 The correlation between Index of Democracy and perceived professional autonomy found by @reich:2013:DJP could be spurious and the GDP per capita were the actual determinant of perceived professional autonomy.
@@
 
-The following is the complete code to construct the two Bayesian model. The cubic relationship can be set using the `I()` function.
+The following is the complete code to construct the two Bayesian models. The cubic relationship can be set using the `I()` function.
 
@@
 By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34).
-It is not only statistical significant in the traditional sense but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
-It supports @hamada:2021:DJA's h2a, but our model does that without the problem of aforementioned ecological fallacy and with adjustment for other potential confounders.
+The Index of Democracy is not only a substantial predictor as 0 is not covered by the 95% HDI but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
+It supports @hamada:2021:DJA's h2a, but our model does that without the problem of the aforementioned ecological fallacy and with adjustment for other potential confounders.
 
-Regarding the possible convex "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194).
-By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not convex "J shape".
-Journalists in countries scored a lower Index of Democracy have also the lowest perceived professional autonomy.
+Regarding the possible "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194) [^loo].
+By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not "J shape".
+In average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.
 
-```{r fig5, echo = FALSE, fig.cap = 'Conditional effects plot showing no convex "J shape" relationship between perceived professional autonomy and Index of Democracy.'}
+```{r fig5, echo = FALSE, fig.cap = 'Conditional effects plot showing no "J shape" relationship between perceived professional autonomy and Index of Democracy.'}
+require(ggplot2)
 x <- readRDS("qmod_condit.RDS")
@@
 
-[^jshape]: Actually, the replication by @hamada:2021:DJA has shown that the relationship is not in such convex J shape. But we were assumed to be in the time point before such replication.
+[^jshape]: Actually, the replication by @hamada:2021:DJA has shown that the relationship is not in such J shape. But we were assumed to be in the time point before such replication.
+
+[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See Appendix for the analysis.
 
@@
 [^TIME]: We benchmarked the same model B1 but with subsets of data of some more "typical" sample sizes.
-A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 6-core computer.
+A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 8-core computer.
 Although it is comparatively more computational intensive than *lme4*, the time needed is still reasonable.

### 2022-02-07 extract_bib.R

@@ -1,1 +1,1 @@
-condensebib::reduce_bib("manuscript.rmd", master_bib = "/home/chainsawriot/dev/dotfiles/bib.bib", out_bib = "manuscript.bib")
+condensebib::reduce_bib(c("manuscript.rmd", "extension.rmd"), master_bib = "/home/chainsawriot/dev/dotfiles/bib.bib", out_bib = "manuscript.bib")

### 2022-02-07 wjs2.R

@@ -4,3 +4,11 @@ x <- readRDS("ppa_qmod.RDS")
 qmod_condit <- plot(conditional_effects(x, effects = "eiu", ask = FALSE, plot = FALSE))
 
 saveRDS(qmod_condit, "qmod_condit.RDS")
+
+## LOO
+
+ppa_mod <- readRDS("ppa_mod.RDS")
+ppa_qmod <- readRDS("ppa_qmod.RDS")
+
+saveRDS(loo(ppa_qmod, ppa_mod), "ppa_loo.RDS")
+

### 2022-02-15 extension.rmd
Add all files essential for compiling manuscript.rmd; anonymize

@@
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
-wordcount         : "7618"
+wordcount         : "1883"
 

### 2022-02-15 manuscript.rmd
Add all files essential for compiling manuscript.rmd; anonymize

@@
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
-wordcount         : "7618"
+wordcount         : "8964"
 
@@
 
-Communication research is often comparative, journalism studies are no exception.
-For example, comparative approach is used in modeling journalistic culture [e.g.
+Communication research is often comparative, journalism studies are increasingly so [@hanusch:2019:C].
+Comparative approach is used in modeling journalistic culture [e.g.
 @esser:2013:C], comparative news value research [e.g.
@@
 @wu:2000:SDI;@grasland:2019:I], among others.
-A typical comparative study in journalism research, otherwise known as comparative content analysis, includes news articles from various outlets and usually also from various countries.
+Around 40% of recent  comparative studies in journalism research are comparative content analysis [@hanusch:2019:C], which include news articles from various outlets and usually also from various countries.
 Then the included news articles are coded either manually or automatically.
-Surveys in journalism research are often comparative, e.g.
-the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].
+Another 10% of recent comparative studies in journalism research are surveys such as the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].
 
 Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g.
-political orientation, online versus offline) and their countries (e.g.
-post-communist country) influence the content of news articles or behaviours of journalists.
+political orientation, online versus offline) or their countries (e.g.
+post-communist country) influence the content of news articles or behaviors of journalists.
 For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
@@
 
-[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years.
-One could question the necessity of another repetition in this paper.
-The non-atomicity argument might be repetitious but we believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
-356] said-- is still not the default regression approach in communication research.
-For example, as recent as in 2020 some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5].
-Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel].
-We reject this justification because it violates the independence assumption and thus commits atomistic fallacy.
-A fallacious result with less error is still fallacious.
-See also @nezlek:2008:IMM for a criticism of such justification.
+[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious.
+We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
+356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g.
+an example in @zhu:2020:S [footnote 5].
+Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel].
+See also @nezlek:2008:IMM for a criticism of these justifications.
 
@@
 
-Before we move on to the next section, it is important to point that **non-stochastic data is not an essential condition for applying the Bayesian approach**.
+Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**.
 The same approach is equally applicable to both non-stochastic and stochastic comparative datasets.
@@
 
-Table \@ref(tab:t1) shows a summary of all models from outlet-level analysis using three different ways of modeling.
+Table \@ref(tab:t1) shows a summary of all models from the outlet-level analysis using three different ways of modeling.
 The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$).
@@
 [^5]: HDI is one representation of the Bayesian credible interval.
-It is important to note that, like confidence intervals, there should be no "correct" choice of the level of credibility but some established conventions.
+There should be no "correct" choice of the level of credibility but some established conventions.
 We choose, like many published works [e.g.
-@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% to maintain "compatibility" with the established convention of reporting 95\% confidence interval.
+@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\%.
 However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
@@
 
-We propose several extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes.
+We propose four extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes.
 The analyses in these extensions are not preregistered.
@@
 By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not "J shape".
-In average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.
+On average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.
 
@@
 As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
-If we have prior knowledge it allows us to create even better models.
+If we have prior knowledge it allows us to create even better models, as Example 2 has shown.
 Furthermore, it takes more time to get the results of a Bayesian regression analysis.
@@
 Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6,525 articles in @esser:2013:C] can be estimated within a reasonable time frame [^TIME].
+6,525 articles in @esser:2013:C or 27,567 journalists in Example 2] can be estimated within a reasonable time frame [^TIME].
 

### 2022-02-19 extension.rmd
Add small fixes to the mentions of online appendix

@@
 ---
-title             : "Appendix to \"Bayesian (comparative) journalism studies\""
+title             : "Online appendix to \"Bayesian (comparative) journalism studies\""
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time.
-Given the rest of the data and the prediction model, we evaluate how accurate is the model to predict the outcome of the removed data point.
-The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].
+Given the rest of the data and the prediction model, one evaluates how accurate is the model to predict the outcome of the removed data point.
+The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can be used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].
 
@@
 
-The difference in $elpd_{loo}$ between the cubic model and the parsimonious model is only -0.3 but with a standard error of 0.5.
+The difference in $elpd_{loo}$ between the cubic model and the parsimonious model is only -0.3 with a larger standard error of 0.5.
 One would say there is a difference in out of sample model fit, when $elpa_{loo}$ is many times larger than its standard error.

### 2022-02-19 manuscript.rmd
Add small fixes to the mentions of online appendix

@@
 
-[^dict_val]: The validation of the dictionary is available in the Appendix.
+[^dict_val]: The validation of the dictionary is available in the online appendix.
 
@@
 The analyses in these extensions are not preregistered.
-Please refer to Appendix I for these extensions.
+Please refer to the online appendix for these extensions.
 
@@
 
-[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See Appendix for the analysis.
+[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See the online appendix for the analysis.
 

### 2022-02-19 deanony.R
Make auto deanony. version

@@ -1,0 +1,4 @@
+x <- readLines("manuscript.rmd")
+x[x == "mask              : yes"] <- "mask              : no"
+writeLines(x, "manuscript_name.rmd")
+rmarkdown::render('manuscript_name.rmd', output_format = 'all')

### 2022-03-01 extension.rmd
Make the Makefile emit docx; trim to under 8900 words
For IJOC; the emitted docx still needs some manual work, e.g. chopping
the equations etc.. But this is the most reproducible workflow one can
get for a journal only processing docx.

@@
 
-author: 
-  - name          : "Chung-hong Chan"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
-    email         : "chung-hong.chan@mzes.uni-mannheim.de"
-  - name          : "Adrian Rauschfleisch"
-    affiliation   : "2"
+# author: 
+#   - name          : "Chung-hong Chan"
+#     affiliation   : "1"
+#     corresponding : yes
+#     address       : "A5, 6 (section A), 68159 Mannheim, Germany"
+#     email         : "chung-hong.chan@mzes.uni-mannheim.de"
+#   - name          : "Adrian Rauschfleisch"
+#     affiliation   : "2"
 
-affiliation:
-  - id            : "1"
-    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
-  - id            : "2"
-    institution   : "National Taiwan University, Taiwan"
+# affiliation:
+#   - id            : "1"
+#     institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
+#   - id            : "2"
+#     institution   : "National Taiwan University, Taiwan"
 
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+# Source Code
+
+All source will be available on the author(s)' Github upon acceptance. The following are key code chunks used in the paper.
+
+## Expression of outlet-level models in lme4 and brms
+
+```r
+require(brms)
+require(lme4)
+# brms
+brm(z ~ offset(log(n)) + (1|k)+log(x),
+          family = negbinomial(), data = outlet_data)
+# lme4
+glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
+```
+
+## Expression of disaggregated out-level model in MASS
+
+```r
+require(MASS)
+glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
+```
+
+## Expression of article-level models in lme4 and brms
+
+```r
+brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
+glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
+```
+
+## Expression of disaggregated article-level model in MASS
+
+```r
+glm(y ~ log(x), family = binomial(), data = article_data)
+```
+
+## Setting up weakly informative prior in the brms model
+
+```r
+weaklyinformative_prior <- c(prior_string("normal(0, 1)",
+                                          class = "b"),
+                             prior_string("normal(0, 1)",
+                                          class = "Intercept"))
+# The sample_prior argument is optional. But useful for further analysis.
+import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
+          data = outlet_data, family = negbinomial(),
+          prior = weaklyinformative_prior, sample_prior = TRUE)
+import_brms
+```
+
+## WJS: Estimation of prior
+
+```r
+beta_d_1 <- 0.15
+sig_level <- 0.001
+beta_d_1 / abs(qnorm(sig_level / 2))
+```
+
+## WJS: Full code
+
+The cubic relationship can be set using the `I()` function.
+
+```r
+require(tidyverse)
+
+informative_prior <- c(prior_string("normal(0, 1)", class = "b"),
+                       prior_string("normal(0, 1)", class = "Intercept"),
+                       prior_string("normal(0.14, 0.045)",
+                                    class = "b", coef = "EXPRNCE"),
+                       prior_string("normal(0.07, 0.027)",
+                                    class = "b", coef = "RANK"))
+
+std <- function(x){
+  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
+}
+## eiu is Index of Democracy, gdppc is GDP per capita (log)
+set.seed(12121)
+wjs %>%
+    select(ppa, EXPRNCE, RANK, GENDER, UNI_EDU, UNI_EDU, eiu, gdppc, COUNTRY) %>%
+    mutate(gdppc = log(gdppc), COUNTRY = as.factor(COUNTRY)) %>%
+    mutate_at(vars(ppa:gdppc), std) -> wjs_processed
+brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
+    data = wjs_processed, cores = 4, iter = 3000, prior = informative_prior,
+        sample_prior = TRUE) -> ppa_mod
+
+set.seed(12121)
+## iter needs to set larger to ensure convergence
+brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + I(eiu^3) + gdppc + (1|COUNTRY),
+    data = wjs_processed, cores = 4, iter = 4000, prior = informative_prior,
+    sample_prior = TRUE) -> ppa_qmod
 ```

### 2022-03-01 manuscript.rmd
Make auto deanony. version
Make the Makefile emit docx; trim to under 8900 words
For IJOC; the emitted docx still needs some manual work, e.g. chopping
the equations etc.. But this is the most reproducible workflow one can
get for a journal only processing docx.

@@
   The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
+The authors report there are no competing interests to declare.
   Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/
@@
 
-*"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM
+<!-- *"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM -->
 
@@
 Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research.
-An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
+An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
 Hypothesis-generating comparative study, however, is rare.
@@
 It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
-A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author].
+A news article is nested within its media outlet and its media outlet is in turn nested within its country.
 Such data structure brings two problems: non-atomicity and non-stochasticity.
-
-[^author]: Theoretically, with large enough data it can be argued that a news article is nested within authors.
 
@@
 The choice of media outlets or countries is almost always not randomly selected.
-[^1] This sampling approach makes the independence assumption even more fragile.
+<!-- [^1] --> This sampling approach makes the independence assumption even more fragile.
 
-[^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa.
+<!-- [^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa. -->
 
@@
 The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis.
-[^2]
+<!-- [^2] -->
 
-[^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious.
+<!-- [^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious.
 We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
@@
 an example in @zhu:2020:S [footnote 5].
-Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel].
-See also @nezlek:2008:IMM for a criticism of these justifications.
+<\!-- Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel].
+-\-> See also @nezlek:2008:IMM for a criticism of these justifications.
+-->
 
@@
 
-*"PROBABILITY DOES NOT EXIST."* Bruno de Finetti
-
-What is the probability for this paper being accepted by *Journalism Studies*?
-Under the frequentist framework (and if *Journalism Studies* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *Journalism Studies*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
-It is indeed impractical as well as inhumane to the editorial team of *Journalism Studies*.
+What is the probability for this paper being accepted by *IJOC*?
+Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
+It is indeed impractical as well as inhumane to the editorial team of *IJOC*.
 Instead, we assert before submission that this paper has a probability of 24% for being accepted.
-That is the published acceptance rate from *Journalism Studies*’s website.
+That is the published acceptance rate of a similar journal.
 After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%.
@@
 After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%.
-If you see this paper under the "Latest articles" section of *Journalism Studies*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
+If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
 
@@
 Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M].
-In this way, one specifies only the possible range of the posterior [^4].
+In this way, one specifies only the possible range of the posterior<!-- [^4] -->.
 Some so-called "default weakly informative priors", e.g.
@@
 
-[^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised.
+<!-- [^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised. -->
 
@@
 
-*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
-19]
+<!-- *"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
+19] -->
 
@@
 It is reasonable to say that Bayesian analysis is extremely rare in our field.
-Although some communication researchers adopted the method [e.g.
-@kovic:2017:B;@chan2020high], these studies are not comparative.
+Although some communication researchers adopted the method (e.g.
+AUTHOR2, AUTHOR3) <!-- [e.g.
+@kovic:2017:B;@chan2020high] -->, these studies are not comparative.
 As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE.
 We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
-Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of the rest of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced].
+Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], one purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ).
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
-The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
+<!-- The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
+-->
 
@@
 We used only the data from 2019 as the baseline.
-It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
+<!-- It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
 Also, it was at the zenith of the US-China trade war.
+-->
 
@@
 
-In lme4 and brms, the above equation is expressed as such:
-
-```r
-require(brms)
-require(lme4)
-# brms
-brm(z ~ offset(log(n)) + (1|k)+log(x),
-          family = negbinomial(), data = outlet_data)
-# lme4
-glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
-```
-
 In the disaggregation case, the multilevel structure is ignored and the regression equation becomes:
@@
 \end{align}
-
-In MASS, it is expressed as such:
-
-```r
-require(MASS)
-glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
-```
 
@@
 
-Or in lme4/brms code:
-
-```r
-brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
-glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
-```
-
 In the disaggregation case, the multilevel structure is ignored and the regression equations become:
@@
 \end{align}
-
-In MASS, it is expressed as such:
-
-```r
-glm(y ~ log(x), family = binomial(), data = article_data)
-```
 
@@
 
-All, except the prior for regression coefficients, are default priors suggested by *brms*. The prior can be set with the following R code.
-
-```r
-weaklyinformative_prior <- c(prior_string("normal(0, 1)",
-                                          class = "b"),
-                             prior_string("normal(0, 1)",
-                                          class = "Intercept"))
-# The sample_prior argument is optional. But useful for further analysis.
-import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
-          data = outlet_data, family = negbinomial(),
-          prior = weaklyinformative_prior, sample_prior = TRUE)
-import_brms
-```
+All, except the prior for regression coefficients, are default priors suggested by *brms*.
 
@@
 We choose, like many published works [e.g.
-@stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\%.
+@stegmueller:2013:HMC<!-- ; @kovic:2017:B; @chan2020high -->], the default value of 95\%.
 However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
-Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals.
+<!-- Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals.
 @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.
 @leeuw:2020:AAT select 90\%.
+-->
 
@@
 
-There are several diagnostic checks that we can do to make sure our model is valid.
+There are <!-- several --> two diagnostic checks that we can do to make sure our model is valid.
 
-* Increasing number of iterations
+<!-- * Increasing number of iterations -->
 
-The first test is to increase the number of iterations from 2000 to a higher value, e.g.
+<!-- The first test is to increase the number of iterations from 2000 to a higher value, e.g.
 4000, and see if the result is consistent with the initial analysis.
 This check makes sure our result is not transient due to short iteration time.
+-->
 
-Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses.
+<!-- Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses. -->
 
@@
 We estimated the maximum standard deviation based on the significance level.
-For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving [^wald]:
+For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving <!-- [^wald] -->:
 
@@
 \end{align}
-
-or in R
-
-```r
-beta_d_1 <- 0.15
-sig_level <- 0.001
-beta_d_1 / abs(qnorm(sig_level / 2))
-```
 
@@
 
-The following is the complete code to construct the two Bayesian models. The cubic relationship can be set using the `I()` function.
-
-```r
-require(tidyverse)
-
-informative_prior <- c(prior_string("normal(0, 1)", class = "b"),
-                       prior_string("normal(0, 1)", class = "Intercept"),
-                       prior_string("normal(0.14, 0.045)",
-                                    class = "b", coef = "EXPRNCE"),
-                       prior_string("normal(0.07, 0.027)",
-                                    class = "b", coef = "RANK"))
-
-std <- function(x){
-  (x - mean(x, na.rm = TRUE))/sd(x, na.rm = TRUE)
-}
-## eiu is Index of Democracy, gdppc is GDP per capita (log)
-set.seed(12121)
-wjs %>%
-    select(ppa, EXPRNCE, RANK, GENDER, UNI_EDU, UNI_EDU, eiu, gdppc, COUNTRY) %>%
-    mutate(gdppc = log(gdppc), COUNTRY = as.factor(COUNTRY)) %>%
-    mutate_at(vars(ppa:gdppc), std) -> wjs_processed
-brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
-    data = wjs_processed, cores = 4, iter = 3000, prior = informative_prior,
-        sample_prior = TRUE) -> ppa_mod
-
-set.seed(12121)
-## iter needs to set larger to ensure convergence
-brm(ppa ~ EXPRNCE + RANK + GENDER + UNI_EDU + I(eiu^3) + gdppc + (1|COUNTRY),
-    data = wjs_processed, cores = 4, iter = 4000, prior = informative_prior,
-    sample_prior = TRUE) -> ppa_qmod
-```
-
 By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34).
@@
 
-[^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported.
+<!-- [^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported.
 And t-distribution approximates z-distribution asymptotically when df gets larger.
+-->
 

### 2022-11-18 extension.rmd
add r1

@@
 ---
-title             : "Online appendix to \"Bayesian (comparative) journalism studies\""
+title             : "Online appendix to \"Bayesian multilevel modeling and its application in comparative communication research\""
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 require(brms)
+require(parameters)
 import_brms <- readRDS("import_brms.RDS")
@@
 
-## Expression of disaggregated out-level model in MASS
+## Expression of disaggregated outlet-level model in MASS
 
@@
 
-# Validation of the seed dictionaries
+# Multivariate regression of Example 1
+
+Source code:
+
+```r
+brm(mvbind(C9, C10) ~ EXPRNCE + RANK + GENDER + UNI_EDU + eiu + gdppc + (1|COUNTRY),
+    family=cumulative("logit"), cores = 4, iter = 3000, sample_prior = TRUE,
+    data = wjs, control = list(adapt_delta = 0.99), prior = informative_prior)
+```
+
+## Results
+
+```{r, results = "asis", warning = FALSE, echo = FALSE}
+clmod <- readRDS("ppa_clmod.RDS")
+suppressWarnings(print(print_md(parameters(clmod, ci = 0.95))))
+```
+
+# Example 2: Validation of the seed dictionaries
 
@@
 
-# Extensions to Example 1
+# Extensions to the useNews example
 

### 2022-11-18 manuscript.rmd
add r1

@@
 ---
-title             : "Bayesian (comparative) journalism studies"
+title             : "Bayesian multilevel modeling and its application in comparative communication research"
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 abstract: |
-  Comparative approaches such as comparative content analysis are frequently used in journalism studies.
-The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study.
-It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data.
-Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach.
-Using the openly available *useNews* and *Worlds of Journalism Study* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
-We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model.
-Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.
-
+  Comparative approaches are frequently used in communication research, especially journalism studies.
+The purpose of this paper is to argue that Bayesian multilevel regression is a better option for analyzing comparative data.
+We argue that it is the only approach that can simultaneously account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of comparative data.
+Using the openly available *Worlds of Journalism Study* and *useNews* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
+We address the common challenges when using the Bayesian approach and highlight the advantages of posterior predictive checks for modeling checking.
 keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
@@
 
+```{r, echo = FALSE}
+pts_tab <- readRDS("pts_tab.RDS")
+require(brms)
+import_brms <- readRDS("import_brms.RDS")
+```
+
 <!-- *"The comparative approach attempts to reach conclusions beyond single cases and explains differences and similarities between objects of analysis against the backdrop of their contextual conditions."* @esser:2017:CRM -->
 
-Communication research is often comparative, journalism studies are increasingly so [@hanusch:2019:C].
-Comparative approach is used in modeling journalistic culture [e.g.
-@esser:2013:C], comparative news value research [e.g.
-@burggraaff:2017:T;@wilke:2012], news flow research [e.g.
+Comparative approaches are frequently used in communication research, especially in journalism studies.
+Journalism studies are using the comparative approach [@hanusch:2019:C] to model journalistic culture [e.g.
+@esser:2013:C], news value [e.g.
+@burggraaff:2017:T;@wilke:2012], news flow [e.g.
 @wu:2000:SDI;@grasland:2019:I], among others.
@@
 Another 10% of recent comparative studies in journalism research are surveys such as the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].
+Although this article uses examples from journalism studies, the comparative approach is not bound to journalism studies and has been widely deployed in various subfields of communication.
+Comparative communication research is not exclusive to comparison across countries.
+Based on @de2017comparative’s classification, one can do comparisons across times, media, and other units [e.g.
+language regions within a multilingual country, see @vogler:2021:TNM].
+In social media studies, for instance, it is common to compare content across sources [e.g.
+@zhao2019appealing].
+The methodological issues discussed in this paper apply also to those cases.
 
@@
 political orientation, online versus offline) or their countries (e.g.
-post-communist country) influence the content of news articles or behaviors of journalists.
+post-communist country) influence the behaviors of journalists or the content of news articles .
 For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
-It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.
+It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the journalist-level or article-level.
 
@@
 In @wu:2000:SDI, multiple stepwise regression was used.
-These approaches violate the underlying assumptions of the statistical analyses.
+These approaches violate the underlying assumptions.
 It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
@@
 Such data structure brings two problems: non-atomicity and non-stochasticity.
+And specifically, we propose two solutions: multilevel modeling and Bayesian approach.
 
-In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies.
-While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p.
-121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
-Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
+The goal of this paper is twofold.
+We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models.
+In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as the best possible approach for comparative research in communication science and especially in journalism studies.
+Using the openly available WJS and *useNews* datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
 
-## Non-atomicity
-
-*"When it comes to regression, multilevel regression deserves to be the default approach"* @mcelreath2020statistical [p. 356]
-
-It is perhaps well-known what ecological fallacy is.
-We commit ecological fallacy, when we make inference at the micro-level (e.g.
-Eating more chocolate makes one cleverer) based on macro-level data (e.g.
-the correlation between countries' chocolate consumption and countries' number of Nobel winners).
-The reverse of ecological fallacy, i.e.
-making inference at macro-level based on micro-level data, is equally fallacious.
-This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].
+## Multilevel models and non-atomicity
 
@@
 The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
-Suppose one wants to study a classic news value question of how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China.
-It is related to the news value of "meaningfulness" in @galtung:1965:SFN.
-The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China).
-Suppose there are $m$ news articles where $i = 1,2,\ldots,m$.
+Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the Worlds of Journalism data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA].
+The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (journalist-level: perceived professional autonomy) and $x_{i}$ be the independent variable at the macro-level (country-level: democratic performance).
+Suppose there are $m$ journalists  where $i = 1,2,\ldots,m$.
 
@@
 This method is the so-called "disaggregation approach".
-From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel].
+From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel].
 From a statistical standpoint, this approach violates the underlying independence assumption.
 Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.).
-Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer.
-Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it.
-The choice of media outlets or countries is almost always not randomly selected.
+Journalists from the same country are hardly i.i.d.: they are subjected to being governed by the same government and exposed to the same journalistic culture.
+Also, the way communication researchers survey the journalists resembles (nonrandom) cluster sampling rather than pure random sampling: one usually starts from a specific country and then surveys journalists from it.
+The choice of  countries is almost always not randomly selected.
 <!-- [^1] --> This sampling approach makes the independence assumption even more fragile.
@@
 @clarke:2008:W;@chen:2012:IIL].
-The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis.
+The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W].
 <!-- [^2] -->
@@
 Suppose there are $n$ countries in the above example.
-One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$.
-Then, we can do a count-based regression with a regression equation like so:
+One can aggregate the average level of $x$ as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$.
+Then, we can do a regression with a regression equation like so:
 
@@
   \label{eq:2}
-  \log{z_{k}} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
+  z_{k} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
 \end{equation}
 
-Using this aggregation method, the unit of analysis effectively switches from article to country.
-This method is useful when $x$ is the only independent variable, akin @esser:2013:C.
+Using this aggregation method, the unit of analysis effectively switches from journalist to country.
+This method is useful when $x$ is the only independent variable.
 It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect.
@@
 First, it cannot be used for data with more than two levels.
-In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogeneous and the information about media outlets was discarded.
+In those cases, the lower-level predictors were lumped together and in effect, assumed to be homogeneous and discarded.
 Second, this method discards a massive amount of information.
@@
 For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H].
-Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$).
+Also, the effective sample size is reduced from the number of journalists ($m$) to the number of countries ($n$).
+Third, if one specifies hypotheses at the journalist-level but bases one’s conclusion on the aggregated analysis, this is a risk of interpreting the macro-level association wrongly at the micro-level, otherwise known as ecological fallacy.
 Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g.
@@
 In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels.
-Using the above example, $y_{ik}$ denotes whether the $i$-th article in the $j$-th country is covering China; $x_{k}$ denotes the trade volume with China of the $k$-th country where the media outlet of $i$-th article is located.
+Using the above example, $y_{ik}$ denotes the perceived professional autonomy of the $i$-th journalist in the $j$-th country; $x_{k}$ denotes the democratic performance of the $k$-th country.
 
@@
 The benefit of using multilevel modeling lies in its flexibility in handling multi-level data.
-Suppose we also want to consider the clustering of articles around $o$ different media outlets in the above example and $j$-th media outlet is the media outlet of the $i$-th article, where $j = 1,\ldots, o$.
-The multilevel regression equations are rewritten as:
+Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available.
+[^WJSOUTLET] The multilevel regression equations are rewritten as:
 
@@
 
+[^WJSOUTLET]: The data on media organizations are not available in the 2nd wave of the WJS dataset.
+
 This flexibility is demonstrated in the study by @rinke:2016:ISB.
@@
 
-Multilevel modeling is the way to go for analyzing non-atomic data from comparative research.
-However, the conventional approach for statistical inference makes it not optimal.
-The conventional approach for statistical inference in multilevel modeling is maximum likelihood estimation (MLE).
-@stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e.
+Another way to look at the flexibility of multilevel modeling is the ability to vary other parameters in the regression equation as well.
+Suppose in another situation, a researcher is interested in analyzing the relationship between experience ($XP$) and perceived professional autonomy.
+Instead of assuming the effect to be uniform across countries, like in the following equation:
+
+\begin{align}
+y_{i} &= \beta_{0} + \beta_{1} XP_i + \epsilon_{i}
+\end{align}
+
+One can also assume the slope ($\beta_{1}$) to be a distribution that is governed by countries, i.e.
+
+\begin{align}
+y_{ik} &= \beta_{0} + \beta_{1} XP_{ik} + \epsilon_{ik} \\
+\beta_{1} &= \gamma_{10} + \mu_{1k}
+\end{align}
+
+This model is called the varying slope model and is useful to establish robust estimation of effect (in this case $\gamma_{10}$) across all countries.
+In this paper, we will not go into detail of this kind of model.
+For an example of its application in comparative communication research, see @barnidge:2018:SMS.
+
+In sum, multilevel modeling is the way to go for analyzing non-atomic data from comparative research.
+For surveys using probabilistic sampling, the conventional frequentist approach (maximum likelihood estimation, MLE) might still be valid and is available in most statistical packages [see an SPSS tutorial for communication researchers by @hayes:2006:PMM].
+However, @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e.
 more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
 countries) is small.
-@stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF;@bryan:2015:MMC].
+@stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF].
 Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons.
-Our argument is more in line with @western:1994:BIC.
+And for studies not using probabilistic sampling, we argue in the next section that the Bayesian approach is a better analytical approach.[@western:1994:BIC].
 
-## Non-stochasticity
+## Bayesian models and non-stochasticity
 
@@
 Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population.
-Suppose we replicated the same survey for 100 times and we would obtain a slightly different sample every time.
+Suppose we replicated the same survey 100 times and we would obtain a slightly different sample every time.
 We then calculated the 90\% confidence interval of the mean for each of these 100 surveys.
-We should anticipate that more or less 90 out of these 100 confidence intervals would include the true mean of the population.
+We should anticipate that roughly 90 out of these 100 confidence intervals would include the true mean of the population.
 We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**.
@@
 
-Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data.
-In contrast to sampling, these studies are actually doing a census of all data.
-There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
+Most of the comparative content analytic studies, unlike randomized surveys such as WJS, often collect all available content data from a bunch of selected media outlets.
+In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets.
+In these census-like situations, there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
 It is especially true for modern large-N studies using automated content analytic techniques.
-@burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p.
-6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.
+@burggraaff:2017:T, for instance, "collected **all** available news items from **a selection of major Dutch news outlets**, both online and print" (p.
+6, emphasis added) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.
+In that study, one could only get more data by including more media outlets or widening the time window.
+Unlike a repeatable survey like WJS, one can always randomly select more journalists from the sampling frame of all journalists in the respective country.
 
-Census-style studies are not repeatable and thus they generate non-stochastic data.
-In other words, data from comparative journalism studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
-P-values and confidence intervals generated do not have the same meaning as those from repeatable studies.
+Therefore, these modern comparative content analytic studies are not repeatable and thus they generate non-stochastic data.
+It could be argued that data from these comparative content analytic studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
+Confidence intervals generated do not have the same meaning as those from repeatable studies.
 According to @western:1994:BIC [p.
 413], these values from non-stochastic data "lack meaning even as abstract propositions".
+[^PVALUES]
+
+[^PVALUES]: In this article, we will not go into detail of the null hypothesis statistical testing (NHST) and p-values, except in the Online Appendix.
+It is because for studies with a very large N, which comparative studies usually are, NHST is guaranteed to give positive results due to the so-called “Too Big To Fail” problem [see @lin:2013:RCT].
+Also, researchers are usually not only interested in whether there is or isn’t an effect.
+Instead, we are interested in how large the magnitude and in what direction the effect is.
+Therefore, we will focus only on the point and interval estimations from various regression models.
 
@@
 In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation.
-This counterargument could be useful but unlike a regular sample, whose representativeness can be assessed, we can never assess the representativeness of the census with respect to the theoretical superpopulation.
+This counterargument could be useful but unlike a regular random sample (cluster sample included), whose representativeness can be assessed, we can never assess the representativeness of the census-like data with respect to the theoretical superpopulation.
 Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.
@@
 Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field.
-Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA].
+Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA].
 Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
@@
 Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.
+Besides these more abstract conceptual implications, choosing a Bayesian approach has some practical advantages, as we will later illustrate with the posterior predictive checks (PPCs), which can only be calculated if a Bayesian approach is used.
 
-## Bayesian analysis
+## Bayesian analysis as alternative
 
@@
 After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%.
-After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%.
+After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%.
 If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
@@
 The $P(X| \theta)$ part is called likelihood function.
-In the *Journalism Studies* example, the likelihood function is based on rough rules from our experience and thus is not systematic.
+In the *IJOC* example, the likelihood function is based on rough rules from our experience and thus is not systematic.
 In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
-Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
+Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), which require no elaboration, 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
 
-We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount.
-The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper.
-<!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition.
---> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computers since the mid-1990s [@robert:2011:SHM].
-And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S].
-R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users.
+R interfaces to Stan (the probabilistic programming language for conducting MCMC), such as *brms* [@burkner2017advanced], can enable the derivation of the likelihood function (Part 2).
 But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE.
@@
 Part 3 (Prior) is arguably the most controversial part of Bayesian analysis.
-In the *Journalism Studies* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
+In the *IJOC* example, we can select a reasonable prior (or **informative** prior) of 24% from published information.
 Finding previous studies for an informative prior is the logical first thing to do.
@@
 And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g.
-@efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].
+@efron1986isn] and social scientists [e.g.
+@elff:2020:MAF].
 
-Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB].
+Undoubtedly, setting prior is consequential to the analysis.
 But the influence from priors is greatly weakened, when the data is getting bigger.
@@
 $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].
-The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).
 
@@
 @kovic:2017:B;@chan2020high] -->, these studies are not comparative.
-As far as we know, the only available comparative research in journalism studies that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE.
-We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.
-Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], one purpose of this paper is to demonstrate how to actually do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ).
+As far as we know, the only available comparative communication research that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE.
+We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.This paper demonstrates how to do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ).
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
@@
 The two examples below show how the Bayesian multilevel regression analysis can be deployed to the common archetypes of comparative journalism studies.
-The first example is an analysis of a comparative, non-stochastic content analytic dataset.
-The second example is an analysis of a comparative, stochastic survey dataset.
+The first example is an analysis of a comparative, stochastic survey dataset (WJS).
+This example was chosen to highlight the multilevel (non-atomicity) aspect and represent the situation of replication studies.
+The second example is an analysis of a comparative, non-stochastic content analytic dataset.
+This example was chosen to highlight the necessity of using the Bayesian approach to analyze non-stochastic comparative data and represent the situation of studies where noninformative priors were needed.
 
-# Example 1: useNews
+# Example 1: The Worlds of Journalism study
 
-We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a typical Bayesian multilevel regression analysis on a nonstochastic comparative dataset.
+In this example, the Bayesian approach is applied to a stochastic dataset from a randomized survey.
+The starting point of this example is the recent study by @hamada:2021:DJA.
+Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*.
+To rephrase this, the level of democracy in a country has an ecological effect on the journalists’ perceived professional autonomy.
+
+It is important to point out that the study is a replication.
+The same hypothesis has been studied in the earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA.
+The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.
+It is important to recite the operationalization of professional autonomy here.
+The two questions in the survey are: (1) “Thinking of your work overall, how much freedom do you personally have in selecting news stories you work on?” (2) “How much freedom do you personally have in deciding which aspects of a story should be emphasized?” The possible answers ranged from 5 = “complete freedom” to 1 = “no freedom at all”.
+The two answers were averaged.
+We will come back to this operationalization later in this article.
+
+Interestingly, the analytical approaches are also similar in the two studies.
+The study by @reich:2013:DJP contains multiple regression models on how journalist-level characters predict perceived professional autonomy.
+However, for country-level predictors such as Index of Democracy, @reich:2013:DJP apply an aggregated approach due to "methodological considerations" of "includ[ing] substantive country-level predictors in an OLS regression" (p.
+146).
+Effectively, the analysis boils down to aggregating the perceived professional autonomy of all journalists into mean values according to baskets of Index of Democracy and then comparing those mean values by ANOVA.
+The subsequent study by @hamada:2021:DJA applies the same aggregated approach by studying the bivariate correlation between the mean perceived professional autonomy of all journalists in a country and the Index of Democracy of a country.
+
+## Bayesian multilevel analysis of WJS
+
+Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression is a better approach.
+
+First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democratic performance on the journalist-level perceived professional autonomy.
+It allows for adjustment of other journalist-level predictors that are known to influence perceived professional autonomy, e.g.
+rank ($RANK$), experience ($XP$), gender ($GEN$), & having a university degree ($UNIV$).
+It also makes it possible to adjust for the possible confounding effects of other country-level variables.
+For example, GDP per capita (according to the World Bank) is moderately correlated with the Index of Democracy (r = `r cor(pts_tab$eiu, pts_tab$gdppc, use = "complete")`).
+The correlation between Index of Democracy ($DEMO$) and perceived professional autonomy ($PPA$) found by @reich:2013:DJP could be spurious and the GDP per capita were the actual determinant of perceived professional autonomy.
+We can adjust for the effect of GDP per capita by entering it also as an independent variable.
+The data can also provide such variance because there are countries with high GDP per capita but with low democracy (e.g.
+UAE and Qatar) and vice versa (e.g.
+Botswana and India).
+
+## Priors
+
+The idea of choosing priors is to select a probable probability distribution for each of unknown parameters in a model.
+Usually, the first step for choosing priors is to review previous studies and look for possible values to be used as our informative priors.
+Incorporating of prior information from @reich:2013:DJP in this Bayesian analysis makes the intention to replicate clearer.
+
+@reich:2013:DJP suggest that the relationship between Index of Democracy and perceived professional autonomy is in "J shape", with the average perceived professional autonomy of journalists in authoritarian regimes (the lowest end of democratic performance) being higher than those in hybrid regimes (3.92 vs 3.65).
+We can incorporate this prior information into our model by modeling a cubic relationship between Index of Democracy and perceived professional autonomy.
+Like the general procedure of conducting polynomial regression, we also create a parsimonious model assuming only a linear relationship to study whether the cubic regression improves the model fit.
+In other words, whether the relationship is really in "J shape" is studied <!-- [^jshape] -->.
+It’s important to spell out all the equations so that we can have a better idea of all the estimands.
+For the parsimonious model, the regression equations are:
+
+\begin{align}
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i + \epsilon_{ik} \\
+  \beta_{0} &= \gamma_{00} + \gamma_{01} DEMO_{k} + \gamma_{02} \log{GDP_{k}} + \mu_{0k}
+\end{align}
+
+For the cubic model, the regression equations are:
+
+\begin{align}
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i + \epsilon_{ik} \\
+  \beta_{0} &= \gamma_{00} + \gamma_{010} DEMO_{k} + \gamma_{011} DEMO^{2}_{k} + \gamma_{012} DEMO^{3}_{k}+ \gamma_{02} \log{GDP_{k}} + \mu_{0k}
+\end{align}
+
+From the model 4 in @reich:2013:DJP, we know that the standardized beta coefficients for the variables rank ($\beta_{1}$) and professional experience ($\beta_{2}$) are .15 and .07 respectively.
+Unfortunately, the associated standard errors (or standard deviations) were not reported but only asterisks representing statistical significance (p < 0.001 for rank, p < 0.01 for professional experience).
+We estimated the maximum standard deviation based on the significance level.
+For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving <!-- [^wald] -->:
+
+\begin{align}
+Pr(\frac{\beta'_{1}}{\sigma_{\beta'_{1}}}) &= \frac{0.001}{2} \sim \mathcal{N}(0, 1) \\
+\frac{\beta'_{1}}{\sigma_{\beta'_{1}}} &= 3.29 \\
+\frac{0.15}{\sigma_{\beta'_{1}}} &= 3.29 \\
+\sigma_{\beta'_{1}} &= 0.045
+\end{align}
+
+The above information can be used as an informative prior of the current analysis.
+Unfortunately, the ANOVA result in relation to $\gamma_{01}$ from @reich:2013:DJP cannot be used as the prior and we need to use weakly informative priors suggested by @lemoine:2019:M.
+For regression coefficients, e.g.
+$\gamma_{01}$, we used a normal distribution of $\mathcal{N}(0, 1)$.
+For variance terms, e.g.
+$\mu_{0k}$, a student t-distribution of $\mathcal{t}(3, 0, 2.5)$ was used.
+All, except the prior for regression coefficients, are default priors suggested by *brms*.
+In practice, we suggest pre-registering the priors before the data collection.
+As this is a secondary data analysis, we cannot do that.
+
+In order to make the result from this replication comparable to that of @reich:2013:DJP, we also calculate the standardized regression coefficients, i.e. all variables are mean-centered.
+
+### Other parameters
+
+Other parameters such as *adapt_delta* control how the MCMC should be performed.
+It is in general safe to use the default values unless MCMC shows evidence of nonconvergence.
+We provide a short guide on how to diagnose convergence (online appendix).
+
+## Modeling
+
+For this analysis, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression.
+In the disaggregation case, the multilevel structure is ignored and the regression equations become:
+
+\begin{align}
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} + \epsilon_{i}
+\end{align}
+
+\begin{align}
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} \\ + \beta_{7} DEMO^2_{k} + \beta_{8} DEMO^3_{k} + \epsilon_{i}
+\end{align}
+
+It is important to remind our readers that the results from the three are likely to be similar, but it is not evidence for the disaggregation approach and the MLE approach is a replacement of the Bayesian approach [@morey:2015].
+The interval estimates have different meanings and can’t be directly compared.
+Comparing the three approaches, the disaggregation approach is the least useful because it violates the underlying independence assumption.
+
+## Results
+
+The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficients.
+It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution.
+By default, *brms* displays the mean and the 95\% High Density Interval (HDI).
+<!-- [^5] --> These two values represent the point and interval estimates of the regression coefficient.
+
+<!-- [^5]: HDI is one representation of the Bayesian credible interval.
+There should be no "correct" choice of the level of credibility but some established conventions.
+We choose, like many published works [e.g.
+@stegmueller:2013:HMC<\!-- ; @kovic:2017:B; @chan2020high -\->], the default value of 95\%.
+However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
+-->
+
+```{r}
+wjs_reg <- readRDS("wjs_reg.RDS")
+wjs_reg$term <- c("(Intercept)", "Experience", "Rank", "Gender (Female)", "University Degree", "Index of Democracy", "GDP per capita")
+colnames(wjs_reg)[2:4] <- c("Bayesian", "MLE", "Disaggregation")
+apa_table(wjs_reg, caption = "Point and interval estimates from WJS analysis using three different analytic strategies: Bayesian multilevel modeling, multilevel modeling using MLE, and Disaggregation approach")
+```
+
+By looking at the regression coefficient and the 95\% HDI of the parsimonious model (Table 1), the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34).
+The Index of Democracy is the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
+It supports @hamada:2021:DJA's h2a.
+
+By comparing the point and interval estimates using different approaches, point estimates are remarkably similar.
+Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods.
+It is like previous studies [@stegmueller:2013:HMC; @elff:2020:MAF].
+While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
+The Bayesian approach allows us to say that *given the observed data, the true estimate of the standardized regression coefficient has 95% probability of falling within  0.13 and 0.34*.
+In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true estimate of the standardized regression coefficient*.
+One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
+This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.
+
+### J Shape
+
+<!-- Regarding the possible "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194) [^loo].
+-->By looking at the conditional effects plot of the cubic model (Figure \@ref(fig:fig5)), it suggests that the relationship is not "J shape" [^loo].
+<!-- On average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.
+-->
+
+```{r fig5, echo = FALSE, fig.cap = 'Conditional effects plot showing no "J shape" relationship between perceived professional autonomy and Index of Democracy.'}
+require(ggplot2)
+x <- readRDS("qmod_condit.RDS")
+x$`eiu` + xlab("Index of Democracy (mean-centered)") + ylab("Perceived professional autonomy (mean-centered)") + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
+```
+
+[^jshape]: Actually, the replication by @hamada:2021:DJA has shown that the relationship is not in such J shape. But we were assumed to be in the time point before such replication.
+
+[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See the online appendix for the analysis.
+
+### Posterior predictive checks
+
+One unique feature of the Bayesian approach is posterior predictive checks (PPC) for studying how our model works.
+Bayesian analysts have a strong culture of model checking [e.g.
+@mimno:2015:P; @gelman2007comment], while many analyses – not only in communication research – end with regression tables and inferences.
+
+A good model for theory testing should pin down the data-generating process in the real world, not just whether the model fits the data.
+Therefore, a good model should be able to generate simulated data that are like the observed data [@gelman2007comment].
+The gist of posterior predictive check is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original observed data ($y$).
+A good model should display a similar probability distribution of $y_{rep}$ and $y$.
+(Figure \@ref(fig:fig3) ).
+
+As one can see in Figure \@ref(fig:fig3), the fitted model can get the range and the peak of the original data about right.
+But the model can only give simulated data $y_{rep}$ with a gaussian distribution whilst the shape of the original data $y$ is not gaussian at all.
+The finger-like shape is a manifestation of analyzing the two ordinal variables (two Likert items) as if they were in an interval scale.
+With this check, it shows the original analytic scheme of both @reich:2013:DJP and @hamada:2021:DJA cannot capture the shape of the data.
+Also, the psychological distances between two neighboring options in a Likert scale (e.g.
+“complete freedom” and “a great deal of freedom”) are not the same across all pairs and one can’t assume that Likert items can be summed or averaged [@buerkner:2019:ORM].
+
+```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data based on the parsimonious model"}
+readRDS("ppa_mod_ppc.RDS")
+```
+
+If this were not a replication and one didn't need to accept the previous operationalization of perceived professional autonomy, a better way to answer this research question using the WJS data is to make two modifications.
+First, one should use the ordinal regression technique to model the responses from Likert items [@buerkner:2019:ORM].
+Second, the two Likert items related to perceived professional autonomy can be modeled jointly using a multivariate regression model [^MULTIVARIATE].
+
+[^MULTIVARIATE]: Please notice we are not talking about *multiple* regression regression.
+
+As an exploratory analysis, we fitted a Bayesian model with these two modifications (see Online Appendix).
+And indeed the posterior predictive check of the model suggests that the modified model is better at pinning down the data-generating process of the Likert items than the unmodified model: the new model correctly pins down both the range, peaks and shape of the original data (Figure \@ref(fig:clplot)).
+The bottom line is the same: democratic performance of a country is still a strong predictor of journalists’ perceived professional autonomy in the modified model, although the magnitude of influence is not as great as shown by the unmodified model displayed in table 1.
+
+```{r clplot, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data based on the multivariate ordinal model"}
+require(cowplot)
+c9c10ppc <- readRDS("ppa_clmod_ppc.RDS")
+c9c10ppc[[1]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in selecting news stories you work on?") -> c9gg
+c9c10ppc[[2]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in deciding which aspects of a story should \n be emphasized?") -> c10gg
+plot_grid(c9gg, c10gg, ncol = 1)
+```
+
+# Example 2: useNews
+
+We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a Bayesian multilevel regression analysis on a nonstochastic comparative dataset.
 The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage?
-In other words, we studied the ecological effect of the distance from China on the frequency of China coverage.
-Several distance measures were used to formulate our pre-registered hypotheses: physical distance between two capitals, trade volume between two countries, and cultural distance between two societies.
+In other words, we hypothesized that there is an ecological effect between a closer distance to China and an increased frequency of China coverage.
+Several distance measures were used to formulate our pre-registered hypotheses<!-- : physical distance between two capitals, trade volume between two countries, and cultural distance between two societies -->.
+Due to limited space, only the analysis of trade volume between two countries is displayed here.
+For other analyses, please refer to the online appendix.
 
-For demonstrative purposes, our analysis was separated into two levels: outlet-level analysis and article-level analysis.
+For demonstrative purposes, our analysis was separated into two levels: outlet-level analysis (here) and article-level analysis (in the Online Appendix).
 The outlet-level analysis is an aggregated version of article-level analysis.
@@
 
-We used only the data from 2019 as the baseline.
-<!-- It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year.
-Also, it was at the zenith of the US-China trade war.
--->
-
-We excluded media outlets that contributed <1,000 articles in that year.
+We used only the data from 2019 as the baseline<!-- .
+We --> and excluded media outlets that contributed <1,000 articles in that year.
 This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated.
-In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included.
-These 61 media outlets contributed 1,525,871 articles.
+In total, <!-- 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included.
+These --> 61 media outlets contributed 1,525,871 articles.
 
@@
 The data contains a count of articles covering China ($z$), total number of articles ($n$), country of the outlet($k$), and distance measures ($x$).
-
-In the article-level analysis, the data has 1,525,871 rows and each row represents an article.
-The data contains a binary dependent variable of China coverage ($y$), media outlet($j$), country of the outlet($k$), and distance measures ($x$).
 
@@
 
-## Distance measures
+## Distance measure: Trade volume
 
-Several distance measures were used as the independent variable to test our central research questions: physical distance, trade volume, and cultural distance.
-Physical distance is calculated as the Great-circle distance between Beijing and the capital of the hosting city of the media outlet (e.g.
-Bucharest).
 The volumes of import to and export from China with the host country of a media outlet was extracted from the 2019 edition of China Statistical Yearbook (http://www.stats.gov.cn/tjsj/ndsj/2019/indexeh.htm).
-Cultural distance from China to the host country of a media outlet was extracted from culturaldistance.com, which was calculated using the data from World Value Survey with the algorithm from @bell:2009:C.
-All of these distance measures were log-transformed, because previous studies showed the relationship between news coverage and these distance measures is not linear [@grasland:2019:I;@wu:2000:SDI].
-
-## Modeling
-
-For all analyses, we tried 3 different approaches: 1) Disaggregation approach (ignoring the multilevel structure); 2) Multilevel regression using MLE; and 3) Bayesian multilevel regression.
-It is important to remind our readers that the results from the three are likely to be similar, but it is not evidence for the disaggregation approach and the MLE approach is a replacement of the Bayesian approach [@morey:2015].
-It is because the disaggregation approach commits atomistic fallacy and the MLE approach ignores the non-stochastic nature of the data.
+This measure was log-transformed, because previous studies showed the relationship between news coverage and these distance measures is not linear [@grasland:2019:I;@wu:2000:SDI].
 
@@
 
-We used negative binomial regression for this analysis.
-Media outlets are nested in countries (e.g.
-*Der Standard* and *Österreichischer Rundfunk* are nested in Austria).
+We used negative binomial regression for this analysis [^EXT].
+Media outlets are nested in countries <!-- (e.g.
+*Der Standard* and *Österreichischer Rundfunk* are nested in Austria) -->.
 Thus, a country-based variance is added ($\mu_{0k}$).
 We also added $\log{n_{j}}$ as an offset value.
-An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation \@ref(eq:2).
+An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation.
 Effectively, we modeled the *rate* of China coverage.
@@
 
-\begin{align}
-\log{z_{jk}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \log{n_j} + \epsilon_{jk} \\
-\log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} +  \epsilon_{jk} \\
-\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} x_{k} + \epsilon_{jk}\end{align}
-
-The estimand of interest, $\gamma_{01}$, is interpreted as the average unit change in the log rate of China coverage, $\log\frac{z_{jk}}{n_{j}}$, for each unit change in the distance measure of the outlet $k$.
-
-In the disaggregation case, the multilevel structure is ignored and the regression equation becomes:
+[^EXT]: We propose four extensions: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes (online appendix).
 
 \begin{align}
-\log\frac{z_{jk}}{n_{j}} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{j}
-\end{align}
+\log{z_{jk}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} + \log{n_j} + \epsilon_{jk} \\
+\log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} +  \epsilon_{jk} \\
+\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} + \epsilon_{jk}\end{align}
 
-We named the models with different independent variables as model A1-4 respectively (A1: log import volume; A2: log export volume; A3: log physical distance; A4: log cultural distance).
-
-### Article-level analysis
-
-We used logistic regression for this analysis.
-However, due to the computational time needed to conduct the Bayesian regression in this case (it took 4 days on a regular computer), we only did the model with import volume as the independent variable.
-
-In this analysis, an article is nested in its media outlet.
-The media outlet is in turn nested in its country.
-Two variance terms ($\mu_{0j}$ and $\mu_{00k}$) are needed.
-The multilevel regression equations are:
-
-\begin{align}
-p_{ijk} &= Pr(y_{ijk} = 1) \\
-L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
-L_{ijk} &= \pi_{0} + \epsilon_{ijk} \\
-\pi_{0} &= \beta_{00} + \mu_{0j} \\
-\beta_{00} &= \gamma_{000} + \mu_{00k} + \gamma_{001} x_{k}
-\end{align}
-
-In the disaggregation case, the multilevel structure is ignored and the regression equations become:
-
-\begin{align}
-p_{ijk} &= Pr(y_{ijk} = 1) \\
-L_{ijk} &= \log{\frac{p_{ijk}}{1 - p_{ijk}}} \\
-L_{ijk} &= \beta_{0} + \beta_{1} x_{k} + \epsilon_{ijk}
-\end{align}
-
-We named this model as model B1.
+The estimand of interest, $\gamma_{01}$, is interpreted as the average unit change in the log rate of China coverage, $\log\frac{z_{jk}}{n_{j}}$, for each unit change in the log distance measure of the outlet $k$ with China.
 
@@
 
-For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$.
-For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ and $\mu_{0j}$.
-The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.
-
-Usually, the first step for choosing priors is to review previous studies and look for possible values to be used as our informative priors.
-Although @wu:2000:SDI is a possible reference point, we select not to use this because China was not studied.
-Also, the modeling technique was quite different from the current one.
-
-In this analysis, we used weakly informative priors suggested by @lemoine:2019:M.
-
-For regression coefficients, e.g.
-$\gamma_{00}$, we used a normal distribution of $\mathcal{N}(0, 1)$.
-For variance terms, e.g.
-$\mu_{0k}$, a student t-distribution of $\mathcal{t}(3, 0, 2.5)$ was used.
-A gamma distribution of $\mathcal{Gamma}(0.01, 0.01)$ was used for the shape parameter $\phi$.
-
-All, except the prior for regression coefficients, are default priors suggested by *brms*.
-
-### Other parameters
-
-Other parameters for Bayesian multilevel regression analysis control how the MCMC should be performed.
-Three parameters are important: number of iterations, number of chains and *adapt_delta*.
-They are not some magic numbers that you can plug and play.
-However, it is in general safe to use the default values, i.e.
-number of iterations = 2000, number of chains = 4 and *adapt_delta* = 0.8, unless MCMC shows evidence of nonconvergence.
-*brms* is smart enough to suggest how to adjust these three values.
-Nonetheless, we provide a short guide on how to diagnose convergence.
+There are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$.
+Although @wu:2000:SDI is a possible reference point, we select not to use this as priors because China was not studied.
+<!-- Also, the modeling technique was quite different from the current one.
+--> In this analysis, we used weakly informative priors suggested by @lemoine:2019:M.
+The priors were the same as the ones used in Example 1.
+An additional gamma distribution of $\mathcal{Gamma}(0.01, 0.01)$ was used for the shape parameter $\phi$.
 
@@
 
-Table \@ref(tab:t1) shows a summary of all models from the outlet-level analysis using three different ways of modeling.
-The Bayesian multilevel regression gave the *posterior distribution*, $P(\theta | X)$, of the regression coefficient ($\gamma_{001}$).
-It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution.
-By default, *brms* displays the mean and the 95\% high density interval (HDI).
-[^5] These two values represent the point and interval estimates of the regression coefficient.
+Table 2 shows a summary of all models from the outlet-level analysis using three different ways of modeling.
+Similar to Example 1, three methods give a similar point estimate but a wider interval estimate from the Bayesian model.
 
-[^5]: HDI is one representation of the Bayesian credible interval.
-There should be no "correct" choice of the level of credibility but some established conventions.
-We choose, like many published works [e.g.
-@stegmueller:2013:HMC<!-- ; @kovic:2017:B; @chan2020high -->], the default value of 95\%.
-However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing].
-<!-- Some Bayesians, notably Andrew Gelman, report very liberal 50\% credible intervals.
-@mcelreath2020statistical selects 89\% to show the arbitrariness of the practice.
-@leeuw:2020:AAT select 90\%.
--->
-
-Consistently, point estimates are remarkably similar.
-Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods.
-It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF].
-The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting of China.
-While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
-The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*.
-In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true estimate of log import volume*.
-One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
-This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.
-
-Table: (\#tab:t1) Point and interval estimates from outlet-level analysis using three different analytic strategies: Disaggregation approach, multilevel modeling using MLE and Bayesian multililevel modeling
-
-| Model                           | Disaggregate ($\beta_{1}$, 95\% CI) | MLE ($\gamma_{01}$, 95\% CI) | Bayesian ($\gamma_{01}$, 95\% HDI) |
-|:--------------------------------|:------------------------------------|------------------------------|------------------------------------|
-| Model A1: Log import volume     | 0.25 (0.18, 0.33)                   | 0.25 (0.18, 0.33)            | 0.25 (0.18, 0.33)                  |
-| Model A2: Log export volume     | 0.22 (0.14, 0.30)                   | 0.22 (0.13, 0.31)            | 0.22 (0.11, 0.33)                  |
-| Model A3: Log Physical distance | -0.02 (-0.34, 0.24)                 | -0.10 (-0.55, 0.31)          | -0.12 (-0.63, 0.39)                |
-| Model A4: Log Cultural distance | -0.45 (-1.26, 0.34)                 | -0.60 (-1.80, 0.55)          | -0.62 (-2.12, 0.78)                |
-
-Model B1 confirms the above again (Table \@ref(tab:t2) ). Therefore, both article- and outlet-level analyses arrive at the same conclusion.
-
-<!-- ```{r t2, results = "asis"} -->
-<!-- ### TODO: to prim it further -->
-<!-- require(brms) -->
-<!-- require(parameters) -->
-<!-- require(dplyr) -->
-<!-- article_level <- readRDS("import_logit.RDS") -->
-<!-- article_level %>% parameters(ci = 0.95, effects = "fixed", dispersion = TRUE, centrality = "mean", test = "pd") %>% as.data.frame -> res -->
-
-<!-- res %>% dplyr::select(Parameter, Mean, SD, CI_low, CI_high) %>% rename(Estimate = Mean) %>% knitr::kable(format = "markdown", caption = "Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country", digits = 2) -->
-<!-- ``` -->
-
-Table: (\#tab:t2) Bayesian multilevel logistic regression analyzing the article-level likelihood of China coverage in relation to log import volume of the outlet's country
-
-| Parameter                          | Estimate | SD   | 95 \%HDI       |
-|:-----------------------------------|:---------|------|----------------|
-| $\gamma_{000}$ (Intercept)         | -7.06    | 0.81 | (-8.61, -5.44) |
-| $\gamma_{001}$ (Log import volume) | 0.27     | 0.06 | (0.16, 0.38)   |
-
-### Diagnosis of convergence
-
-It is important to confirm the model is converged. We demonstrate how to confirm this with model A1.
-
-The first step is Gelman-Rubin convergence diagnostic [@brooks:1998:GMM; @vehtari:2020:RNF].
-*brms* displays this in the form of $\widehat{R}$.
-In general, $\widehat{R} \approx 1$.
-The model might not have converged, when $\widehat{R} \ge 1.01$ [@vehtari:2020:RNF].
-The *summary()* function of brms displays the $\widehat{R}$ for each of the estimated unknown parameters.
-All parameter estimates have a $\widehat{R} = 1.0$.
-
-The second step is the MCMC trace plot (can be obtained with the function *plot()*).
-The traceplot should display the so-called "fuzzy caterpillar" pattern (Figure \@ref(fig:fig1)).
-There should be no breakage.
-
-```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy caterpillar pattern."}
-require(brms)
-import_brms <- readRDS("import_brms.RDS")
-plot(import_brms)
+```{r}
+import_reg <- readRDS("import_reg.RDS")
+import_reg$term <- c("(Intercept)", "Log (Trade Volume)")
+colnames(import_reg)[2:4] <- c("Bayesian", "MLE", "Disaggregation")
+apa_table(import_reg, caption = "Point and interval estimates from outlet-level analysis using three different analytic strategies: Bayesian multilevel modeling, multilevel modeling using MLE, and Disaggregation approach")
 ```
 
-An additional check is to study the autocorrelation of all chains.
-The correlogram should display low serial correlation (successive high correlation).
-The function *mcmc_plot* can be used to plot this (Figure \@ref(fig:fig2)).
+### Posterior predictive checks
 
-If the diagnostics show evidence of nonconvergence, it is suggested to increase the number of iterations and number of chains.
+Similar to the previous example, we conducted the posterior predictive check (Figure  \@ref(fig:fig3x)).
+Our model can capture both the range, peak and shape of the original data.
+But there are many variations in the simulated data, probably due to the fact that the Bayesian model is based on just 61 data points and one single predictor.
 
-```{r fig2, echo = FALSE, fig.cap = "Correlogram of four chains showing no significant higher-order lag"}
-mcmc_plot(import_brms, type = "acf")
-```
-
-### Further diagnostics
-
-There are <!-- several --> two diagnostic checks that we can do to make sure our model is valid.
-
-<!-- * Increasing number of iterations -->
-
-<!-- The first test is to increase the number of iterations from 2000 to a higher value, e.g.
-4000, and see if the result is consistent with the initial analysis.
-This check makes sure our result is not transient due to short iteration time.
--->
-
-<!-- Increasing the number of iterations did change a bit of the estimates, but only at the second decimal place. It shows that the results are consistent between the two analyses. -->
-
-* Using another weakly informative prior
-
-We can also use another weakly informative prior to see how our initial choice influences the result.
-We tried another weakly informative prior for the regression coefficients, $\mathcal{t}(1, 0, 0.25)$ [@gelman:2008].
-Similarly, changing prior only impacts the second decimal place of the estimates.
-
-* Posterior predictive checks
-
-We can use posterior predictive checks to study how our model fits our data.
-The gist of the method is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original data ($y$).
-A good model should display a similar probability distribution of $y_{rep}$ and $y$.
-It can be done with the function *pp_check()* (Figure \@ref(fig:fig3) ).
-
-```{r fig3, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
+```{r fig3x, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
 pp_check(import_brms, ndraws = 100)
 ```
-
-## Extensions
-
-We propose four extensions to the above barebone analysis: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes.
-The analyses in these extensions are not preregistered.
-Please refer to the online appendix for these extensions.
-
-# Example 2: The Worlds of Journalism study
-
-Example 1 above demonstrated how to conduct a Bayesian multilevel regression analysis.
-In this example, the same approach is applied to a stochastic dataset from a randomized survey.
-The starting point of this example is the recent study by @hamada:2021:DJA.
-Using the second wave data from WJS (2012-2016), the study seeks to study this hypothesis (the H2a in the paper): *The greater the level of democracy in a country, the more perceived professional autonomy journalists enjoy*.
-
-It is important to point out that the study is actually a replication.
-The same hypothesis has been studied in an earlier study by @reich:2013:DJP, which uses the first wave data from WJS and has a remarkably similar title to that of @hamada:2021:DJA.
-The earlier study has studied this hypothesis (the H4): *Journalists’ perceived professional autonomy is positively associated with democratic performance and press freedom, and it is negatively related to political parallelism and state intervention.* The operationalizations of both professional autonomy (based on two questions in WJS) and level of democracy (based on the Economist Intelligence Unit's Index of Democracy) are the same in the two studies.
-
-Interestingly, the analytical approaches are also similar in the two studies.
-The study by @reich:2013:DJP contains multiple regression models on how journalist-level characters predict perceived professional autonomy.
-However, for country-level predictors such as Index of Democracy, @reich:2013:DJP apply an aggregated approach due to "methodological considerations" of "includ[ing] substantive country-level predictors in an OLS regression" (p.
-146).
-Effectively, the analysis boils down to aggregating the perceived professional autonomy of all journalists into mean values according to baskets of Index of Democracy and then comparing those mean values by ANOVA.
-The subsequent study by @hamada:2021:DJA applies the same aggregated approach by studying the bivariate correlation between the mean perceived professional autonomy of all journalists in a country and the Index of Democracy of a country.
-
-There are two weaknesses of the aggregated approach.
-First, a massive amount of information at the author-level was discarded and cannot leverage the hierarchical structure of the data.
-As shown in @reich:2013:DJP, author-level variables such as year of experience and being in a management position are also predictive of perceived professional autonomy.
-Taking the aggregated approach assumes that all of these author-level variables are homogeneous across countries.
-This assumption could create spurious correlation when the distribution of author-level variables is associated with contextual factors, e.g.
-Index of Democracy.
-Second, the two hypotheses specified in the two quoted studies refer to the perception at the micro-level ("the perceived professional autonomy journalists enjoy", "Journalists’ perceived professional autonomy"), not at the macro-level (e.g.
-the average level of perceived professional autonomy of journalists in a country).
-Interpreting the macro-level association wrongly at the micro-level leads to ecological fallacy.
-
-## Bayesian analysis of WJS
-
-Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data.
-Bayesian multilevel regression is probably the only valid approach.
-First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democracy performance on the journalist-level perceived professional autonomy.
-Second, the incorporating of prior information from @reich:2013:DJP makes the intention to replicate clearer.
-
-From the model 4 in @reich:2013:DJP, we know that the standardized beta coefficients for the variables rank and professional experience are .15 and .07 respectively.
-Unfortunately, the associated standard errors (or standard deviations) were not reported but only asterisks representing statistical significance (p < 0.001 for rank, p < 0.01 for professional experience).
-We estimated the maximum standard deviation based on the significance level.
-For example, the standard deviation of the standardized regression coefficient ($\sigma_{\beta'_{1}}$) of rank can be estimated by solving <!-- [^wald] -->:
-
-\begin{align}
-Pr(\frac{\beta'_{1}}{\sigma_{\beta'_{1}}}) &= \frac{0.001}{2} \sim \mathcal{N}(0, 1) \\
-\frac{\beta'_{1}}{\sigma_{\beta'_{1}}} &= 3.29 \\
-\frac{0.15}{\sigma_{\beta'_{1}}} &= 3.29 \\
-\sigma_{\beta'_{1}} &= 0.045
-\end{align}
-
-The above information can be used as an informative prior of the current analysis.
-Unfortunately, the ANOVA result from @reich:2013:DJP cannot be used as the prior and we still need to use weakly informative prior.
-However, @reich:2013:DJP suggest that the relationship between Index of Democracy and perceived professional autonomy is in "J shape", with the average perceived professional autonomy of journalists in authoritarian regimes (the lowest end of democracy performance) being higher than those in hybrid regimes (3.92 vs 3.65).
-We can incorporate this prior information into our model by modeling a cubic relationship between Index of Democracy and perceived professional autonomy.
-Similar to the general procedure of conducting polynomial regression, we also create a parsimonious model assuming only a linear relationship to study whether the cubic regression improves the model fit.
-In other words, whether the relationship is really in "J shape" is studied [^jshape].
-
-```{r, echo = FALSE}
-pts_tab <- readRDS("pts_tab.RDS")
-```
-
-Another advantage of taking a Bayesian multilevel regression approach rather than the bivariate approach as in @reich:2013:DJP is the possibility to adjust for the possible confounding effects of other marco-level variables.
-For example, GDP per capita (according to the World Bank) is moderately correlated with the Index of Democracy (r = `r cor(pts_tab$eiu, pts_tab$gdppc, use = "complete")`).
-The correlation between Index of Democracy and perceived professional autonomy found by @reich:2013:DJP could be spurious and the GDP per capita were the actual determinant of perceived professional autonomy.
-We can adjust for the effect of GDP per capita by entering it also as an independent variable.
-The data can also provide such variance because there are countries with high GDP per capita but with low democracy (e.g.
-UAE and Qatar) and vice versa (e.g.
-Botswana and India).
-
-In order to make the result from this replication comparable to that of @reich:2013:DJP, we also calculate the standardized regression coefficients, i.e.
-all variables are mean-centered before entering into the regression model.
-
-By looking at the regression coefficient and the 95\% HDI, the standardized regression coefficient for Index of Democracy is 0.24 (95\% HDI: 0.13 to 0.34).
-The Index of Democracy is not only a substantial predictor as 0 is not covered by the 95% HDI but also the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
-It supports @hamada:2021:DJA's h2a, but our model does that without the problem of the aforementioned ecological fallacy and with adjustment for other potential confounders.
-
-Regarding the possible "J shape" relationship suggested by @reich:2013:DJP, we compare the model fit ($R^{2}$) of the cubic model and the parsimonious model and the cubic model provides no improvement in model fit over the parsimonious model (both: 0.194) [^loo].
-By looking at the conditional effects plot (Figure \@ref(fig:fig5)), it also suggests that the relationship is not "J shape".
-On average, a journalist in countries that scored a lower Index of Democracy has a lower perceived professional autonomy.
-
-```{r fig5, echo = FALSE, fig.cap = 'Conditional effects plot showing no "J shape" relationship between perceived professional autonomy and Index of Democracy.'}
-require(ggplot2)
-x <- readRDS("qmod_condit.RDS")
-x$`eiu` + xlab("Index of Democracy (mean-centered)") + ylab("Perceived professional autonomy (mean-centered)") + theme_minimal() + scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2")
-```
-
-<!-- [^wald]: Here we used the z-approximation of Wald test rather than the more typical t-distribution-based Wald test because the degree of freedom (df) is not reported.
-And t-distribution approximates z-distribution asymptotically when df gets larger.
--->
-
-[^jshape]: Actually, the replication by @hamada:2021:DJA has shown that the relationship is not in such J shape. But we were assumed to be in the time point before such replication.
-
-[^loo]: Another way to evaluate the model fit is to use leave-one-out cross validation. See the online appendix for the analysis.
 
@@
 We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
-Using a Bayesian approach, however, has also clearly some disadvantages.
-Researchers have to define priors in order to run a Bayesian regression analysis.
-As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters.
-If we have prior knowledge it allows us to create even better models, as Example 2 has shown.
-Furthermore, it takes more time to get the results of a Bayesian regression analysis.
+We mainly used the WJS dataset to illustrate the strength of multilevel models, whereas the useNews dataset was selected as an example where Bayesian models are conceptually the better choice.
+However, both multilevel models and Bayesian analysis are connected approaches.
+
+First of all, both examples require a multilevel approach.
+We believe this is not an optional choice.
+The question then is why we should use a Bayesian approach as these models can also be estimated with a frequentist approach.
+As the useNews dataset represents a census-like situation, we argue a Bayesian approach is more appropriate.
+Of course, as the argument about the theoretical superpopulation shows, one could always justify a frequentist approach.
+However, there are also several practical reasons why a Bayesian approach is more suitable than a default approach.
+
+First, the Bayesian interpretation of CIs is far more intuitive than the frequentist interpretation [@morey:2015].
+Secondly, while all the models reported here can also be estimated within a frequentist framework, using a Bayesian framework and, more specifically, brms allows estimating them all with the same package.
+This also makes it easier to compare different competing models, as we have illustrated in our analysis.
+Third, comparing models and checking the predictive quality of the models is an essential part of a Bayesian framework.
+Of course, frequentist models can also be compared based on information criteria such as the BIC.
+However, PPCs that give by far the most detailed information about models and indicate in which area they potentially fail are only possible by using a Bayesian approach.
+Finally, while we discussed the question about priors as a potential challenge of Bayesian models, they are instead a strength of Bayesian models.
+Researchers must define priors to run a Bayesian regression analysis.
+As we could show, this limitation does not pose a controversial challenge as weakly informative priors can be chosen, and in most cases, enough data is available.
+Thus, the priors have almost no influence on the posterior distribution of the parameters.
+Moreover, if we have prior knowledge, it allows us to create even better models, as the first example has shown.
+
+Using a Bayesian approach still has several limitations.
+First, it takes more time to get the results of a Bayesian regression analysis.
 Estimating a Bayesian regression model is a computationally demanding task.
-It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 1, Model B1).
-Still, eventually it worked and typical studies in comparative journalism research [e.g.
-6,525 articles in @esser:2013:C or 27,567 journalists in Example 2] can be estimated within a reasonable time frame [^TIME].
+It took four days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 2, article-level analysis).
+Still, eventually, it worked, and typical studies in comparative journalism research [e.g.
+27,567 journalists in Example 1] can be estimated within a reasonable time frame.
+Secondly, if sampling procedures are used for a typical experimental design that could be replicated, using a frequentist approach is probably the less complicated approach and  a valid choice if combined with a preregistration of the hypotheses [@schaefer:2019:MES] [^PREREG].
+In any other scenario, we believe the benefits of the Bayesian approach outweigh the potential limitations.
 
-[^TIME]: We benchmarked the same model B1 but with subsets of data of some more "typical" sample sizes.
-A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 8-core computer.
-Although it is comparatively more computational intensive than *lme4*, the time needed is still reasonable.
+[^PREREG]: Even using the Bayesian approach, hypotheses should also be preregistered.
+
+# Coda: A radical education reform proposal
+
+@rinke:2018:PMA advocate a different teaching of statistics for communication research.
+In their opinion, the teaching of frequentist hypothesis testing would be less central.
+“Instead, more substantive concerns, replication, effect sizes, and better ways of drawing statistical inferences, including Bayesian methods, would take center stage.” [@rinke:2018:PMA, p.
+18] We concur with their proposal and hope that this paper can convince the educators of our field to teach Bayesian methods to future communication researchers.
+Unlike what it was several years ago, we now have communication studies using the Bayesian approach published in top communication journals.
+Software and educational materials for doing Bayesian analysis have been tremendously improved.
+We see the availability of the R package *brms* [@burkner2017advanced] and approachable textbooks such as *Statistical Rethinking* [@mcelreath2020statistical] as watershed moments in the (re)mainstreamization of the Bayesian approach.
+Based on the recent development and the conclusion of this paper, we would like to make an even more radical education reform proposal than @rinke:2018:PMA’s: We should teach the Bayesian approach as the default way of drawing statistical inferences.
+The frequentist approach should instead be taught as an option specifically for the analysis of stochastic data from studies such as media experiments and simple random surveys.
+When it comes to teaching regression analysis, we should teach the statistical issues concerning the non-atomicity of the data, as well as the necessity of model checking with procedures such as posterior predictive checks.
 

### 2023-01-02 extension.rmd
Address most of the reviewers' comments

@@
 require(parameters)
+require(cowplot)
 import_brms <- readRDS("import_brms.RDS")
+import_brms_poisson <- readRDS("import_brms_poisson.RDS")
 ```
@@
 
-## Expression of outlet-level models in lme4 and brms
+## Example 1
 
-```r
-require(brms)
-require(lme4)
-# brms
-brm(z ~ offset(log(n)) + (1|k)+log(x),
-          family = negbinomial(), data = outlet_data)
-# lme4
-glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
-```
+### Estimation of prior
 
-## Expression of disaggregated outlet-level model in MASS
-
-```r
-require(MASS)
-glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
-```
-
-## Expression of article-level models in lme4 and brms
-
-```r
-brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
-glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
-```
-
-## Expression of disaggregated article-level model in MASS
-
-```r
-glm(y ~ log(x), family = binomial(), data = article_data)
-```
-
-## Setting up weakly informative prior in the brms model
-
-```r
-weaklyinformative_prior <- c(prior_string("normal(0, 1)",
-                                          class = "b"),
-                             prior_string("normal(0, 1)",
-                                          class = "Intercept"))
-# The sample_prior argument is optional. But useful for further analysis.
-import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
-          data = outlet_data, family = negbinomial(),
-          prior = weaklyinformative_prior, sample_prior = TRUE)
-import_brms
-```
-
-## WJS: Estimation of prior
+Determination of prior based on the level of significance.
 
@@
 
-## WJS: Full code
+### Full code
 
@@
 
-# Multivariate regression of Example 1
+## Example 2
 
-Source code:
+### Expression of outlet-level models in lme4 and brms
+
+As below
+
+```r
+require(brms)
+require(lme4)
+# brms
+brm(z ~ offset(log(n)) + (1|k)+log(x),
+          family = negbinomial(), data = outlet_data)
+# lme4
+glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
+```
+
+### Expression of disaggregated outlet-level model in MASS
+
+As below
+
+```r
+require(MASS)
+glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
+```
+
+## Expression of article-level models in lme4 and brms
+
+As below
+
+```r
+brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
+glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
+```
+
+### Expression of disaggregated article-level model in MASS
+
+As below
+
+```r
+glm(y ~ log(x), family = binomial(), data = article_data)
+```
+
+### Setting up weakly informative prior in the brms model
+
+As below
+
+```r
+weaklyinformative_prior <- c(prior_string("normal(0, 1)",
+                                          class = "b"),
+                             prior_string("normal(0, 1)",
+                                          class = "Intercept"))
+# The sample_prior argument is optional. But useful for further analysis.
+import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
+          data = outlet_data, family = negbinomial(),
+          prior = weaklyinformative_prior, sample_prior = TRUE)
+import_brms
+```
+
+# Finger-like shape of Example 1 and multivariate regression
+
+The finger-like shape is a manifestation of analyzing the two ordinal variables (two Likert items) as if they were in an interval scale.
+The PPC shows the original analytic scheme of both @reich:2013:DJP and @hamada:2021:DJA cannot capture the shape of the data.
+Also, the psychological distances between two neighboring options in a Likert scale (e.g.
+"complete freedom" and "a great deal of freedom") are not the same across all pairs and one can’t assume that Likert items can be summed or averaged [@buerkner:2019:ORM].
+
+If this were not a replication and one didn't need to accept the previous operationalization of perceived professional autonomy, a better way to answer this research question using the WJS data is to make two modifications.
+First, one should use the ordinal regression technique to model the responses from Likert items [@buerkner:2019:ORM].
+Second, the two Likert items related to perceived professional autonomy can be modeled jointly using a multivariate regression model.
+
+As an exploratory analysis, we fitted a Bayesian model with these two modifications (see Online Appendix).
+And indeed the posterior predictive check of the model suggests that the modified model is better at pinning down the data-generating process of the Likert items than the unmodified model: the new model correctly pins down both the range, peaks and shape of the original data (Figure \@ref(fig:clplot)).
+The bottom line is the same: democratic performance of a country is still a strong predictor of journalists’ perceived professional autonomy in the modified model, although the magnitude of influence is not as great as shown by the unmodified model displayed in table 1.
+
+```{r clplot, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data based on the multivariate ordinal model"}
+require(cowplot)
+c9c10ppc <- readRDS("ppa_clmod_ppc.RDS")
+c9c10ppc[[1]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in selecting news stories you work on?") -> c9gg
+c9c10ppc[[2]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in deciding which aspects of a story should \n be emphasized?") -> c10gg
+plot_grid(c9gg, c10gg, ncol = 1)
+```
+
+As below
 
@@
 
-```{r, results = "asis", warning = FALSE, echo = FALSE}
+```{r ppa, results = "asis", warning = FALSE, echo = FALSE}
 clmod <- readRDS("ppa_clmod.RDS")
@@
 There are several reasons not related to our seed dictionaries that could lead to the 6 misclassified cases.
-The false-positive case is Korean and that could be due to incorrect tokenization at the MIT Media Cloud’s end.
+The false-positive case is Korean and that could be due to incorrect tokenization at the Media Cloud’s end.
 The 5 false-negative cases are in Norwegian, Portuguese, and Romanian.
-The content on the website might have changed since MIT Media Cloud collected the data.
+The content on the website might have changed since Media Cloud collected the data.
 For example, the ever-changing content in the sidebar might be counted as “main content” and recorded in the DTM.
@@
 
+# Poisson regression
+
+The useNews example could also be modeled by Poisson regression.
+
+```r
+weaklyinformative_prior <- c(prior_string("normal(0, 1)",
+                                          class = "b"),
+                             prior_string("normal(0, 1)",
+                                          class = "Intercept"))
+import_brms_poisson <- brm(z~offset(log(n))+(1|k)+log(x_import),
+                           data = outlet_data, family = poisson(),
+                           prior = weaklyinformative_prior,
+                           sample_prior = TRUE)
+```
+
+However, the PPCs reveal a property of the Poisson model.
+Compared with the PPCs of the negative binomial model (the same as Figure 4 in the main text), the Poisson model tends to produce stimulated data with an unusual high level of certainty (both models were based on 61 data points).
+It is an indication of shrinkage (reduction of standard error, i.e.
+more false positives) due to overdispersion [the variance of the data is higher than the expectation of the model, see @gardner:1995:R].
+Poisson model assumes the data to have only one parameter ($\lambda$), which represents both mean and variance.
+The current data clearly violates this assumption (the variance is far larger than the mean).
+
+```{r fig3x, warning = FALSE, echo = FALSE, fig.cap = "Posterior predictive checks of the Poisson model (Left) and the negative binomial model (Right) with 100 sets of simulated data"}
+ppc_poisson <- pp_check(import_brms_poisson, ndraws = 100)+ theme_minimal()+ xlim(0, 5000) + ylim(0, 7e-4)
+ppc_nb <- pp_check(import_brms, ndraws = 100)+ theme_minimal() + xlim(0, 5000) + ylim(0, 7e-4)
+plot_grid(ppc_poisson, ppc_nb, ncol = 2)
+```
+
 # References

### 2023-01-02 manuscript.rmd
Address most of the reviewers' comments

@@
 ---
-title             : "Bayesian multilevel modeling and its application in comparative communication research"
+title             : "Bayesian multilevel modeling and its application in comparative journalism studies"
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
     corresponding : yes
-    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
-    email         : "chung-hong.chan@mzes.uni-mannheim.de"
+    address       : "Unter Sachsenhausen 6-8, 50667 Köln"
+    email         : "chung-hong.chan@gesis.org"
   - name          : "Adrian Rauschfleisch"
@@
   - id            : "1"
-    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
+    institution   : "GESIS – Leibniz-Institut für Sozialwissenschaften, Germany"
   - id            : "2"
@@
   Comparative approaches are frequently used in communication research, especially journalism studies.
-The purpose of this paper is to argue that Bayesian multilevel regression is a better option for analyzing comparative data.
+The purpose of this paper is to argue that Bayesian multilevel regression is the most justifiable option for analyzing comparative data.
 We argue that it is the only approach that can simultaneously account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of comparative data.
-Using the openly available *Worlds of Journalism Study* and *useNews* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
+Using the openly available *Worlds of Journalism Study* and *useNews* datasets, we demonstrate how to apply the Bayesian approach for the analysis of comparative data.
 We address the common challenges when using the Bayesian approach and highlight the advantages of posterior predictive checks for modeling checking.
@@
 political orientation, online versus offline) or their countries (e.g.
-post-communist country) influence the behaviors of journalists or the content of news articles .
+post-communist country) influence the behaviors of journalists or the content of news articles.
 For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
@@
 
-This study of ecological effects on individual behaviors has a long tradition in social sciences.
-A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide].
-Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries.
-Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research.
+This study of ecological effects on individual behaviors has a long tradition in communication research.
+There are hypothesis-generating and hypothesis- testing comparative studies.
 An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
 Hypothesis-generating comparative study, however, is rare.
-Most studies have a confirmatory outlook.
 As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects.
@@
 In @wu:2000:SDI, multiple stepwise regression was used.
-These approaches violate the underlying assumptions.
+These approaches violate the underlying independence of observations assumption of linear regression (See non-atomicity below).
 It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
@@
 We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models.
-In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as the best possible approach for comparative research in communication science and especially in journalism studies.
-Using the openly available WJS and *useNews* datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
+In our paper, we first discuss these two issues and then suggest Bayesian multilevel regression as the most defensible option.
+Using the openly available WJS and *useNews* datasets, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
 
@@
 
-In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g.
+In comparative research, it is easy to assume that macro-level independent variables (e.g.
 Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g.
 the degree of opinion-orientation).
-The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
-Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the Worlds of Journalism data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA].
+The manifestation of this assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
+Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the WJS data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA].
 The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (journalist-level: perceived professional autonomy) and $x_{i}$ be the independent variable at the macro-level (country-level: democratic performance).
@@
 The choice of countries is almost always not randomly selected.
-<!-- [^1] --> This sampling approach makes the independence assumption even more fragile.
-
-<!-- [^1]: If countries were randomly selected, we shall see more African countries in comparative works. It is because 1/4, or 54 out of 195, UN countries are in Africa. -->
-
+This sampling approach makes the independence assumption even more fragile.
 Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g.
 @clarke:2008:W;@chen:2012:IIL].
-The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W].
-<!-- [^2] -->
 
-<!-- [^2]: The non-atomicity argument has been in standard statistics textbooks for 40+ years and it might look repetitious.
-We believe it is still necessary, not least because multilevel modeling --unlike what @mcelreath2020statistical [p.
-356] said-- is still not the default regression approach in communication research for hierarchical data and there are many justifications for using the disaggregation approach, e.g.
-an example in @zhu:2020:S [footnote 5].
-<\!-- Even a multilevel modeling textbook advocates these justifications [@bickel2007multilevel].
--\-> See also @nezlek:2008:IMM for a criticism of these justifications.
--->
-
-There are two solutions to this.
+There are two solutions to this [^indieerror].
 The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable.
@@
 Then, we can do a regression with a regression equation like so:
+
+[^indieerror]: In general, the non-atomicity alone only influences the inference (e.g.
+p-values, confidence intervals) by increasing the chance of Type I errors.
+The magnitude of the regression coefficient should still be consistent.
+Another approach, which we are not going to discuss in detail, is to use the clustered-robust standard error.
+For a survey of the technique, see @wooldridge:2003:CSM.
+The technique can only address the non-atomicity issue alone, but not non-stochasticity.
 
@@
 Second, this method discards a massive amount of information.
-It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
+It is useful only for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
 counting a binary variable).
@@
 
-In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average.
+In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average [^pooling].
 It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e.
@@
 We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.
+
+[^pooling]: One can also think about this in terms of pooling: how the data from different groups are combined.
+We can have complete pooling (the disaggregation approach, just one slope), no pooling (each group should be modelled individually and each group has a different slope), and partial pooling (each group does have a unique slope.
+But the distribution of all slopes follow a distribution).
 
@@
 
-In sum, multilevel modeling is the way to go for analyzing non-atomic data from comparative research.
+In sum, multilevel modeling is more justifiable for analyzing non-atomic data from comparative research.
 For surveys using probabilistic sampling, the conventional frequentist approach (maximum likelihood estimation, MLE) might still be valid and is available in most statistical packages [see an SPSS tutorial for communication researchers by @hayes:2006:PMM].
-However, @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e.
-more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
-countries) is small.
-@stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF].
-Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons.
-And for studies not using probabilistic sampling, we argue in the next section that the Bayesian approach is a better analytical approach.[@western:1994:BIC].
 
@@
 
-Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is.
+@stegmueller:2013:HMC demonstrates that MLE for multilevel modeling is associated with shrinkage (reduction of standard error, i.e.
+more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
+countries) is small.
+@stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF].
+Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons [@western:1994:BIC].
+
+Before diving into our theoretical reasoning, it is important to revisit what frequentist inference is.
 Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population.
@@
 
-Most of the comparative content analytic studies, unlike randomized surveys such as WJS, often collect all available content data from a bunch of selected media outlets.
+Most of the comparative content analytic studies, for example, often collect all available content data from a bunch of selected media outlets.
 In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets.
@@
 6, emphasis added) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.
-In that study, one could only get more data by including more media outlets or widening the time window.
-Unlike a repeatable survey like WJS, one can always randomly select more journalists from the sampling frame of all journalists in the respective country.
+In that study, one could only get more data by including more media outlets or widening the time window [^conventionalcontentanalysis].
+Unlike a (theoretically) repeatable survey like WJS, one can randomly select more journalists from the sampling frame of all journalists in the respective country.
 
-Therefore, these modern comparative content analytic studies are not repeatable and thus they generate non-stochastic data.
-It could be argued that data from these comparative content analytic studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
+[^conventionalcontentanalysis]: Comparative content analytic studies can also be performed without this census-like approach.
+The traditional approach of making probabilistic sample from all units can also be used [@krippendorff2018content].
+As there is an explicit sampling frame of all units, the population of content about which the sample is making inference from is known in this case.
+Any further inference made beyond the population is speculative.
+
+Therefore, these modern comparative content analytic studies are often not repeatable and thus they generate non-stochastic data.
+It could be argued that data from these comparative content analytic studies with a census-like approach are fundamentally irrelevant for frequentist inference [@western:1994:BIC].
 Confidence intervals generated do not have the same meaning as those from repeatable studies.
@@
 [^PVALUES]: In this article, we will not go into detail of the null hypothesis statistical testing (NHST) and p-values, except in the Online Appendix.
-It is because for studies with a very large N, which comparative studies usually are, NHST is guaranteed to give positive results due to the so-called “Too Big To Fail” problem [see @lin:2013:RCT].
-Also, researchers are usually not only interested in whether there is or isn’t an effect.
+Researchers are usually not only interested in whether there is or isn’t an effect.
 Instead, we are interested in how large the magnitude and in what direction the effect is.
@@
 45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3].
-In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation.
+In other words, a finite census-as-a-sample census is assumed to be a "representative sample" of an infinite superpopulation.
 This counterargument could be useful but unlike a regular random sample (cluster sample included), whose representativeness can be assessed, we can never assess the representativeness of the census-like data with respect to the theoretical superpopulation.
@@
 Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
-<!-- However, for Bayesian models so-called priors have to be chosen by researchers.
--->
 
@@
 The same approach is equally applicable to both non-stochastic and stochastic comparative datasets.
-Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.
-Besides these more abstract conceptual implications, choosing a Bayesian approach has some practical advantages, as we will later illustrate with the posterior predictive checks (PPCs), which can only be calculated if a Bayesian approach is used.
 
@@
 After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%.
-If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).
+If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100%.
+If we (or other researchers) "repeat the experiment" and resubmit the same paper again to *IJOC*, the probability of the resubmitted paper for being accepted is 0%.
 
-Without repeated experiment, these probabilities quantify our certainty on how likely this paper is being accepted, given the current available data .
+Without repeated experiment, these probabilities quantify our certainty on how likely the paper is being accepted, given the current available data .
 We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$).
@@
 Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use a weakly informative prior [@lemoine:2019:M].
-In this way, one specifies only the possible range of the posterior<!-- [^4] -->.
+In this way, one specifies only the possible range of the posterior.
 Some so-called "default weakly informative priors", e.g.
@@
 
-<!-- [^4]: One could also use a completely *noninformative* prior such as $\mathcal{U}(-\infty, \infty)$. It is, however, no longer advised. -->
-
 ## Bayesian communication research
 
-<!-- *"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p.
-19] -->
-
 Bayesian analysis is still a minority statistical method in social sciences.
-It is reasonable to say that Bayesian analysis is extremely rare in our field.
-Although some communication researchers adopted the method (e.g.
-AUTHOR2, AUTHOR3) <!-- [e.g.
-@kovic:2017:B;@chan2020high] -->, these studies are not comparative.
 As far as we know, the only available comparative communication research that Bayesian multilevel regression was used for studying ecological effect are @leeuw:2020:AAT and @heidenreich:2022:DE.
-We believe comparative communication research fits the use case of Bayesian multilevel regression analysis.This paper demonstrates how to do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ).
+As argued in the two previous sections,
+comparative communication research fits the use case of Bayesian multilevel regression analysis.
+This paper demonstrates how to do the analysis using the R package *brms* [@burkner2017advanced] (see the source code in the Online Appendix https://osf.io/2h4w8/?view_only=be14dc637b8e4fd1a26ac5c64682b6d9 ).
 As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar.
-<!-- The above-quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.
--->
 
@@
 
-In this example, the Bayesian approach is applied to a stochastic dataset from a randomized survey.
+In this example, the Bayesian approach is applied to a stochastic dataset from a survey in which some randomization is involved.
 The starting point of this example is the recent study by @hamada:2021:DJA.
@@
 It is important to recite the operationalization of professional autonomy here.
-The two questions in the survey are: (1) “Thinking of your work overall, how much freedom do you personally have in selecting news stories you work on?” (2) “How much freedom do you personally have in deciding which aspects of a story should be emphasized?” The possible answers ranged from 5 = “complete freedom” to 1 = “no freedom at all”.
+The two questions in the survey are: (1) "Thinking of your work overall, how much freedom do you personally have in selecting news stories you work on?" (2) "How much freedom do you personally have in deciding which aspects of a story should be emphasized?" The possible answers ranged from 5 = "complete freedom" to 1 = "no freedom at all".
 The two answers were averaged.
-We will come back to this operationalization later in this article.
 
@@
 
-Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data. Bayesian multilevel regression is a better approach.
+Let's assume we were in the shoes of @hamada:2021:DJA and wanted to replicate the study by @reich:2013:DJP with the second wave WJS data.
+Bayesian multilevel regression provides several advantages over the aggregated approach.
 
-First, it can take advantage of the hierarchical structure of the data and correctly estimate the contextual effect of democratic performance on the journalist-level perceived professional autonomy.
+First, it can take advantage of the hierarchical structure of the data and estimate the contextual effect of democratic performance on the journalist-level perceived professional autonomy.
 It allows for adjustment of other journalist-level predictors that are known to influence perceived professional autonomy, e.g.
@@
 In other words, whether the relationship is really in "J shape" is studied <!-- [^jshape] -->.
-It’s important to spell out all the equations so that we can have a better idea of all the estimands.
+It’s important to spell out all the equations so that we can have an idea of all the estimands.
 For the parsimonious model, the regression equations are:
@@
 
-In order to make the result from this replication comparable to that of @reich:2013:DJP, we also calculate the standardized regression coefficients, i.e. all variables are mean-centered.
+In order to make the result from this replication comparable to that of @reich:2013:DJP, we also calculate the standardized regression coefficients, i.e. all variables are transformed to Z-scores.
 
@@
 The Index of Democracy is the strongest predictor among all other predictors (Rank: 0.15, Experience: 0.08, gender: -0.06, university degree: -0.01).
-It supports @hamada:2021:DJA's h2a.
+The standardized regression coefficient for GDP per capita is not large (-0.05).
+It supports @hamada:2021:DJA's h2a, even after adjusting for the possible confounding effect of GDP per capita.
 
@@
 While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
-The Bayesian approach allows us to say that *given the observed data, the true estimate of the standardized regression coefficient has 95% probability of falling within  0.13 and 0.34*.
-In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true estimate of the standardized regression coefficient*.
+The Bayesian approach allows us to say that *given the observed data, the true value of the standardized regression coefficient has 95% probability of falling within  0.13 and 0.34*.
+In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies (if possible), 95% of the confidence intervals will include the true value of the standardized regression coefficient*.
 One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way as described above [@morey:2015].
@@
 
-A good model for theory testing should pin down the data-generating process in the real world, not just whether the model fits the data.
-Therefore, a good model should be able to generate simulated data that are like the observed data [@gelman2007comment].
+A useful model for theory testing should pin down the data-generating process in the real world, not just whether the model fits the data.
+Therefore, a model should be able to generate simulated data that are like the observed data [@gelman2007comment].
 The gist of posterior predictive check is to use the fitted model to generate some simulated data ($y_{rep}$) and compare them with the original observed data ($y$).
-A good model should display a similar probability distribution of $y_{rep}$ and $y$.
+If the model is useful, the model should display a similar probability distribution of $y_{rep}$ and $y$.
 (Figure \@ref(fig:fig3) ).
@@
 But the model can only give simulated data $y_{rep}$ with a gaussian distribution whilst the shape of the original data $y$ is not gaussian at all.
-The finger-like shape is a manifestation of analyzing the two ordinal variables (two Likert items) as if they were in an interval scale.
-With this check, it shows the original analytic scheme of both @reich:2013:DJP and @hamada:2021:DJA cannot capture the shape of the data.
-Also, the psychological distances between two neighboring options in a Likert scale (e.g.
-“complete freedom” and “a great deal of freedom”) are not the same across all pairs and one can’t assume that Likert items can be summed or averaged [@buerkner:2019:ORM].
+In the online appendix, we model the finger-like shape of the data with another technique.
 
@@
 
-If this were not a replication and one didn't need to accept the previous operationalization of perceived professional autonomy, a better way to answer this research question using the WJS data is to make two modifications.
-First, one should use the ordinal regression technique to model the responses from Likert items [@buerkner:2019:ORM].
-Second, the two Likert items related to perceived professional autonomy can be modeled jointly using a multivariate regression model [^MULTIVARIATE].
+## Summary
 
-[^MULTIVARIATE]: Please notice we are not talking about *multiple* regression regression.
-
-As an exploratory analysis, we fitted a Bayesian model with these two modifications (see Online Appendix).
-And indeed the posterior predictive check of the model suggests that the modified model is better at pinning down the data-generating process of the Likert items than the unmodified model: the new model correctly pins down both the range, peaks and shape of the original data (Figure \@ref(fig:clplot)).
-The bottom line is the same: democratic performance of a country is still a strong predictor of journalists’ perceived professional autonomy in the modified model, although the magnitude of influence is not as great as shown by the unmodified model displayed in table 1.
-
-```{r clplot, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data based on the multivariate ordinal model"}
-require(cowplot)
-c9c10ppc <- readRDS("ppa_clmod_ppc.RDS")
-c9c10ppc[[1]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in selecting news stories you work on?") -> c9gg
-c9c10ppc[[2]] + ggtitle(label = "", subtitle = "How much freedom do you personally have in deciding which aspects of a story should \n be emphasized?") -> c10gg
-plot_grid(c9gg, c10gg, ncol = 1)
-```
+In this example, the Bayesian multilevel regression approach allows the study of ecological effect hypotheses of a macro-level variable (e.g.
+Democracy) on a micro-level variable with a comparative, semi-randomized dataset.
+The inference of the model is at the level specified in the hypotheses (micro-level, i.e.
+journalists) and allows adjustment for other confounding variables (e.g.
+GDP per capita).
+Visualizations such as conditional effects plot and posterior predictive checks assist model checking.
 
@@
 
-We used only the data from 2019 as the baseline<!-- .
-We --> and excluded media outlets that contributed <1,000 articles in that year.
+We used only the data from 2019 as the baseline and excluded media outlets that contributed <1,000 articles in that year.
 This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated.
-In total, <!-- 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included.
-These --> 61 media outlets contributed 1,525,871 articles.
+In total, 61 media outlets contributed 1,525,871 articles.
 
@@
 
-<!-- ```{r, echo = FALSE} -->
-<!-- Language <- c("English", "German", "Spanish", "Romanian", "Korean", "Portugese", "Norwegian", "Dutch") -->
-
-<!-- Lexicon <- c("chinese, china, beijing, shanghai", "chinesisch*, chinesin*, chinese*, china*, peking, shanghai", "chino*, china*, pekin, shanghái", "chinez*, china, beijing, shanghai", "중국인, 중화, 중국, 베이징, 북경, 상하이, 상해", "chinês, chines*, china, pequim, xangai", "kineser*, kinesar*, kinesisk, kina, beijing, shanghai", "chinezen, chinees*, chinezin*, chines*, china, peking, beijing, sjanghai, shanghai") -->
-<!-- papaja::apa_table(data.frame(Language, Lexicon), caption = "Dictionaries used for detecting China coverage") -->
-<!-- ``` -->
-
 ## Distance measure: Trade volume
@@
 
-We used negative binomial regression for this analysis [^EXT].
-Media outlets are nested in countries <!-- (e.g.
-*Der Standard* and *Österreichischer Rundfunk* are nested in Austria) -->.
-Thus, a country-based variance is added ($\mu_{0k}$).
-We also added $\log{n_{j}}$ as an offset value.
-An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation.
-Effectively, we modeled the *rate* of China coverage.
-Applying the same notation under the introduction section, the multilevel regression equations are:
+We used negative binomial regression for this analysis [^EXT]. Applying the same notation under the introduction section, the multilevel regression equations are:
 
@@
 \log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} + \epsilon_{jk}\end{align}
+
+Media outlets are nested in countries.
+Thus, a country-based variance is added ($\mu_{0k}$).
+We also added $\log{n_{j}}$ as an offset value.
+An offset value is a term that does not have the associated regression coefficient at the right-hand side of the regression equation.
+Effectively, we modeled the *rate* of China coverage.
 
@@
 
+## Summary
+
+In this example, the Bayesian multilevel regression approach allows the study of ecological effect hypotheses in a nonrandom, comparative dataset.
+Various extensions we demonstrated in the online appendix show the flexibility of the approach.
+
 # Conclusion
@@
 In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research.
-We demonstrate using the openly available useNews and WJS datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
-We mainly used the WJS dataset to illustrate the strength of multilevel models, whereas the useNews dataset was selected as an example where Bayesian models are conceptually the better choice.
+We demonstrate using the openly available WJS and useNews datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
+We mainly used the WJS dataset to illustrate the strength of multilevel models, whereas the useNews dataset was selected as an example where Bayesian models are conceptually the most defensible option.
 However, both multilevel models and Bayesian analysis are connected approaches.
 
-First of all, both examples require a multilevel approach.
-We believe this is not an optional choice.
+First of all, the hierarchical data structure in both examples warrants the multilevel modeling approach.
 The question then is why we should use a Bayesian approach as these models can also be estimated with a frequentist approach.
@@
 Of course, as the argument about the theoretical superpopulation shows, one could always justify a frequentist approach.
-However, there are also several practical reasons why a Bayesian approach is more suitable than a default approach.
+However, there are also several practical reasons why a Bayesian approach is more suitable than a frequetist approach.
 
@@
 Thus, the priors have almost no influence on the posterior distribution of the parameters.
-Moreover, if we have prior knowledge, it allows us to create even better models, as the first example has shown.
+Moreover, if we have prior knowledge, it allows us to create even more useful models, as the first example has shown.
 
@@
 It took four days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Example 2, article-level analysis).
-Still, eventually, it worked, and typical studies in comparative journalism research [e.g.
-27,567 journalists in Example 1] can be estimated within a reasonable time frame.
-Secondly, if sampling procedures are used for a typical experimental design that could be replicated, using a frequentist approach is probably the less complicated approach and  a valid choice if combined with a preregistration of the hypotheses [@schaefer:2019:MES] [^PREREG].
+Still, eventually, it worked, and typical studies in comparative journalism research , e.g.
+27,567 journalists in Example 1 can be estimated within a reasonable time frame.
+Secondly, if sampling procedures are used for a typical experimental design that could be replicated, using a frequentist approach is probably the less complicated approach.
 In any other scenario, we believe the benefits of the Bayesian approach outweigh the potential limitations.
 
-[^PREREG]: Even using the Bayesian approach, hypotheses should also be preregistered.
+# Coda: An education reform proposal
 
-# Coda: A radical education reform proposal
-
-@rinke:2018:PMA advocate a different teaching of statistics for communication research.
+Unlike what it was several years ago, software and educational materials for doing Bayesian analysis have been tremendously improved.
+We see the availability of the R package *brms* [@burkner2017advanced] and approachable textbooks such as *Regression and Other Stories* [@gelman2020regression] and *Statistical Rethinking* [@mcelreath2020statistical] as watershed moments in the (re)mainstreamization of the Bayesian approach.
+These development coincides with @rinke:2018:PMA's recommendation of a different teaching of statistics for communication research.
 In their opinion, the teaching of frequentist hypothesis testing would be less central.
-“Instead, more substantive concerns, replication, effect sizes, and better ways of drawing statistical inferences, including Bayesian methods, would take center stage.” [@rinke:2018:PMA, p.
-18] We concur with their proposal and hope that this paper can convince the educators of our field to teach Bayesian methods to future communication researchers.
-Unlike what it was several years ago, we now have communication studies using the Bayesian approach published in top communication journals.
-Software and educational materials for doing Bayesian analysis have been tremendously improved.
-We see the availability of the R package *brms* [@burkner2017advanced] and approachable textbooks such as *Statistical Rethinking* [@mcelreath2020statistical] as watershed moments in the (re)mainstreamization of the Bayesian approach.
-Based on the recent development and the conclusion of this paper, we would like to make an even more radical education reform proposal than @rinke:2018:PMA’s: We should teach the Bayesian approach as the default way of drawing statistical inferences.
-The frequentist approach should instead be taught as an option specifically for the analysis of stochastic data from studies such as media experiments and simple random surveys.
-When it comes to teaching regression analysis, we should teach the statistical issues concerning the non-atomicity of the data, as well as the necessity of model checking with procedures such as posterior predictive checks.
+"Instead, more substantive concerns, replication, effect sizes, and better ways of drawing statistical inferences, including Bayesian methods, would take center stage." [@rinke:2018:PMA, p.
+18] We concur with their proposal.
+The frequentist approach should be taught only in the context of analyzing data with explicit randomization, such as randomized experiments and simple random surveys.
+We hope that this paper can convince the educators of our field to teach Bayesian methods, especially for multilevel regression analysis.
+We should also teach the issues concerning the non-atomicity and non-stochasticity of real-world data, as well as the necessity of model checking with procedures such as posterior predictive checks.
 

### 2023-01-03 manuscript.rmd
Add Adrian's suggestions

@@
 authornote: |
-  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
+  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (Hong Kong Baptist University) for sharing details about her study.
 The authors report there are no competing interests to declare.
@@
 
-In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average [^pooling].
+In these equations, $\gamma_{00}$ is the average slope, while $\mu_{0k}$ is group-dependent deviations of the slope from the average.
 It is usually set as having a normal distribution with a variance $\tau_{00}$, i.e.
 $\mu_{0k} \sim \mathcal{N}(0, \tau_{00})$.
-Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group.
+Instead of a single value, the regression coefficient $\gamma_{00}$ is assumed to be a distribution of values depending on a macro-level group [^pooling].
 It addresses the problem of clustering of articles by macro-level variables.
@@
 
-[^pooling]: One can also think about this in terms of pooling: how the data from different groups are combined.
-We can have complete pooling (the disaggregation approach, just one slope), no pooling (each group should be modelled individually and each group has a different slope), and partial pooling (each group does have a unique slope.
-But the distribution of all slopes follow a distribution).
+[^pooling]: One can also think about this in terms of pooling: how the data from different groups are pooled together.
+Complete pooling (the disaggregation approach, one slope for all groups), no pooling (each group is modelled individually and each group has a different slope), and partial pooling (each group has a unique slope.
+But the distribution of all slopes follows a distribution) are three scenarios.
+Multilevel modeling uses partial pooling.
 
-The benefit of using multilevel modeling lies in its flexibility in handling multi-level data.
+The advantage of using multilevel modeling lies in its flexibility in handling multi-level data.
 Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available.
@@
 Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA].
-Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
+Unlike the frequentist confidence intervals, Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120].
 
@@
 What is the probability for this paper being accepted by *IJOC*?
-Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
+Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we could only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions.
 It is indeed impractical as well as inhumane to the editorial team of *IJOC*.
@@
 After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%.
-After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%.
+After months of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%.
 After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%.
@@
 
-Without repeated experiment, these probabilities quantify our certainty on how likely the paper is being accepted, given the current available data .
+Without repeated experiment, these probabilities quantify our certainty on how plausible the paper is being accepted, given the current available data.
 We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$).
@@
 In the *IJOC* example, the likelihood function is based on rough rules from our experience and thus is not systematic.
-In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC).
+In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC) [^mcmcexplanation].
 Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), which require no elaboration, 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.
+
+[^mcmcexplanation]: How concretely MCMC can faciliate the estimation of likelihood function, given the data and prior, is too technical to be included in this paper.
+Readers can get an intuition of how it works in Chapter 8 of @mcelreath2020statistical.
+For how the method works in regression models, Chapters 9, 10, and 12 of @mcelreath2020statistical.
+For a comparative perspective between Bayesian and frequentist approaches, please refer to @samaniego2010comparison.
 
@@
 For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.
-
 For the other six sevenths, one might not have any information to set an informative prior.
@@
 A standardized protocol for expert elicitation is available [@hanea:2017:IDE] and there are many software tools available to facilitate the process [^experttools].
-
-[^experttools]: Some examples are the web-based MATCH Uncertainty Elicitation Tool (http://optics.eee.nottingham.ac.uk/match/uncertainty.php) and the R package SHELF.
-
 But one person's expert opinion could be another person's wishful thinking.
@@
 @elff:2020:MAF].
+
+[^experttools]: Some examples are the web-based MATCH Uncertainty Elicitation Tool (http://optics.eee.nottingham.ac.uk/match/uncertainty.php) and the R package SHELF.
 
@@
 
-\begin{align}
-  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} + \epsilon_{i}
-\end{align}
-
-\begin{align}
-  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} + \beta_{6} GDP_{k} \\ + \beta_{7} DEMO^2_{k} + \beta_{8} DEMO^3_{k} + \epsilon_{i}
-\end{align}
+\begin{align*}
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i \\ + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} \\ + \beta_{6} GDP_{k} + \epsilon_{i} \\
+  PPA_{ik} &= \beta_{0} +\beta_{1} XP_i + \beta_{2} RANK_i + \beta_{3} GEN_i \\ + \beta_{4} UNIV_i +  \beta_{5} DEMO_{k} \\ + \beta_{6} GDP_{k} + \beta_{7} DEMO^2_{k} \\ + \beta_{8} DEMO^3_{k} + \epsilon_{i}\\
+\end{align*}
 
@@
 
-## Summary
+## Summary of Example 1
 
@@
 ```{r fig3x, echo = FALSE, fig.cap = "Posterior predictive checks with 100 sets of simulated data"}
-pp_check(import_brms, ndraws = 100)
+pp_check(import_brms, ndraws = 100) + theme_minimal()
 ```
 
-## Summary
+## Summary of Example 2
 
@@
 First, the Bayesian interpretation of CIs is far more intuitive than the frequentist interpretation [@morey:2015].
-Secondly, while all the models reported here can also be estimated within a frequentist framework, using a Bayesian framework and, more specifically, brms allows estimating them all with the same package.
+Secondly, while all the models reported here can also be estimated within a frequentist framework, using a Bayesian framework and, more specifically, *brms* allows estimating them all with the same package.
 This also makes it easier to compare different competing models, as we have illustrated in our analysis.
-Third, comparing models and checking the predictive quality of the models is an essential part of a Bayesian framework.
+Third, comparing models and checking the data-generating quality of the models is an essential part of a Bayesian framework.
 Of course, frequentist models can also be compared based on information criteria such as the BIC.

### 2023-01-10 extension.rmd
some small edits

@@
 In total, 160 items were selected.
-A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the meta data provided in the useNews dataset [@puschmann:2020].
-For some languages, the coder used Google Translate to translate the full text article to English.
+A coder with no knowledge of the ground truth (matching or not) annotated the full-text articles by following the URLs in the metadata provided in the useNews dataset [@puschmann:2020].
+For some languages, the coder used Google Translate to translate the full-text article to English.
 In total, only 138 URLs were still accessible.
@@
 
-[^POWER]: Statistical power is a frequentist concept specifying the long run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.
+[^POWER]: Statistical power is a frequentist concept specifying the long-run probability of correctly rejecting the null hypothesis. It is usually not relevant for Bayesian inference.
 
@@
 The proportion of 95\% HDI falling inside the ROPE is 0\%.
-Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) have no overlap with the ROPE (the shaded region).
+Figure \@ref(fig:figrope) also displays that the 95\% HDI (the pink region) has no overlap with the ROPE (the shaded region).
 Using the decision rules by @kruschke:2018:RAP, there are 3 possible scenarios: reject the null (when most of the 95\% HDI falls outside the ROPE), accept the null (when most of the 95\% HDI falls inside the ROPE) and undecided (when it can’t be decided).
@@
 In this situation, the proportion of 95\% HDI falls inside the ROPE is 68\%.
-The proportion is quite high but it is not decisive.
+The proportion is quite high, but it is not decisive.
 @kruschke:2018:RAP suggests accepting the null when more than 95\% of the 95\% HDI falls inside the ROPE.
@@
 One should note that the decision rules by @kruschke:2018:RAP depend on many methodological decisions, e.g.
-how to determine the ROPE, how wide should the ROPE be, and which level of HDI to use.
+how to determine the ROPE, how wide the ROPE should be, and which level of HDI to use.
 ROPE is also sensitive to the scale of measurement.
@@
 
-# Leave-one-out cross validation of Example 2
+# Leave-one-out cross-validation of Example 2
 
-Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross validation (LOO).
+Another way to compare the cubic model and the parsimonious model is to conduct a leave-one-out cross-validation (LOO).
 The basic idea of LOO is to study the out-of-sample accuracy of the model by removing one data point at a time.
-Given the rest of the data and the prediction model, one evaluates how accurate is the model to predict the outcome of the removed data point.
+Given the rest of the data and the prediction model, one evaluates how accurate the model is in predicting the outcome of the removed data point.
 The Bayesian LOO estimate of out-of-sample predictive fit ($elpd_{loo}$) can be used to compare the out-of-sample accuracy of models [@vehtari:2016:PBW].
 
-In R, the LOO cross validation of the two models (parsimonious model: *ppa_mod*; cubic model *ppa_qmod*) can be launched with the function `loo`.
+In R, the LOO cross-validation of the two models (parsimonious model: *ppa_mod*; cubic model *ppa_qmod*) can be launched with the function `loo`.
 
@@
 more false positives) due to overdispersion [the variance of the data is higher than the expectation of the model, see @gardner:1995:R].
-Poisson model assumes the data to have only one parameter ($\lambda$), which represents both mean and variance.
+The Poisson model assumes the data to have only one parameter ($\lambda$), which represents both mean and variance.
 The current data clearly violates this assumption (the variance is far larger than the mean).

### 2023-01-10 manuscript.rmd
small edits

@@
 @zhao2019appealing].
-The methodological issues discussed in this paper apply also to those cases.
+The methodological issues discussed in this paper also apply to those cases.
 
@@
 This study of ecological effects on individual behaviors has a long tradition in communication research.
-There are hypothesis-generating and hypothesis- testing comparative studies.
+There are hypothesis-generating and hypothesis-testing comparative studies.
 An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
@@
 It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure.
-A news article is nested within its media outlet and its media outlet is in turn nested within its country.
+A news article is nested within its media outlet and its media outlet is, in turn, nested within its country.
 Such data structure brings two problems: non-atomicity and non-stochasticity.
@@
 In our paper, we first discuss these two issues and then suggest Bayesian multilevel regression as the most defensible option.
-Using the openly available WJS and *useNews* datasets, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.
+Using the openly available WJS and *useNews* datasets, we then demonstrate how to apply a Bayesian approach to analyze comparative data.
 
@@
 
-In comparative research, it is easy to assume that macro-level independent variables (e.g.
-Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g.
-the degree of opinion-orientation).
+In comparative research, it is easy to assume that macro-level independent variables (e.g., Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g., the degree of opinion-orientation).
 The manifestation of this assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable.
@@
 This sampling approach makes the independence assumption even more fragile.
-Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g.
-@clarke:2008:W;@chen:2012:IIL].
+Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g., @clarke:2008:W;@chen:2012:IIL].
 
@@
 
-[^indieerror]: In general, the non-atomicity alone only influences the inference (e.g.
-p-values, confidence intervals) by increasing the chance of Type I errors.
+[^indieerror]: In general, the non-atomicity alone only influences the inference (e.g., p-values, confidence intervals) by increasing the chance of Type I errors.
 The magnitude of the regression coefficient should still be consistent.
@@
 Second, this method discards a massive amount of information.
-It is useful only for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
+It is useful only for the analysis of a dependent micro-level variable with a reasonable aggregation function (e.g.
 counting a binary variable).
@@
 
-The advantage of using multilevel modeling lies in its flexibility in handling multi-level data.
-Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available.
+The advantage of using multilevel modeling lies in its flexibility in handling multilevel data.
+Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available.
 [^WJSOUTLET] The multilevel regression equations are rewritten as:
@@
 This model is called the varying slope model and is useful to establish robust estimation of effect (in this case $\gamma_{10}$) across all countries.
-In this paper, we will not go into detail of this kind of model.
+In this paper, we will not go into detail about this kind of model.
 For an example of its application in comparative communication research, see @barnidge:2018:SMS.
@@
 @stegmueller:2013:HMC demonstrates that MLE for multilevel modeling is associated with shrinkage (reduction of standard error, i.e.
-more false positives) and the shrinkage is more severe when the number of macro-level units (e.g.
-countries) is small.
+more false positives), and the shrinkage is more severe when the number of macro-level units (e.g., countries) is small.
 @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF].
@@
 Most of the comparative content analytic studies, for example, often collect all available content data from a bunch of selected media outlets.
-In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets.
+In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies collect the entire population of observations from some non-probabilistically selected media outlets.
 In these census-like situations, there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA].
@@
 [^conventionalcontentanalysis]: Comparative content analytic studies can also be performed without this census-like approach.
-The traditional approach of making probabilistic sample from all units can also be used [@krippendorff2018content].
+The traditional approach of making a probabilistic sample from all units can also be used [@krippendorff2018content].
 As there is an explicit sampling frame of all units, the population of content about which the sample is making inference from is known in this case.
@@
 
-Without repeated experiment, these probabilities quantify our certainty on how plausible the paper is being accepted, given the current available data.
+Without repeated experiments, these probabilities quantify our certainty on how plausible the paper is being accepted, given the currently available data.
 We revise our old beliefs (or **prior**, $p(\theta)$) with the new data ($X$) and form our revised belief (or **posterior**, $p(\theta|X)$).
@@
 
-[^mcmcexplanation]: How concretely MCMC can faciliate the estimation of likelihood function, given the data and prior, is too technical to be included in this paper.
+[^mcmcexplanation]: How concretely MCMC can facilitate the estimation of likelihood function, given the data and prior, is too technical to be included in this paper.
 Readers can get an intuition of how it works in Chapter 8 of @mcelreath2020statistical.
@@
 R interfaces to Stan (the probabilistic programming language for conducting MCMC), such as *brms* [@burkner2017advanced], can enable the derivation of the likelihood function (Part 2).
-But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE.
+But still, it is important to be mindful that Bayesian analysis is much more computationally intensive than methods such as MLE.
 Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.
@@
 @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt.
-For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.
-For the other six sevenths, one might not have any information to set an informative prior.
+For these one-seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.
+For the other six-sevenths, one might not have any information to set an informative prior.
 One option is to consult experts or to make an educated guess.
@@
 But one person's expert opinion could be another person's wishful thinking.
-And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g.
+And this perceived subjectivity of specifying priors by experts’ judgment attracts widespread criticism from both statisticians [e.g.
 @efron1986isn] and social scientists [e.g.
@@
 It is like previous studies [@stegmueller:2013:HMC; @elff:2020:MAF].
-While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference.
+While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are totally different from a philosophical point of view and lead to different forms of inference.
 The Bayesian approach allows us to say that *given the observed data, the true value of the standardized regression coefficient has 95% probability of falling within  0.13 and 0.34*.
@@
 
-We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a Bayesian multilevel regression analysis on a nonstochastic comparative dataset.
+We used the useNews dataset [@puschmann:2020] to demonstrate how to perform a Bayesian multilevel regression analysis on a non-stochastic comparative dataset.
 The analysis was guided by a classic question in news value research: Does the distance between China and the host country of a media outlet increase the frequency of China coverage?
@@
 The outlet-level analysis is an aggregated version of article-level analysis.
-It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with a very small data size.
+It is used to demonstrate the flexibility of Bayesian analysis to handle two-level data with very small data size.
 The article-level analysis is used to demonstrate the analysis of a massive three-level dataset.

### 2023-04-06 extension.rmd
Add post-acceptance edits by Adrian

@@
 ---
-title             : "Online appendix to \"Bayesian multilevel modeling and its application in comparative communication research\""
+title             : "Online appendix to \"Bayesian multilevel modeling and its application in comparative journalism studies\""
 shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"
@@
 require(cowplot)
+require(ggplot2)
 c9c10ppc <- readRDS("ppa_clmod_ppc.RDS")

### 2023-04-06 manuscript.rmd
Add post-acceptance edits by Adrian

@@
     email         : "chung-hong.chan@gesis.org"
-  - name          : "Adrian Rauschfleisch"
+  - name          : "Adrian Rauchfleisch"
     affiliation   : "2"
@@
 authornote: |
-  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (Hong Kong Baptist University) for sharing details about her study.
-The authors report there are no competing interests to declare.
-  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/
+  Adrian Rauchfleisch’s work was supported by the National Science and Technology Council, Taiwan (ROC), grant no.
+111-2628-H-002-003-.
+The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Professor Junior Yuner Zhu (Hong Kong Baptist University) for sharing details about her study.
+  Source code and data are available at https://github.com/chainsawriot/usenews_bayes. Preregistration: https://osf.io/2h4w8/
 
@@
 political orientation, online versus offline) or their countries (e.g.
-post-communist country) influence the behaviors of journalists or the content of news articles.
+post-communist country) influence journalists' behaviors or the content of news articles.
 For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological.
@@
 There are hypothesis-generating and hypothesis-testing comparative studies.
-An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
+An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized.
 Hypothesis-generating comparative study, however, is rare.
 As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects.
-In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
+Usually traditional (frequentist) hypothesis testing approaches were used in this context: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries.
 In @wu:2000:SDI, multiple stepwise regression was used.
@@
 The goal of this paper is twofold.
-We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models.
+We use examples from journalism studies as the most critical cases in communication science to highlight (1) the strength of multilevel models and (2) the advantages of Bayesian models.
 In our paper, we first discuss these two issues and then suggest Bayesian multilevel regression as the most defensible option.
@@
 This method is the so-called "disaggregation approach".
-From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel].
+From an epistemic standpoint, searching for an ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel].
 From a statistical standpoint, this approach violates the underlying independence assumption.
@@
 In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels.
-Using the above example, $y_{ik}$ denotes the perceived professional autonomy of the $i$-th journalist in the $j$-th country; $x_{k}$ denotes the democratic performance of the $k$-th country.
+Using the above example, $y_{ik}$ denotes the perceived professional autonomy of the $i$-th journalist in the $k$-th country; $x_{k}$ denotes the democratic performance of the $k$-th country.
 
@@
 It addresses the problem of clustering of articles by macro-level variables.
-This model is called the varying-intercept model and is used frequently in social science research.
+This model is called the varying-intercept model and is frequently used in social science research.
 We can then study the magnitude of $\gamma_{01}$ to determine the ecological effect.
@@
 [^pooling]: One can also think about this in terms of pooling: how the data from different groups are pooled together.
-Complete pooling (the disaggregation approach, one slope for all groups), no pooling (each group is modelled individually and each group has a different slope), and partial pooling (each group has a unique slope.
+Complete pooling (the disaggregation approach, one slope), no pooling (each group is modelled individually and each group has a different slope), and partial pooling (each group has a unique slope.
 But the distribution of all slopes follows a distribution) are three scenarios.
@@
 It is a distribution and therefore we need ways to display both the central tendency and spread of the distribution.
-By default, *brms* displays the mean and the 95\% High Density Interval (HDI).
+By default, *brms* displays the mean and the 95\% Highest Density Interval (HDI).
 <!-- [^5] --> These two values represent the point and interval estimates of the regression coefficient.
@@
 colnames(wjs_reg)[2:4] <- c("Bayesian", "MLE", "Disaggregation")
-apa_table(wjs_reg, caption = "Point and interval estimates from WJS analysis using three different analytic strategies: Bayesian multilevel modeling, multilevel modeling using MLE, and Disaggregation approach")
+apa_table(wjs_reg, caption = "Point and Interval Estimates From WJS Analysis Using Three Different Analytic Strategies: Bayesian Multilevel Modeling, Multilevel Modeling Using MLE, and Disaggregation Approach")
 ```
@@
 
-[^EXT]: We propose four extensions: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes (online appendix).
-
 \begin{align}
@@
 \log{z_{jk}} - \log{n_j} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} +  \epsilon_{jk} \\
-\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} + \epsilon_{jk}\end{align}
+\log\frac{z_{jk}}{n_{j}} &= \gamma_{00} + \mu_{0k} + \gamma_{01} \log{x_{k}} + \epsilon_{jk}
+\end{align}
 
@@
 Effectively, we modeled the *rate* of China coverage.
+
+[^EXT]: We propose four extensions: hypothesis testing, investigating cross-level interaction, establishing informative prior, and testing for temporal changes (online appendix).
 
@@
 colnames(import_reg)[2:4] <- c("Bayesian", "MLE", "Disaggregation")
-apa_table(import_reg, caption = "Point and interval estimates from outlet-level analysis using three different analytic strategies: Bayesian multilevel modeling, multilevel modeling using MLE, and Disaggregation approach")
+apa_table(import_reg, caption = "Point and Interval Estimates From Outlet-Level Analysis Using Three Different Analytic Strategies: Bayesian Multilevel Modeling, Multilevel Modeling Using MLE, and Disaggregation Approach")
 ```
@@
 Similar to the previous example, we conducted the posterior predictive check (Figure  \@ref(fig:fig3x)).
-Our model can capture both the range, peak and shape of the original data.
+Our model can capture the original data's range, peak, and shape.
 But there are many variations in the simulated data, probably due to the fact that the Bayesian model is based on just 61 data points and one single predictor.
@@
 In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative communication research.
-We demonstrate using the openly available WJS and useNews datasets that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
+Using the openly available WJS and useNews datasets, we demonstrate that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*.
 We mainly used the WJS dataset to illustrate the strength of multilevel models, whereas the useNews dataset was selected as an example where Bayesian models are conceptually the most defensible option.
@@
 Still, eventually, it worked, and typical studies in comparative journalism research , e.g.
-27,567 journalists in Example 1 can be estimated within a reasonable time frame.
+27,567 journalists in Example 1 can be estimated within a reasonable time frame (< 10 mins).
 Secondly, if sampling procedures are used for a typical experimental design that could be replicated, using a frequentist approach is probably the less complicated approach.
